### 2022-01-30 bps_conference.Rmd
data file completed

---
title: "Testing the precision of Bangla Communication Scale: Item Response Theory Guided Analysis"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r pacman, include=FALSE}
#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap, foreign,DT,SimDesign)
library(gtExtras)
library(tabledown)

#if you dont have LaTeX installed run the following lines
#install.packages("tinytex")
#tinytex::install_tinytex()
```

## Slide with Bullets

- Introduction
- Method
- Results
- Discussion

## Introduction

## Method

## Demographics
```{r demo}
knitr::include_graphics("Figures/demographics.png", dpi = 600) 
```

## Response Distribution

```{r}
knitr::include_graphics("Figures/communication.png", dpi = 600)

```

## Item Response Theory
-R version 4.1.2 (2021-11-01) with "mirt" package  
-Estimation Method: Marginal Maximum Likelihood  method with the MHRM algorithm.
_ Model : "Graded Response Model"
- Monty Carlo Study Showed for 23 items root mean squared error become stabilized for a sample range 200-250. Our sample is within that range.

## Option Charecteristics Curve
```{r}
knitr::include_graphics("Figures/problem.icc.png", dpi = 600)

```

## Option Charecteristics Curve (Cnt.)
```{r}
knitr::include_graphics("Figures/good.icc.png", dpi = 600)

```

## Item Plots

```{r ip1}
knitr::include_graphics("Figures/ICC1.png", dpi = 600) 
```

## Item Plots (Cont)

```{r ip2}
knitr::include_graphics("Figures/ICC2.png", dpi = 600) 
```

## Item Plots (Cont)

```{r ip3}
knitr::include_graphics("Figures/ICC3.png", dpi = 600) 
```

## Item Plots (Cont)

```{r ip4}
knitr::include_graphics("Figures/ICC4.png", dpi = 600) 
```

## IRT Parameters
```{r irtparadata, include=F}
param <- readr::read_csv("table_raw/IRT_parameters.csv")

```

## Person Fit

```{r personfit}
knitr::include_graphics("Figures/person.png", dpi = 600)

```

```{r para, results='asis'}
param %>% 
  flextable::flextable() 
```

## Test Information Plot

```{r TIC, results='asis'}
knitr::include_graphics("Figures/TIC.png", dpi = 600)

```

## Conditional Reliability
```{r conrel}
knitr::include_graphics("Figures/conrel.png", dpi = 600)

```

### 2022-01-30 manuscript.Rmd
data file completed

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200)

set.seed(123)
par(family = "Arial")
```

```{r pacman, eval=FALSE, include=FALSE}
#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap, foreign,DT,SimDesign)
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")

papaja::r_refs("references.bib")
#if you dont have LaTeX installed run the following lines
#install.packages("tinytex")
#tinytex::install_tinytex()
```

---
nocite: |
  `r cite_r("references.bib")`

---

# Methods
```{r data, include=F}
data = foreign::read.spss("Raw/Validity construct.sav", to.data.frame=TRUE)

write_csv(data, "Processeddata/part2.csv")

## Recoding data$CS9 into data$CS9_rec
data$CS9 <- fct_recode(data$CS9,
  "always" = "always_duplicated_4"
)

## Recoding com$Cs1 into com$Cs1_rec
data$Cs1 <- fct_recode(data$Cs1,
  "rarely" = "Rarely"
)

## Recoding com$CS23 into com$CS23_rec
data$CS23 <- fct_recode(data$CS23,
  "never" = "Never",
  "rarely" = "Rarely"
)

com <- data[,7:29]

names(com)[names(com) == "Cs1"] <- "CS01"
names(com)[names(com) == "Cs2"] <- "CS02"
names(com)[names(com) == "CS3"] <- "CS03"
names(com)[names(com) == "CS4"] <- "CS04"
names(com)[names(com) == "CS5"] <- "CS05"
names(com)[names(com) == "CS6"] <- "CS06"
names(com)[names(com) == "CS7"] <- "CS07"
names(com)[names(com) == "Cs8"] <- "CS08"
names(com)[names(com) == "CS9"] <- "CS09"
names(com)[names(com) == "Cs10"] <- "CS10"

code <- c(    "never"=1,
              "rarely"=2,
              "sometimes"=3,
              "often"=4,
              "always" =5)

com2 <- mutate(com, across(starts_with("CS"), ~unname(code[.])))

#write.csv(com2, "Processeddata/com_2.csv")

```

```{r descriptivrd}
desc <- data[,c(3, 5,6)]
## Recoding desc$Sex
desc$Sex <- fct_recode(desc$Sex,
  "Boy" = "male",
  "Girl" = "female"
)
colnames(desc) <- c("Gender", "Social Status", "Age")

des_tab <- desc %>%
  tbl_summary(
    by = Gender,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    type = list(Age ~ 'continuous'),
    digits = all_continuous() ~ 2,

    missing = "no"
    ) %>% add_overall() %>% bold_labels() %>% 
modify_header(label ~ "**Variable**")  %>%
  modify_caption("Demographic Characteristics") 
```

```{r gt-pic, include=F}
des_tab  %>%    # build gtsummary table
  as_gt() %>%             # convert to gt table
  gt::gtsave(             # save table as image
    filename = "Figures/demographics.png"
  )
```

```{r}
reliability <- psych::alpha(com2, check.keys = T)
```

```{r}

gt.data <- na.omit(com2)

#Creating long data
gt.data.long <- as.data.frame(gather(gt.data, Items, value))
gt.data.long$value <- as.numeric(as.character(gt.data.long$value))

gt.data.tab <- gt.data.long %>% 
  group_by(Items) %>% 
  # calculate summary stats & create data for the histogram and density plot
  dplyr::summarise(
    nr = n(),
    mean = mean(value, na.rm = TRUE),
    med = median(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    hist_data = list(value),
    dens_data = list(value),
    .groups = "drop"
  ) %>% 
  gt()

gt.likert <-  as.data.frame(gt.data)

#gt.likert <-  mutate(gt.likert, across(starts_with("ASQ"), ~unname(recod[.])))

gt.likert.Factor = as.data.frame(lapply(gt.likert,factor,
                                     ordered = T))

#get the items name
gt.items <- names(gt.likert.Factor ) 
#Calculate percentage
gt.percentage <- kutils::likert(gt.likert.Factor, vlist = gt.items )

gt.percentage <- gt.percentage$table %>% 
  as.data.frame(.)

#data wrangling
labels <- c("never", "rarely","sometimes", "often", "always","Total")
as.data.frame(labels)

full.percentage <- cbind(labels,gt.percentage) #tables with labels  
full.percentage<- t(full.percentage ) #transpose
as.data.frame(full.percentage)
full.percentage1 <- full.percentage[-1,-6] #removing 1st row and total column
#full.percentage2 <- full.percentage1[, c(3, 4, 1, 2,5)]# rearranging
as.data.frame(full.percentage1)

colnames(full.percentage1) <- c("Never", "Rarely","Sometimes", "Often", "Always")

Items <- rownames(full.percentage1)
as.data.frame(Items)
full.percentage3 <- cbind(Items,full.percentage1)

full.percentage3 <- full.percentage3[order(Items),] 
full.percentage3 <- as.data.frame(full.percentage3[,-1]) %>% 
  gt()

gt.table <- gt.data.tab$'_data'
gt.liket <- full.percentage3$"_data"
Table <-  cbind( gt.table, gt.liket )%>% 
  gt()%>% 
  # histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "grey",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "grey",
    bw = 0.75,
    same_limit = TRUE
  )%>%
  # format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
  # header
  tab_header(
    title = md("**Communication**"),
    subtitle = md("Summary Descriptives")
  ) %>% 
  tab_footnote(
    footnote = md("**Histogram**"),
    locations = cells_column_labels(columns = hist_data)
  ) %>%
  tab_footnote(
    footnote = md("**Density**"),
    locations = cells_column_labels(columns = dens_data)
  ) %>% 
  #create groups of columns
  tab_spanner(
    label = "Items",
    columns = Items
  ) %>%
  tab_spanner(
    label = "Summary Statistics",
    columns = nr:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  )  %>%
  # change column names to appear in the table
  cols_label(
    Items = ("Items"),
    nr = ("n"),
    mean = ("Mean"),
    med = ("Median "),
    sd = (("SD")),
    hist_data = "Histogram",
    dens_data = "Density"
  ) %>%

  tab_spanner(
    label = "Response Pattern",
    columns = "Never":"Always"
  ) %>%
  # set alignment as per wish
  cols_align(
    align = "center",
    columns = everything()
  ) %>%
  opt_align_table_header(align = "left") %>%
  gtExtras::gt_plt_dot(
    mean,
    Items,
    palette = "ggthemes::fivethirtyeight")%>%gtsave("Figures/communication.png",vwidth = 7000)

```

```{r}

apatheme=theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        #text=element_text(family = "Helvetica"),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        plot.title = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.title=element_blank(),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))

```

```{r EFAdata, include=FALSE}
### EFA data
EFA.data <- com2
#library(VIM)
missing <- VIM::aggr(EFA.data, plot =T)

```

```{r EFAassumptions, include=FALSE}

#KMO test
KMO <- psych::KMO(EFA.data)

# Test of correlation matrix
bartlet <- psych::cortest.bartlett(EFA.data, n =202)

#Histogram
#psych::multi.hist(EFA.data[,sapply(EFA.data, is.numeric)])

# Univariate normality

#creating normality function
shapiro_test_df <- function(df, bonf= TRUE, alpha= 0.05) {
  l <- lapply(df, shapiro.test)
  s <- do.call("c", lapply(l, "[[", 1))
  p <- do.call("c", lapply(l, "[[", 2))
  if (bonf == TRUE) {
    sig <- ifelse(p > alpha / length(l), "H0", "*")
  } else {
    sig <- ifelse(p > alpha, "H0", "*")
  }
  return(list(statistic= s,
              p.value= p,
              significance= sig,
              method= ifelse(bonf == TRUE, "Shapiro-Wilks test with Bonferroni Correction",
                             "Shapiro-Wilks test without Bonferroni Correction")))
}

Shapiro.efa <- shapiro_test_df(EFA.data)

efa.normality.tab = matrix(nrow = 48, ncol = 2)
rownameprefix <- "Item"
rownamesufix <- seq(1:48)
my.item.names <- paste(rownameprefix,rownamesufix, sep = "" )
rownames(efa.normality.tab) <- my.item.names
colnames(efa.normality.tab) <- c("statistic", "p")

efa.normality.tab[,1] <- apa(Shapiro.efa$statistic,2,T)
efa.normality.tab[,2] <- apa(Shapiro.efa$p.value,2,T)

efa.normalityprefix <- efa.normality.tab[,1]
efa.normalitysufix <- Shapiro.efa$significance
efa.normality.stat <- paste(efa.normalityprefix,efa.normalitysufix, sep = "" )

# Multivariate Normality
mardia <- psych::mardia(EFA.data, na.rm = T, plot =F)

# Descriptive Stats
Descriptives <- psych::describe(EFA.data)
alpha <- psych::alpha(EFA.data,check.keys=TRUE)
Item.total <- alpha$item.stats

Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), efa.normality.stat,  apa(Item.total$r.cor,2,T))

colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
rownameprefix <- "Item"
rownamesufix <- seq(1:48)
my.names <- paste(rownameprefix,rownamesufix, sep = "" )
rownames(Des.combined) = (my.names)
```

## Item Analysis
`

```{r Cronbach, results='asis', width = 60}
Cron.bach <- psych::alpha(EFA.data,check.keys=TRUE) 
Cron.bach$total %>% 
  knitr::kable(caption = "Alpha", digits = 2) %>% 
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F)
Cron.bach$alpha.drop %>% 
  knitr::kable(caption = "Alpha value if item is dropped", digits = 2) %>% 
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F)

Cron.bach$item.stats %>% 
  knitr::kable(caption = "Corrected Item total Correlation", digits = 2) %>% 
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F)

Cron.bach$item.stats$r.cor
low.r.corec <- (min(Cron.bach$item.stats$r.cor))  #minimum item total correlation
high.r.corec <- (max(Cron.bach$item.stats$r.cor))     # maximum item total correlation

```

```{r CorrMatrix, include=FALSE}
#Polychoric Correlation matrix

correlations <- psych::polychoric(EFA.data, correct = 0)
upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]

min.cor <- apa(min(abs(upper)),2,F) #minimum cor.coefficient of the matrix
max.cor <- apa(max(abs(upper)),2,F) # max. correlation coefficient of the matrix

determinets <- det(correlations$rho) 
# Calculating the percentage of correlations higher than .30

BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
totR = length(EFA.data)*(length(EFA.data)-1)/2
cor.per <- print (BigR/totR)*100
```

```{r figCor, out.height="150%",out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}

ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90,colors = c("red", "white", "blue") )
#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
#to show pvalue in the fig add p.mat=p.mat
```

```{r ParallelEFA, include=FALSE}

# Parallel analysis
Horn <- paran(EFA.data, iterations=500, centile=0, quietly=FALSE,
           status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
           color=TRUE, col=c("black","red","blue"),
           lty=c(1,2,3), lwd=1, legend=TRUE, 
           width=640, height=640, grdevice=png, seed=0, mat=NA, n=NA)

Adjusted.EV <- data.frame(Horn$AdjEv)
Adjusted.EV$type = c('Adjusted Ev')
Adjusted.EV$num = c(row.names(Adjusted.EV))
Adjusted.EV$num = as.numeric(Adjusted.EV$num)
colnames(Adjusted.EV) = c('eigenvalue', 'type', 'num')

Random.EV <- data.frame(Horn$RndEv)
Random.EV$type = c('Random EV')
Random.EV$num = c(row.names(Random.EV))
Random.EV$num = as.numeric(Random.EV$num)
colnames(Random.EV) = c('eigenvalue', 'type', 'num')

Unadjusted.EV <- data.frame(Horn$Ev)
Unadjusted.EV$type = c('Unadjusted EV')
Unadjusted.EV$num = c(row.names(Unadjusted.EV))
Unadjusted.EV$num = as.numeric(Unadjusted.EV$num)
colnames(Unadjusted.EV) = c('eigenvalue', 'type', 'num')

parallel = ggplot(Adjusted.EV, aes(x=num, y=eigenvalue, shape=type, color=type)) +
  #Add lines connecting data points
  geom_line()+
    geom_line(data = Random.EV) +
  geom_line(data = Unadjusted.EV)+
    #Add the data points.
  geom_point(size=1)+
  geom_point(data = Random.EV, size=1)+
  geom_point(data = Unadjusted.EV, size=1)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
   #Label the x-axis 'Factor Number', and ensure that it ranges from 1-max # of factors, increasing by one with each 'tick' mark.
  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
    #Add vertical line indicating parallel analysis suggested max # of factors to retain
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme

```

```{r ScreePlot, include=FALSE}
Scree <- scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
      hline=NULL,add=F)

FA.Scree <- data.frame(Scree$fv)
FA.Scree$type = c('Factor Analysis')
FA.Scree$num = c(row.names(FA.Scree))
FA.Scree$num = as.numeric(FA.Scree$num)
colnames(FA.Scree) = c('eigenvalue', 'type', 'num')

PA.Scree <- data.frame(Scree$pcv)
PA.Scree$type = c('Principal Component Analysis')
PA.Scree$num = c(row.names(PA.Scree))
PA.Scree$num = as.numeric(PA.Scree$num)
colnames(PA.Scree) = c('eigenvalue', 'type', 'num')

scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
   geom_line()+
  geom_line(data = PA.Scree)+ 
  geom_point(size=1)+
  geom_point(data = PA.Scree, size=1)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme 
```

```{r HullEFA, include=FALSE}
# HULL
EFA.MRFA::hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL) +xlab("Factor Number")+ylab("CAF")+ 
  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2")) 
```

```{r MAPefa, include=FALSE}
#MAP
psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =202 )
```

## Network graph
```{r Network Graph,message=FALSE, warning=FALSE, width = 60}
library(EGAnet)
library(sna)
EGA(correlations$rho, n= 150, plot.EGA = T, algorithm.args = list(steps = 10))
ega <-ggplot2::last_plot()
```

```{r facIdFig, out.height="250%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method' (D) Network Analysis,  warning=FALSE, results= 'asis'}
cowplot::plot_grid(parallel, scree.plot,Hull,ega, labels = "AUTO",ncol=1, label_size = 8,align = "v")

```

 ( Figure \@ref(fig:facIdFig)). Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterationsindicated a four factor solution. However, Scree plot, the minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a one-factor solution.

```{r EFA, include=FALSE}
fa.3F.1 <- fa(r=correlations$rho, nfactors = 3, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE)
AA <- print(fa.3F.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.3F.1 <- dplyr::select(EFA.data ,
                                    -c( CS21, CS13, CS10, CS19, CS03,CS09, CS05, CS23))

correlations.red.3F.1 <- polychoric(reduced.model.3F.1,correct = 0)

fa.3F.2 <- fa(r=correlations.red.3F.1$rho, nfactors = 3, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, max.iter = 100)

BB <- print(fa.3F.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.3F.2 <- dplyr::select(EFA.data ,
                                    -c( CS21, CS13, CS10, CS19, CS03,CS09, CS05, CS23, CS02, CS01,CS15,CS20,CS12))

correlations.red.3F.2 <- polychoric(reduced.model.3F.2,correct = 0)

fa.3F.3 <- fa(r=correlations.red.3F.2$rho, nfactors = 3, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, max.iter = 500 )

CC <- print(fa.3F.3, cut = .3, digits = 3, sort = TRUE)

var1 <- CC$Vaccounted[2,1]*100
var2 <- CC$Vaccounted[2,2]*100
var3 <- CC$Vaccounted[2,3]*100
var4 <- CC$Vaccounted[2,4]*100
var5 <- CC$Vaccounted[2,5]*100
```

```{r EFA2f, include=FALSE}
fa.2F.1 <- fa(r=correlations$rho, nfactors = 2, fm= "pa",rotate ="promax",
              residuals = TRUE, SMC = TRUE)
AA <- print(fa.2F.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.2F.1 <- dplyr::select(EFA.data ,
                                    -c( CS07, CS13, CS16, CS05, CS10, CS19, CS03, CS02, CS09, CS23))

correlations.red.2F.1 <- polychoric(reduced.model.2F.1)

fa.2F.2 <- fa(r=correlations.red.2F.1$rho, nfactors = 2, fm= "pa",rotate ="promax",
              residuals = TRUE, SMC = TRUE, max.iter = 100)

BB <- print(fa.2F.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.2F.2 <- dplyr::select(EFA.data ,
                                    -c( CS07, CS13, CS16, CS05, CS10, CS19, CS03, CS02, CS09, CS23, CS17, CS04))

correlations.red.2F.2 <- polychoric(reduced.model.2F.2)

fa.2F.3 <- fa(r=correlations.red.2F.2$rho, nfactors = 2, fm= "pa",rotate ="promax",
              residuals = TRUE, SMC = TRUE, max.iter = 500 )

CC <- print(fa.2F.3, cut = .3, digits = 3, sort = TRUE)

```

```{r samplesizeIRT, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='hide', width=60}
set.seed(222)
m <-  23 # item number
n <- c(50, 75, 100, 150, 200, 300, 350) # sample size
design <- as.data.frame(n)

irtGenerate <- function(condition, fixed_objects = FALSE) {
n <- condition$n

a <- matrix(rlnorm(m,.2,.3))
diffs <- t(apply(matrix(runif(m*4, .3, 1), m), 1, cumsum))
diffs <- -(diffs - rowMeans(diffs))
diffs<- diffs + rnorm(m)
d <- diffs
dat <- simdata(a, d, n, itemtype = 'graded')
return(dat)
}

irtAnalyze <- function(condition, dat, fixed_objects = NULL) {
mod <- mirt(dat, 1, itemtype = 'graded', verbose = FALSE)
simpars <- coef(mod, simplify = TRUE, digits = Inf)$items
irtpars <- c(a = simpars[,1], d = simpars[,2])
return(irtpars)
}

irtSummarize <- function(condition, results,
fixed_objects = NULL) {
apop <- fixed_objects['alpha', ]
dpop <- fixed_objects['d', ]
simrmse <- RMSE(results, c(apop, dpop))
out <- c(RMSE = simrmse)
return(out)
}

simres <- runSimulation(design, replications = 100,
parallel = TRUE, generate = irtGenerate,
analyse = irtAnalyze, summarise = irtSummarize,
packages = c('mirt'))
simres

colind <- grep(".a.", colnames(simres))
sima <- as.data.frame(simres[, colind])
nvec <- as.numeric(simres$n)

meanRMSE <- rowMeans(sima)
names(meanRMSE) <- n
round(meanRMSE, 2)
matplot(nvec, log(sima), type = "l", col = 1, lty = 1,
ylab = "log(RMSE)", xlab = "sample size",
main = "Graded Response Model", xaxt = "n")
axis(1, at = nvec)
```

To gather more information on our retained one-factor solution, we sought Item Response Theory (IRT). IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty. IRT judges an item's quality by providing item information in the light of participants' trait level ($\theta$). We gathered evidence on item quality as well as item fit, person fit and model by fitting a graded response model  in RStudio with the "mirt" package [@R-mirt]  [@R-mirt]. We did a Monte Carlo simulation using "SimDesign" package [@R-SimDesign]  with sample sizes varying from 50-350 and calculated average root mean squared error(RMSE) to estimate the optimal sample size for the graded response model with 23 items. The RMSE became stable for n = 200 to 300 (RMSE ranging between .25-.35). Our sample size within the estimated sample size for stability.

```{r}
fit <- mirt(EFA.data, model = 1, itemtype = 'graded', 
               SE = TRUE, Se.type = 'MHRM',
               technical = list(NCYCLES = 10000))

# Model Parameters ####
params <- coef(fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
items <- data.frame(params$items)
se <- coef(fit, printSE = TRUE)

# Model Fit (degrees of freedom too low to check model fit)
model <- M2(fit)

#Item fit
item.fit<- itemfit(fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
                                  impute=10)

#Identifying Missfit items based on RMSEA Value
item_misfits <- subset(item.fit, RMSEA.S_X2 >= .06)

# Person Fit ####

personfit <- personfit(fit) 
personfit_model_misfits <- subset(personfit, Zh < -2)
rownames(personfit_model_misfits)
nrow(personfit_model_misfits)
hist(personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
abline(v = -2, lwd = 2, lty = 2)

# Plots ####

OCC <- plot(fit, type = "trace", facet =T, main = "Communication Scale OCC")
info <- plot(fit, type = "infoSE", main = "Communication Scale")
iteminfo <- plot(fit, type = "infotrace", 
                    facet_items = T, main = "Communication Scale")

item1<- plot(fit, type = "infotrace", 
                    facet_items = T, which.items = 1,main = "")
item1<- plot(fit, type = "infotrace", 
                    facet_items = T, which.items = 1,main = "")
item1<- plot(fit, type = "infotrace", 
                    facet_items = T, which.items = 1,main = "")

#conditional reliability
reliability <- plot(fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )

marginal.rel <- marginal_rxx(fit)

#scale characteristics curve
scale <- plot(fit, type = 'score', theta_lim = c(-6, 6), main = "")

#-3<b<3
#.5<a<2; baker p12
```

```{r OCC, include=F}
ggicc <- function(model, item, theta){
  Theta <- matrix(seq(-theta,theta, by = .1))
  iteminfo <- mirt::extract.item(model, item)
  P <-mirt::probtrace(x=iteminfo , Theta=Theta  )
  icc <- data.frame(P = P, Theta = Theta)
  colnames(icc) <- c(paste("P", 1:ncol(P), sep=''), "Theta")
  icc2<- reshape(icc, direction='long', varying = paste("P", 1:ncol(P), sep=''), v.names = 'P',
                 times = paste("P", 1:ncol(P), sep=''))
  plot <- ggplot2::ggplot(icc2,aes(Theta,P, col =time))+geom_line()+xlab(expression(theta)) + 
    ylab(expression(P(theta)))+ theme(legend.title=element_blank())
  return(plot)

}

library(ggsci)

item01 <- ggicc(fit,1,6)+apatheme+ggtitle("item01")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item02 <- ggicc(fit,2,6)+apatheme+ggtitle("item02")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item03 <- ggicc(fit,3,6)+apatheme+ggtitle("item03")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item04 <- ggicc(fit,4,6)+apatheme+ggtitle("item04")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item05 <- ggicc(fit,5,6)+apatheme+ggtitle("item05")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item06 <- ggicc(fit,6,6)+apatheme+ggtitle("item06")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item07 <- ggicc(fit,7,6)+apatheme+ggtitle("item07")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item08 <- ggicc(fit,8,6)+apatheme+ggtitle("item08")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item09 <- ggicc(fit,9,6)+apatheme+ggtitle("item09")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item10 <- ggicc(fit,10,6)+apatheme+ggtitle("item10")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item11 <- ggicc(fit,11,6)+apatheme+ggtitle("item11")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
ggsave("Figures/ideal_icc.png",item11 , width = 12, height = 8, dpi = 600, bg = "white")

item12 <- ggicc(fit,12,6)+apatheme+ggtitle("item12")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item13 <- ggicc(fit,13,6)+apatheme+ggtitle("item013")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item14 <- ggicc(fit,14,6)+apatheme+ggtitle("item14")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item15 <- ggicc(fit,15,6)+apatheme+ggtitle("item15")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item16 <- ggicc(fit,16,6)+apatheme+ggtitle("item16")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item17 <- ggicc(fit,17,6)+apatheme+ggtitle("item17")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item18 <- ggicc(fit,18,6)+apatheme+ggtitle("item18")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item19 <- ggicc(fit,19,6)+apatheme+ggtitle("item19")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item20 <- ggicc(fit,20,6)+apatheme+ggtitle("item20")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item21 <- ggicc(fit,21,6)+apatheme+ggtitle("item21")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item22 <- ggicc(fit,22,6)+apatheme+ggtitle("item22")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

item23 <- ggicc(fit,23,6)+apatheme+ggtitle("item23")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))

ICC <- cowplot::plot_grid(item01, item02, item03, item04, item05, item06, item07, item08, item09,
                   item10, item11, item12, item13, item14, item15, item16, item17, item19,
                   item20, item21, item23,
                      labels = "AUTO",
                     ncol=4,  
                    label_size = 15, 
                     align = "v")

ggsave("Figures/ICC.png",ICC , width = 12, height = 12, dpi = 600, bg = "white")

problem.icc <- cowplot::plot_grid(item01, item02, item03,  item05, item08, item09,
                                  item10,  item13,  item16, item17,  item23,
                                  labels = "AUTO",
                                  ncol=4,  
                                  label_size = 15, 
                                  align = "v")

ggsave("Figures/problem.icc.png",problem.icc , width = 12, height = 8, dpi = 600, bg = "white")

good.icc <- cowplot::plot_grid( item04,  item06, item07,
                                item11, item12, item14, item15, item18, item19,
                               item20, item21, item22,
                                  labels = "AUTO",
                                  ncol=4,  
                                  label_size = 15, 
                                  align = "v")

ggsave("Figures/good.icc.png",good.icc , width = 12, height = 8, dpi = 600, bg = "white")

```

```{r item-plots, inclide =F}
pacman::p_load(reshape,ggsci)
Theta <- matrix(seq(-6,6, by = .1))

item1.extract<- extract.item(fit, 1)
item2.extract<- extract.item(fit, 2)
item3.extract<- extract.item(fit, 3)
item4.extract<- extract.item(fit, 4)
item5.extract<- extract.item(fit, 5)
item6.extract<- extract.item(fit, 6)
item7.extract<- extract.item(fit, 7)
item8.extract<- extract.item(fit, 8)
item9.extract<- extract.item(fit, 9)
item10.extract<-extract.item(fit, 10)
item11.extract<- extract.item(fit, 11)
item12.extract<- extract.item(fit, 12)
item13.extract<- extract.item(fit, 13)
item14.extract<- extract.item(fit, 14)
item15.extract<- extract.item(fit, 15)
item16.extract<- extract.item(fit, 16)
item17.extract<-extract.item(fit, 17)
item18.extract<- extract.item(fit, 18)
item19.extract<- extract.item(fit, 19)
item20.extract<- extract.item(fit, 20)
item21.extract<-extract.item(fit, 21)
item22.extract<- extract.item(fit, 22)
item23.extract<- extract.item(fit, 23)

item1 <- iteminfo(item1.extract, Theta)
item2 <- iteminfo(item2.extract, Theta)
item3 <- iteminfo(item3.extract, Theta)
item4 <- iteminfo(item4.extract, Theta)
item5 <- iteminfo(item5.extract, Theta)
item6 <- iteminfo(item6.extract, Theta)
item7 <- iteminfo(item7.extract, Theta)
item8 <- iteminfo(item8.extract, Theta)
item9 <- iteminfo(item9.extract, Theta)
item10 <- iteminfo(item10.extract, Theta)
item11 <- iteminfo(item11.extract, Theta)
item12 <- iteminfo(item12.extract, Theta)
item13 <- iteminfo(item13.extract, Theta)
item14 <- iteminfo(item14.extract, Theta)
item15 <- iteminfo(item15.extract, Theta)
item16 <- iteminfo(item16.extract, Theta)
item17 <- iteminfo(item17.extract, Theta)
item18 <- iteminfo(item18.extract, Theta)
item19 <- iteminfo(item19.extract, Theta)
item20 <- iteminfo(item20.extract, Theta)
item21 <- iteminfo(item21.extract, Theta)
item22 <- iteminfo(item22.extract, Theta)
item23 <- iteminfo(item23.extract, Theta)

info.data <- as.data.frame(cbind(item1, item2, item3,item4,item5,item6,item7,item8,item9,item10,
                                 item11,item12,item13,item14,item15,item16,item17,item18,item19,item20,
                                 item21,item22,item23))

item1.iic1 <- ggplot(info.data,aes(Theta,item1))+geom_line()+apatheme+
  ggtitle(" Item01")+theme(legend.position = "none")+ylim(0,.7)+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info

item2.iic1 <- ggplot(info.data,aes(Theta,item2))+geom_line()+apatheme+
  ggtitle(" Item02")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info

item3.iic1 <- ggplot(info.data,aes(Theta,item3))+geom_line()+apatheme+
  ggtitle(" Item03")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info

item4.iic1 <- ggplot(info.data,aes(Theta,item4))+geom_line()+apatheme+
  ggtitle(" Item04")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info

item5.iic1 <- ggplot(info.data,aes(Theta,item5))+geom_line()+apatheme+
  ggtitle(" Item05")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info

item6.iic1 <- ggplot(info.data,aes(Theta,item6))+geom_line()+apatheme+
  ggtitle(" Item06")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))

item7.iic1 <- ggplot(info.data,aes(Theta,item7))+geom_line()+apatheme+
  ggtitle(" Item07")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))

item8.iic1 <- ggplot(info.data,aes(Theta,item8))+geom_line()+apatheme+
  ggtitle(" Item08")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info

item9.iic1 <- ggplot(info.data,aes(Theta,item9))+geom_line()+apatheme+
  ggtitle(" Item09")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info

item10.iic1 <- ggplot(info.data,aes(Theta,item10))+geom_line()+apatheme+
  ggtitle(" Item10")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info

item11.iic1 <- ggplot(info.data,aes(Theta,item11))+geom_line()+apatheme+
  ggtitle(" Item11 ")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))

item12.iic1 <- ggplot(info.data,aes(Theta,item12))+geom_line()+apatheme+
  ggtitle(" Item12")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))

item13.iic1 <- ggplot(info.data,aes(Theta,item13))+geom_line()+apatheme+
  ggtitle(" Item13)")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info

item14.iic1 <- ggplot(info.data,aes(Theta,item14))+geom_line()+apatheme+
  ggtitle(" Item14")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))

item15.iic1 <- ggplot(info.data,aes(Theta,item15))+geom_line()+apatheme+
  ggtitle(" Item15 ")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))

item16.iic1 <- ggplot(info.data,aes(Theta,item16))+geom_line()+apatheme+
  ggtitle(" Item16")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info

item17.iic1 <- ggplot(info.data,aes(Theta,item17))+geom_line()+apatheme+
  ggtitle(" Item17")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info

item18.iic1 <- ggplot(info.data,aes(Theta,item18))+geom_line()+apatheme+
  ggtitle("Item18")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))

item19.iic1 <- ggplot(info.data,aes(Theta,item19))+geom_line()+apatheme+
  ggtitle(" Item19")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))

item20.iic1 <- ggplot(info.data,aes(Theta,item20))+geom_line()+apatheme+
  ggtitle(" Item20")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))

item21.iic1 <- ggplot(info.data,aes(Theta,item21))+geom_line()+apatheme+
  ggtitle(" Item21")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))

item22.iic1 <- ggplot(info.data,aes(Theta,item22))+geom_line()+apatheme+
  ggtitle(" Item22")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))

item23.iic1 <- ggplot(info.data,aes(Theta,item23))+geom_line()+apatheme+
  ggtitle(" Item23")+
  labs(y = "Item Information")+
  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info

ICC1 <- cowplot::plot_grid( item1.iic1, item2.iic1, item3.iic1, item4.iic1, item5.iic1, item8.iic1 ,  labels = "AUTO",ncol=2, label_size = 15,align = "v")
ggsave("Figures/ICC1.png",ICC1 , width = 12, height = 8, dpi = 600, bg = "white")

ICC2 <- cowplot::plot_grid( item9.iic1, item10.iic1, item13.iic1, item16.iic1, item17.iic1, item23.iic1 ,  labels = "AUTO",ncol=2, label_size = 15,align = "v")
ggsave("Figures/ICC2.png",ICC2 , width = 12, height = 8, dpi = 600, bg = "white")

ICC3 <- cowplot::plot_grid( item6.iic1, item7.iic1, item11.iic1, item12.iic1, item14.iic1, item15.iic1 ,  labels = "AUTO",ncol=2, label_size = 15,align = "v")
ggsave("Figures/ICC3.png",ICC3 , width = 12, height = 8, dpi = 600, bg = "white")

ICC4 <- cowplot::plot_grid( item18.iic1, item19.iic1, item20.iic1, item21.iic1, item22.iic1,  labels = "AUTO",ncol=2, label_size = 15,align = "v")
ggsave("Figures/ICC4.png",ICC4 , width = 12, height = 8, dpi = 600, bg = "white")

bad.info <- ICC1 <- cowplot::plot_grid( item1.iic1, item2.iic1, item3.iic1, item4.iic1, item5.iic1, item8.iic1 ,
                                        item9.iic1, item10.iic1, item13.iic1, item16.iic1, item17.iic1, item23.iic1 ,

                                        labels = "AUTO",ncol=3, 
                                        label_size = 15,align = "v")
ggsave("Figures/bad.info.png",bad.info, width = 12, height = 8, dpi = 600, bg = "white")

good.info <- cowplot::plot_grid( item6.iic1, item7.iic1, item11.iic1, item12.iic1, item14.iic1, item15.iic1 , item18.iic1, item19.iic1, item20.iic1, item21.iic1, item22.iic1, 
                                 labels = "AUTO",ncol=3, label_size = 15,align = "v")

ggsave("Figures/good.info.png",good.info, width = 12, height = 8, dpi = 600, bg = "white")

```

```{r IRT2, include}

irt.2 <- dplyr::select(EFA.data, -c(CS01,CS02,CS03,CS04, CS05,CS08, CS09, CS10, CS13, CS16, CS17,CS23))

fit2 <- mirt(irt.2, model = 1, itemtype = 'graded', 
               SE = TRUE, Se.type = 'MHRM',
               technical = list(NCYCLES = 10000))

occ <- plot(fit2, facet =T, type= "trace")

# Model Parameters ####
params2 <- coef(fit2, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
items2 <- data.frame(params2$items)
se2 <- coef(fit2, printSE = TRUE)

# Model Fit (degrees of freedom too low to check model fit)
model2 <- as.data.frame(M2(fit2))

#Item fit
item.fit2<- itemfit(fit2, fit_stats = c("S_X2",  "infit"),
                                  impute=10)

#Identifying Missfit items based on RMSEA Value
item_misfits2 <- subset(item.fit2, RMSEA.S_X2 >= .06)

## Creating IRT table
item.fit3 <- item.fit2[,-c(1,2,4)] 
colnames(item.fit3) <- c("Outfit", "Infit", "S-Chi-square", "df", "RMSEA", "p")

IRT.details <- cbind(items2 ,item.fit3)

IRT.details <- IRT.details %>% 
 dplyr::mutate_if(is.numeric, round, digits=3)

IRT.details <- tibble::rownames_to_column(IRT.details, "Items")
#write_csv(IRT.details, "table_raw/IRT_parameters.csv")

#-3<b<3
#.5<a<2; baker p12

mean.discrimination <- mean(IRT.details$a)
sd.discrimination <- sd(IRT.details$a)
range.descrimination <- range(IRT.details$a)

cat.prob <- IRT.details[,c(3:6)]
cat.prob.long <- reshape::melt(cat.prob)
range.difficulty <- range(cat.prob.long$value)

range.outfit <-  range(IRT.details$Outfit)
range.infit <-  range(IRT.details$Infit)
range.rmsea <- range(IRT.details$RMSEA)

# Person Fit ####
personfit2 <- personfit(fit2) 
personfit_model_misfits2 <- subset(personfit2, Zh < -2)
rownames(personfit_model_misfits2)
nrow(personfit_model_misfits2)

person <- ggplot(personfit2, aes(x=Zh)) + geom_histogram(binwidth=.5,col=I("black"),fill="palegreen4")+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics")+apatheme + xlim(-4,2)+
   scale_y_continuous(limits = c(0, 40), expand = expand_scale(mult = c(0, 0.1)))

annotation.1 <- data.frame(
   x = (-3.1),
   y = (20),
   label = ("Most of the participants
        are within the guidline")
)

per.anno <-person + geom_label(data=annotation.1, aes( x=x, y=y, label=label),                 , 
           color="orange", 
           size=5 , angle=45, fontface="bold" )

ggsave("Figures/person.png",per.anno , width = 12, height = 8, dpi = 600, bg = "white")

# Plots ####

OCC2 <- plot(fit2, type = "trace", facet =T, main = "Communication Scale OCC")
info2 <- plot(fit2, type = "infoSE", main = "Communication Scale")
iteminfo2 <- plot(fit2, type = "infotrace", 
                    facet_items = T, main = "Communication Scale")

##Test Info
info <- tabledown::ggtestinfo(irt.2, fit2)+apatheme+geom_line(colour = "black", size=1.5)+geom_area(fill ="palegreen4" )+geom_vline(xintercept = -3, colour ="black")+
  geom_vline(xintercept = .5, colour ="black")
library(plotly)
info.p <- plotly::ggplotly(info)

annotation <- data.frame(
   x = c(-4.2,1.5),
   y = c(4.5,4.3),
   label = c("Theta = -3", "Theta =.5")
)

info.anno <- info + geom_label(data=annotation, aes( x=x, y=y, label=label),
           color="orange", 
           size=7 , angle=45, fontface="bold" )

ggsave("Figures/TIC.png",info.anno  , width = 12, height = 8, dpi = 600, bg = "white")

#conditional reliability
library(latticeExtra)
library(directlabels)
font.settings <- list(
  font = 1,
  cex = 6,
  fontfamily = "sans")

apa.latice  <- list(
  par.xlab.text = font.settings,
  par.ylab.text = font.settings,
  axis.text = font.settings,
  sub.text = font.settings,
  add.text = font.settings)

reliability.focused <- plot(fit2, type = 'rxx', theta_lim = c(-4, 2), 
      main="Conditional Reliability Plot", par.settings=c(apa.latice),col.line = "#E69F00",lwd = 3.5 )

marginal.rel2 <- marginal_rxx(fit2)

#scale characteristics curve
scale2 <- plot(fit2, type = 'score', theta_lim = c(-6, 6), main = "")

```

```{r conrel-print, include=F}
##
png(filename="Figures/conrel.png", 
    type="cairo",
    units="in", 
    width=12, 
    height=8, 
    pointsize=12, 
    res=300)
plot(fit2, type = 'rxx', theta_lim = c(-6, 6), 
      main="", par.settings=c(apa.latice),col.line = "#E69F00",lwd = 3.5, cex =2.5 )+
  layer(panel.abline(v = -4, colour = "red",panel=panel.filled_smooth))+
  layer(panel.abline(v = 1.5))

dev.off()
```

Marginal reliability is based on the true score model (Lord & Novick, 1968) and is an estimate of the overall reliability of a test based on the average conditional standard errors. Often it is close in value to coefficient alpha (and sometimes it may even be identical). Alpha provides a lower estimate of marginal reliability.

```{r dif}
library("lordif")
DIF <- lordif(as.data.frame(irt.2), data$Sex, criterion = "Chisqr")
DIF$stats[,1:5]
plot(DIF)
```

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("references.bib")` for all our analyses.

# Results

# Discussion

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2022-01-30 Script/ICC.R

@@ -1,0 +1,58 @@
+data = foreign::read.spss("Raw/Test retest of communication scale.sav", to.data.frame=TRUE)
+
+
+code <- c(    "never"=1,
+              "rarely"=2,
+              "sometimes"=3,
+              "often"=4,
+              "always" =5)
+
+
+test.retest.1 <- mutate(data, across(starts_with("TCS"), ~unname(code[.])))
+test.retest.2 <- mutate(test.retest.1, across(starts_with("RCS"), ~unname(code[.])))
+
+
+test.retest <- test.retest.2 %>% 
+  rowwise() %>% 
+  mutate(test_total=sum(across(starts_with("TCS")), na.rm = T))
+
+
+
+test.retest <- test.retest %>% 
+  rowwise() %>% 
+  mutate(retest_total=sum(across(starts_with("RCS")), na.rm = T))
+
+
+
+icc <- as.data.frame(cbind(test.retest$test_total, test.retest$retest_total))
+
+
+psych::ICC(icc)
+
+
+
+library(irr)
+
+icc(icc, model = "twoway",
+    type =  "agreement", unit = "single", conf.level = 0.95)
+icc(icc, model = "twoway",
+    type =  "agreement", unit = "average", conf.level = 0.95)
+
+
+icc(icc, model = "oneway",
+    type =  "agreement", unit = "single", conf.level = 0.95)
+icc(icc, model = "oneway",
+    type =  "consistency", unit = "average", conf.level = 0.95)
+
+
+
+icc(icc, model = c("oneway", "twoway"),
+    type = c("consistency", "agreement"), unit = c("single", "average"),conf.level = 0.95)
+icc(icc, model = c("oneway", "twoway"),
+    type = c("consistency", "agreement"), unit = c("single", "average"),conf.level = 0.95)
+icc(icc, model = c("oneway", "twoway"),
+    type = c("consistency", "agreement"), unit = c("single", "average"),conf.level = 0.95)
+icc(icc, model = c("oneway", "twoway"),
+    type = c("consistency", "agreement"), unit = c("single", "average"),conf.level = 0.95)
+icc(icc, model = c("oneway", "twoway"),
+    type = c("consistency", "agreement"), unit = c("single", "average"),conf.level = 0.95)

### 2022-01-30 manuscript.Rmd
Complete analysis on 581 data Item remained 17

@@
 #tinytex::install_tinytex()
+renv::snapshot()
+```
+
+```{r library, eval=FALSE, include=FALSE}
+#This chunk holds code for calling the required packages
+
+library(papaja) # devtools::install_github("crsh/papaja")
+library(lavaan)
+library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
+library(semTools)
+library(MOTE)
+library(car)#reversecoding 
+library(psych)
+library(dlookr)
+library(plyr)
+library(tidyverse)
+library(qgraph)
+library(kableExtra)
+library(paran) # Parallel analysis
+library(EFA.MRFA) # Hull method
+library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
+library(DiagrammeRsvg) #For DiagrammeR
+library(rsvg) #For DiagrammeR
+library(ggcorrplot)
+library(semTable)
+library(magick)
+library(mirt)
+library(gtsummary)
+library(gt)
+library(gtExtras)
+library(likert)
+library(VIM) #Missing data
+library(kutils)
+library(simsem)
+library(tabledown)
+library(readxl)
+library(koRpus)# stable release
+library(koRpus.lang.en)
+library(reshape)
+library(ggsci)
+renv::snapshot()
+r_refs("references.bib")
 ```
@@
 ```{r data, include=F}
-data = foreign::read.spss("Raw/Validity construct.sav", to.data.frame=TRUE)
-
-write_csv(data, "Processeddata/part2.csv")
-
-## Recoding data$CS9 into data$CS9_rec
-data$CS9 <- fct_recode(data$CS9,
-  "always" = "always_duplicated_4"
-)
-
-## Recoding com$Cs1 into com$Cs1_rec
-data$Cs1 <- fct_recode(data$Cs1,
-  "rarely" = "Rarely"
-)
-
-## Recoding com$CS23 into com$CS23_rec
-data$CS23 <- fct_recode(data$CS23,
-  "never" = "Never",
-  "rarely" = "Rarely"
-)
-
-com <- data[,7:29]
-
-names(com)[names(com) == "Cs1"] <- "CS01"
-names(com)[names(com) == "Cs2"] <- "CS02"
-names(com)[names(com) == "CS3"] <- "CS03"
-names(com)[names(com) == "CS4"] <- "CS04"
-names(com)[names(com) == "CS5"] <- "CS05"
-names(com)[names(com) == "CS6"] <- "CS06"
-names(com)[names(com) == "CS7"] <- "CS07"
-names(com)[names(com) == "Cs8"] <- "CS08"
-names(com)[names(com) == "CS9"] <- "CS09"
-names(com)[names(com) == "Cs10"] <- "CS10"
-
-code <- c(    "never"=1,
-              "rarely"=2,
-              "sometimes"=3,
-              "often"=4,
-              "always" =5)
-
-com2 <- mutate(com, across(starts_with("CS"), ~unname(code[.])))
-
-#write.csv(com2, "Processeddata/com_2.csv")
-
-```
-
-```{r descriptivrd}
+# data <- readxl::read_excel("Processeddata/communication_data_n_582.xlsx")
+# readr::write_rds(data, "Processeddata/communication_data_n_582.rds")
+data <- readr::read_rds("Processeddata/communication_data_n_582.rds")
+
+efa.data.full <- subset(data, Sample == "EFA")
+cfa.data.full <- subset(data, Sample == "CFA"| Sample=="Validity")
+validity.data.full <- subset(data, Sample == "Validity")
+
+sem.data <- data[,c(2,6:66)]
+efa.data <- subset(sem.data , Sample == "EFA")
+efa.data <- efa.data[,c(2:24)]
+efa.data <- na.omit(efa.data)
+
+cfa.data<- subset(sem.data , Sample == "CFA"| Sample=="Validity")
+cfa.data <- cfa.data[,c(2:24)]
+cfa.data <- na.omit(cfa.data)
+
+validity.data <- subset(sem.data , Sample == "Validity")
+validity.data <-na.omit(validity.data)
+
+irt.data <- sem.data[,2:24]
+
+```
+
+```{r descriptivrd, eval=FALSE, include=FALSE}
 desc <- data[,c(3, 5,6)]
@@
 ```{r}
+
+```
+
+```{r}
 reliability <- psych::alpha(com2, check.keys = T)
@@
 
-gt.data <- na.omit(com2)
+gt.data <- na.omit(efa.data)
+
+names(gt.data)[names(gt.data) == "RCS02"] <- "CS02"
+names(gt.data)[names(gt.data) == "RCS05"] <- "CS05"
 
@@
 #get the items name
-gt.items <- names(gt.likert.Factor ) 
+gt.items <- names(gt.likert.Factor) 
 #Calculate percentage
@@
 full.percentage3 <- full.percentage3[order(Items),] 
-full.percentage3 <- as.data.frame(full.percentage3[,-1]) %>% 
+full.percentage3 <- as.data.frame(full.percentage3[,-1])
+
+full.percentage3 <- full.percentage3%>% 
   gt()
@@
 gt.liket <- full.percentage3$"_data"
+
 Table <-  cbind( gt.table, gt.liket )%>% 
@@
     line_color = "black", 
-    fill_color = "grey",
+    fill_color = "#00A08799",
     bw = 1,
@@
     line_color = "black", 
-    fill_color = "grey",
+    fill_color = "#E64B3599",
     bw = 0.75,
@@
     Items,
-    palette = "ggthemes::fivethirtyeight")%>%gtsave("Figures/communication.png",vwidth = 7000)
-
-```
-
-```{r}
-
+    palette = "ggthemes::fivethirtyeight")
+
+gtsave(Table, "Figures/efa_communication.png",vwidth = 7000)
+
+```
+
+```{r ggplot2, include=F}
+#This chunk holds code for creating ggplot2 based apatheme for plots.
 apatheme=theme_bw()+
@@
 ```{r EFAdata, include=FALSE}
-### EFA data
-EFA.data <- com2
+
 #library(VIM)
-missing <- VIM::aggr(EFA.data, plot =T)
+missing <- VIM::aggr(efa.data, plot =T)
 
@@
 #KMO test
-KMO <- psych::KMO(EFA.data)
+KMO <- psych::KMO(efa.data)
 
 # Test of correlation matrix
-bartlet <- psych::cortest.bartlett(EFA.data, n =202)
+bartlet <- psych::cortest.bartlett(efa.data, n =300)
 
@@
 
-Shapiro.efa <- shapiro_test_df(EFA.data)
+Shapiro.efa <- shapiro_test_df(efa.data)
 
@@
 # Multivariate Normality
-mardia <- psych::mardia(EFA.data, na.rm = T, plot =F)
+mardia <- psych::mardia(efa.data, na.rm = T, plot =F)
 
@@
 rownames(Des.combined) = (my.names)
+
+decriptives <- tabledown::des.tab(efa.data)
 ```
@@
 ```{r Cronbach, results='asis', width = 60}
-Cron.bach <- psych::alpha(EFA.data,check.keys=TRUE) 
+Cron.bach <- psych::alpha(efa.data,check.keys=TRUE) 
 Cron.bach$total %>% 
@@
 
-Cron.bach$item.stats$r.cor
 low.r.corec <- (min(Cron.bach$item.stats$r.cor))  #minimum item total correlation
@@
 
-correlations <- psych::polychoric(EFA.data, correct = 0)
+correlations <- psych::polychoric(efa.data)
 upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]
@@
 BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
-totR = length(EFA.data)*(length(EFA.data)-1)/2
+totR = length(efa.data)*(length(efa.data)-1)/2
 cor.per <- print (BigR/totR)*100
@@
 
-```{r figCor, out.height="150%",out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}
-
-ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
-           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90,colors = c("red", "white", "blue") )
+```{r corplot, include =F}
+#This chunk holds code for plotting the correlation matrix
+
+corplot <- ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
+           ggtheme = ggplot2::theme_minimal(),tl.srt = 90,colors = c("#E64B35FF", "white", "#3C5488FF") )+
+  theme( panel.grid.major = element_blank(),
+         axis.text.x = element_text(size = 8),
+         axis.text.y = element_text(size = 8),
+         panel.border = element_rect(color = "black",
+                                    fill = NA,
+                                    size = 1))
 #p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
 #to show pvalue in the fig add p.mat=p.mat
+ggsave("Figures/corplot.png",corplot, width = 6, height = 6, dpi = 600, bg ="white")
+
+```
+
+(ref:figCor) Inter item polychoric correlation coefficients for the 48 items. 4.9 % inter-item correlation coefficients were higher than .30
+
+```{r figCor, out.height="150%",out.width="100%", fig.align= 'center', fig.cap='(ref:figCor)', results='asis', fig.align='center'}
+
+knitr::include_graphics('Figures/corplot.png', dpi =600)
+
 ```
@@
 ```{r ParallelEFA, include=FALSE}
-
+#This chunk holds code for factor identification method : Horn
 # Parallel analysis
-Horn <- paran(EFA.data, iterations=500, centile=0, quietly=FALSE,
+Horn <- paran(correlations$rho, iterations=500, centile=0, quietly=FALSE,
            status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
@@
   #Add lines connecting data points
-  geom_line()+
-    geom_line(data = Random.EV) +
-  geom_line(data = Unadjusted.EV)+
+  geom_line(colour ='#DC000099')+
+    #geom_line(data = Random.EV) +
+  #geom_line(data = Unadjusted.EV)+
     #Add the data points.
-  geom_point(size=1)+
-  geom_point(data = Random.EV, size=1)+
-  geom_point(data = Unadjusted.EV, size=1)+
-  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
+  geom_point(size=1.5,colour ='#3C5488FF')+
+  #geom_point(data = Random.EV, size=3)+
+  #geom_point(data = Unadjusted.EV, size=3)+
+  scale_y_continuous(name="Eigen Value", limits=c(0, 4), breaks=seq(0,4,1)) +
    #Label the x-axis 'Factor Number', and ensure that it ranges from 1-max # of factors, increasing by one with each 'tick' mark.
-  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
+  scale_x_continuous(name='Factor Number (Parallel Analysis)', limits=c(0, 23),breaks=seq(0,23,4))+
     #Add vertical line indicating parallel analysis suggested max # of factors to retain
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme
+  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(,legend.position = "None") 
+#text = element_text(size = 25)
 
@@
 ```{r ScreePlot, include=FALSE}
+
+#This chunk holds code for factor identification method : Scree Plot
+
 Scree <- scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
@@
 
-scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
-   geom_line()+
-  geom_line(data = PA.Scree)+ 
-  geom_point(size=1)+
-  geom_point(data = PA.Scree, size=1)+
-  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
-  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme 
+scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=tye, shape=type))+
+   geom_line(colour ='#DC000099')+
+  #geom_line(data = PA.Scree)+ 
+  geom_point(size=1.5,colour ='#3C5488FF')+
+  #geom_point(data = PA.Scree, size=3)+
+  scale_y_continuous(name="Eigen Value", limits=c(0, 5), breaks=seq(0,5,1)) +
+  scale_x_continuous(name='Factor Number (Scree Plot)', limits=c(0, 20),breaks=seq(0,20,4))+
+  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(legend.position = "None") 
+#text = element_text(size = 25
+
 ```
@@
 ```{r HullEFA, include=FALSE}
+#This chunk holds code for factor identification method : Hull
+
 # HULL
-EFA.MRFA::hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
+EFA.MRFA::hullEFA(efa.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
         details = TRUE)
 hull <- ggplot2::last_plot()
-Hull <- hull+ ggtitle(NULL) +xlab("Factor Number")+ylab("CAF")+ 
-  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2")) 
+Hull <- hull+ ggtitle(NULL)+xlab("Factor Number (Hull Method)")+ylab("CAF")+ aes(color = '#DC000099')+geom_point(color ='#3C5488FF',size =1)+
+  apatheme +theme(legend.position = "None") +scale_fill_identity()
+
 ```
@@
 ```{r MAPefa, include=FALSE}
+#This chunk holds code for factor identification method : MAP
 #MAP
-psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =202 )
-```
-
-## Network graph
-```{r Network Graph,message=FALSE, warning=FALSE, width = 60}
-library(EGAnet)
-library(sna)
-EGA(correlations$rho, n= 150, plot.EGA = T, algorithm.args = list(steps = 10))
-ega <-ggplot2::last_plot()
-```
-
-```{r facIdFig, out.height="250%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method' (D) Network Analysis,  warning=FALSE, results= 'asis'}
-cowplot::plot_grid(parallel, scree.plot,Hull,ega, labels = "AUTO",ncol=1, label_size = 8,align = "v")
-
-```
-
- ( Figure \@ref(fig:facIdFig)).
-Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterationsindicated a four factor solution.
-However, Scree plot, the minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a one-factor solution.
+map <- psych::VSS(efa.data, rotate = "promax", fm = 'pa', n.obs =300 )
+map.map <- as.data.frame(map$map)
+colnames(map.map) <- "MAP Statistic"
+map.statistics <- map$vss.stats[,c(1,2,5,6,7,10,11)]
+full.map <- cbind(map.map,map.statistics)
+
+write.csv(full.map, "Table_raw/map_stat.csv")
+```
+Scree plot, map and hull method ( Figure \@ref(fig:facIdFig)) suggested a one factor solution.
+Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations  indicated a two-factor solution.
+However, the minimum average partial (MAP) method (Table \@ref(tab:factormp)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution.
+As a result, we tested both five-factor and six-factor solutions.
+```{r factors, include=F}
+#This chunk holds code for compiled factor identification plots
+
+factor <- cowplot::plot_grid(parallel, scree.plot,Hull, 
+                   labels = "AUTO",
+                   ncol=1, 
+                  align = "v", 
+                  label_fontfamily = "sans",
+                  label_fontface = "plain")
+ggsave("Figures/factors.png",factor, width = 5, height = 7, dpi = 600)
+```
+
+(ref:facIdFig) Factor Identification Methods (A) Parallel analysis  indicated the optimal number of factors were two.
+(B) Scree plot suggested One facor.
+(C) Hull method indicated 1 factors were required to balance the model fit and number of parameters.
+
+```{r facIdFig, fig.align= 'center', fig.cap='(ref:facIdFig)',  warning=FALSE, results= 'asis'}
+
+knitr::include_graphics("Figures/factors.png", dpi =800)
+
+```
 
 ```{r EFA, include=FALSE}
-fa.3F.1 <- fa(r=correlations$rho, nfactors = 3, fm= "pa",rotate ="varimax",
+fa.2F.1 <- fa(r=correlations$rho, nfactors = 2, fm= "pa",rotate ="varimax",
               residuals = TRUE, SMC = TRUE)
-AA <- print(fa.3F.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.3F.1 <- dplyr::select(EFA.data ,
-                                    -c( CS21, CS13, CS10, CS19, CS03,CS09, CS05, CS23))
-
-correlations.red.3F.1 <- polychoric(reduced.model.3F.1,correct = 0)
-
-fa.3F.2 <- fa(r=correlations.red.3F.1$rho, nfactors = 3, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, max.iter = 100)
-
-BB <- print(fa.3F.2, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.3F.2 <- dplyr::select(EFA.data ,
-                                    -c( CS21, CS13, CS10, CS19, CS03,CS09, CS05, CS23, CS02, CS01,CS15,CS20,CS12))
-
-correlations.red.3F.2 <- polychoric(reduced.model.3F.2,correct = 0)
-
-fa.3F.3 <- fa(r=correlations.red.3F.2$rho, nfactors = 3, fm= "pa",rotate ="varimax",
+AA <- print(fa.2F.1, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.2F.1 <- dplyr::select(efa.data ,
+                                    -c( CS21, CS11, CS23, CS09, RCS02,RCS05, CS16, CS01))
+
+correlations.red.2F.1 <- polychoric(reduced.model.2F.1)
+
+fa.2F.2 <- fa(r=correlations.red.2F.1$rho, nfactors = 2, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE)
+
+BB <- print(fa.2F.2, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.2F.2 <- dplyr::select(efa.data ,
+                                    -c( CS21, CS11, CS23, CS09, RCS02,RCS05, CS16, CS01, CS03))
+
+correlations.red.2F.2 <- polychoric(reduced.model.2F.2)
+
+fa.2F.3 <- fa(r=correlations.red.2F.2$rho, nfactors = 2, fm= "pa",rotate ="varimax",
               residuals = TRUE, SMC = TRUE, max.iter = 500 )
 
-CC <- print(fa.3F.3, cut = .3, digits = 3, sort = TRUE)
+CC <- print(fa.2F.3, cut = .3, digits = 3, sort = TRUE)
 
@@
 var2 <- CC$Vaccounted[2,2]*100
-var3 <- CC$Vaccounted[2,3]*100
-var4 <- CC$Vaccounted[2,4]*100
-var5 <- CC$Vaccounted[2,5]*100
+
+omega <- psych::omega(reduced.model.2F.2,2)
+
 ```
@@
 ```{r EFA2f, include=FALSE}
-fa.2F.1 <- fa(r=correlations$rho, nfactors = 2, fm= "pa",rotate ="promax",
+fa.1F.1 <- fa(r=correlations$rho, nfactors = 1, fm= "pa",
               residuals = TRUE, SMC = TRUE)
-AA <- print(fa.2F.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.2F.1 <- dplyr::select(EFA.data ,
-                                    -c( CS07, CS13, CS16, CS05, CS10, CS19, CS03, CS02, CS09, CS23))
-
-correlations.red.2F.1 <- polychoric(reduced.model.2F.1)
-
-fa.2F.2 <- fa(r=correlations.red.2F.1$rho, nfactors = 2, fm= "pa",rotate ="promax",
-              residuals = TRUE, SMC = TRUE, max.iter = 100)
-
-BB <- print(fa.2F.2, cut = .3, digits = 3, sort = TRUE)
+AA <- print(fa.1F.1, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.1F.1 <- dplyr::select(efa.data ,
+                                    -c( CS16, RCS02, RCS05, CS01, CS09, CS23))
+
+correlations.red.1F.1 <- polychoric(reduced.model.1F.1)
+
+fa.1F.2 <- fa(r=correlations.red.1F.1$rho, nfactors = 1, fm= "pa",
+              residuals = TRUE, SMC = TRUE)
+
+BB <- print(fa.1F.2, cut = .3, digits = 3, sort = TRUE)
 
@@
 CC <- print(fa.2F.3, cut = .3, digits = 3, sort = TRUE)
+
+```
+
+```{r CFAitems, include=FALSE }
+#This chunk holds codes for 1st CFA
+
+model.1 <- "Communication =~ CS15 + CS21 +CS11 + CS20+ CS14+ CS19+ CS22+ CS12+ CS06+ CS07+ CS18+ CS08+        CS04+CS17+CS03+CS13+CS10"
+
+fit.1 <- cfa(model.1, data = cfa.data, ordered = names(cfa.data),estimator = "WLSMV")
+
+## Summary of Model 
+cfa.sum.1 <- summary(fit.1, fit.measures =TRUE,standardized = TRUE,rsq =TRUE)
+
+## Selected Fit measures 
+fit.measures.1 <- fitmeasures (fit.1,c("gfi", "agfi", "nfi","rfi", 
+                       "cfi","tli",
+                       "rmsea", "rmsea.ci.lower", "rmsea.ci.upper","srmr"))
+
+reliability1 <- semTools::reliability(fit.1)
+
+```
+
+```{r mod1, eval=FALSE, include=FALSE}
+#This chunk holds codes for modification indices for 1st CFA
+modfit.Cor.one <- modindices(fit.Cor.1, sort. = TRUE) 
+modfit.Cor.one[modfit.Cor.one$mi>3.84,]
+```
+
+```{r cfaplot, include =F}
+#This chunk holds codes to store CFA plot
+
+png(filename="Manuscript.figures/CFAplot.png", 
+    type="cairo",
+    units="in", 
+    width=12, 
+    height=12, 
+    pointsize=12, 
+    res=1200)
+semPaths (fit.1 , 
+          what= "std",
+          #"hide", #(hides coefficeits)
+          #whatLabels = "std",
+          intercepts = F,
+          style ="OpenMx",
+          #residScale = 6,
+          theme = "colorblind",
+          nCharNodes = 0,
+          reorder =T,
+          rotation =2,
+          layout ="tree",
+          cardinal = T,
+          curvePivot =T,
+          sizeMan =8,#items length
+          sizeMan2 = 2,#items
+          sizeLat = 12,#factors
+          thresholds = FALSE,
+          equalizeManifests =F,
+          fade = FALSE,
+          edge.label.cex = .8,
+          #exoCov = T,
+          centerLevels = T,
+          #edge.color="black",
+          label.scale=T,
+          label.cex=1.2, #Font of factor and item name
+          residuals=FALSE,
+           #exoVar=FALSE,
+          #fixedStyle=6, #Style of arrow (guide item)
+          #freeStyle=1#Style of arrow (other item), #XKCD = TRUE
+
+          )
+
+dev.off()
+```
+
+```{r Shortcut Invariance}
+invariance.data <- cfa.data.full[, c(3, 6:28)]
+invariance.data <- na.omit(invariance.data )
+library("semTools")
+invariance.model <- measurementInvariance(model = model.1,
+                                          data = invariance.data,
+                                          group = "Gender",                                                                         estimator = "WLSMV",
+                                          strict = T)
+invariance.model[[1]] #configural Invariance
+invariance.model[[2]] # loading, weak, metric
+invariance.model[[3]] # intercept, strong, scaler
+invariance.model[[4]] # residual, strict
+invariance.model[[5]] # means, structural invariance
+```
+
+```{r figcfa, fig.cap = "Five Factor  Model of LEBA obtained by Confirmatory Factor Analysis.
+By allowing item pair 41 and 30 to covary their error variance our model attained the best fit.",  out.height='100%', warning=FALSE}
+
+knitr::include_graphics("Figures/CFAplot.png", dpi =600)
+
+```
+
+## Measurement Invariance
+```{r InvarianceAnalysis_data, include=FALSE}
+#This chunk holds codes to prepare measurement invariance data.
+
+invariance.data <- cfa.data.full[, c(3, 6:28)]
+invariance.data <- na.omit(invariance.data )
+mi.count <- invariance.data %>% 
+  group_by(Gender) %>% 
+  count() %>% 
+  as.data.frame()
+```
+
+```{r Invariancedetail, include=FALSE}
+#This chunk holds codes for measurement Invariance
+
+model.1 <- "Communication =~ CS15 + CS21 +CS11 + CS20+ CS14+ CS19+ CS22+ CS12+ CS06+ CS07+ CS18+ CS08+        CS04+CS17+CS03+CS13+CS10"
+
+# Configural invariance ####
+configural <- cfa(model = model.1,
+                  data = invariance.data,
+                  group = "Gender",
+                  estimator = "WLSMV")
+
+summary(configural, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+
+fitmeasures (configural,c("gfi", "agfi", "nfi","rfi", 
+                       "cfi","tli",
+                       "rmsea", "rmsea.ci.lower", "rmsea.ci.upper","srmr"))
+
+#Metric
+weak <- cfa(model = model.1,
+                  data = invariance.data,
+                  group = "Gender",
+
+                  estimator = "WLSMV", 
+            group.equal = "loadings")
+
+summary(weak, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+
+fitmeasures (weak,c("gfi", "agfi", "nfi","rfi", 
+                       "cfi.scaled","tli.scaled",
+                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
+
+First.comp <- compareFit (configural, weak)
+summary(First.comp)
+
+#Scaler
+strong <- cfa(model = model.1,
+                  data = invariance.data,
+                  group = "Gender",
+
+                  estimator = "WLSMV", 
+              group.equal = c("loadings", "intercepts"))
+summary(strong, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+
+Second.comp <- compareFit  (weak, strong)
+summary(Second.comp)
+
+#residual
+strict <- cfa(model = model.1,
+                  data = invariance.data,
+                  group = "Gender",
+
+                  estimator = "WLSMV",  
+              group.equal = c("loadings", "intercepts", "residuals"))
+
+summary(strict, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+residual.fitm <- as.data.frame(fitmeasures (strict,c("gfi", "agfi", "nfi","rfi", "cfi","tli","rmsea", "srmr","aic")))
+
+Third.comp <- compareFit(strict,strong)
+summary(Third.comp)
+#structural
+structural <-cfa(model = model.1,
+                  data = invariance.data,
+                  group = "Gender",
+
+                  estimator = "WLSMV",  
+                 group.equal = c("loadings", "intercepts", "residuals", "means","lv.variances","lv.covariances"))
+
+summary(structural, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+fitmeasures (structural,c("gfi", "agfi", "nfi","rfi", "cfi","tli","rmsea", "srmr","aic"))
+
+fourth.comp <- compareFit  (structural,strict)
+summary(fourth.comp)
+comfit.par <- compareFit(configural, weak, strong, strict)
+summary (comfit.par)
+
+models <-  list("Configural" = configural, 
+                "Metric" = weak, 
+                "Scalar" = strong, 
+                "Residual" = strict)
+
+Invariance.table <- compareLavaan(models,
+              nesting = "Configural > Metric > Scalar > Residual", 
+              fitmeas = c("chisq", "df",  "cfi","tli","rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr" ),
+              scaled = F,
+              chidif = T, digits = 2)
+
+colnames(Invariance.table) <- c("Chi-Square", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper", "Chi-Square Difference", "df difference*", "p")
+
+```
+
+```{r InvarianceTab, results='asis'}
+apa_table(Invariance.table, align = "c",  caption = "Measurment Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; * =  df of model comparison", landscape = T, font_size = "footnotesize" )
 
@@
 ```{r}
-fit <- mirt(EFA.data, model = 1, itemtype = 'graded', 
+irt.data <- na.omit(irt.data)
+irt.data <- irt.data %>% 
+  dplyr::select( CS03, CS04, CS06, CS07,CS08,CS10,CS11,    CS12, 
+                 CS13,CS14,CS15,CS17, CS18, CS19, CS20 ,CS21, CS22)
+
+fit <- mirt(irt.data, model = 1, itemtype = 'graded', 
                SE = TRUE, Se.type = 'MHRM',
@@
                     facet_items = T, main = "Communication Scale")
-
-item1<- plot(fit, type = "infotrace", 
-                    facet_items = T, which.items = 1,main = "")
-item1<- plot(fit, type = "infotrace", 
-                    facet_items = T, which.items = 1,main = "")
-item1<- plot(fit, type = "infotrace", 
-                    facet_items = T, which.items = 1,main = "")
 
@@
 
-item01 <- ggicc(fit,1,6)+apatheme+ggtitle("item01")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item02 <- ggicc(fit,2,6)+apatheme+ggtitle("item02")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item03 <- ggicc(fit,3,6)+apatheme+ggtitle("item03")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item04 <- ggicc(fit,4,6)+apatheme+ggtitle("item04")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item05 <- ggicc(fit,5,6)+apatheme+ggtitle("item05")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item06 <- ggicc(fit,6,6)+apatheme+ggtitle("item06")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item07 <- ggicc(fit,7,6)+apatheme+ggtitle("item07")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item08 <- ggicc(fit,8,6)+apatheme+ggtitle("item08")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item09 <- ggicc(fit,9,6)+apatheme+ggtitle("item09")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item10 <- ggicc(fit,10,6)+apatheme+ggtitle("item10")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item11 <- ggicc(fit,11,6)+apatheme+ggtitle("item11")+apatheme+scale_color_npg()+
+item03 <- ggicc(fit,1,6)+apatheme+ggtitle("item03")+apatheme+scale_color_npg()+
+  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
+
+item04 <- ggicc(fit,2,6)+apatheme+ggtitle("item04")+apatheme+scale_color_npg()+
+  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
+
+item06 <- ggicc(fit,3,6)+apatheme+ggtitle("item06")+apatheme+scale_color_npg()+
+  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
+
+item07 <- ggicc(fit,4,6)+apatheme+ggtitle("item07")+apatheme+scale_color_npg()+
+  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
+
+item08 <- ggicc(fit,5,6)+apatheme+ggtitle("item08")+apatheme+scale_color_npg()+
+  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
+
+item10 <- ggicc(fit,6,6)+apatheme+ggtitle("item10")+apatheme+scale_color_npg()+
+  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
+
+item11 <- ggicc(fit,7,6)+apatheme+ggtitle("item11")+apatheme+scale_color_npg()+
   scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
@@
 
-item12 <- ggicc(fit,12,6)+apatheme+ggtitle("item12")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item13 <- ggicc(fit,13,6)+apatheme+ggtitle("item013")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item14 <- ggicc(fit,14,6)+apatheme+ggtitle("item14")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item15 <- ggicc(fit,15,6)+apatheme+ggtitle("item15")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item16 <- ggicc(fit,16,6)+apatheme+ggtitle("item16")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item17 <- ggicc(fit,17,6)+apatheme+ggtitle("item17")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item18 <- ggicc(fit,18,6)+apatheme+ggtitle("item18")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item19 <- ggicc(fit,19,6)+apatheme+ggtitle("item19")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item20 <- ggicc(fit,20,6)+apatheme+ggtitle("item20")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item21 <- ggicc(fit,21,6)+apatheme+ggtitle("item21")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item22 <- ggicc(fit,22,6)+apatheme+ggtitle("item22")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-item23 <- ggicc(fit,23,6)+apatheme+ggtitle("item23")+apatheme+scale_color_npg()+
-  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-
-ICC <- cowplot::plot_grid(item01, item02, item03, item04, item05, item06, item07, item08, item09,
-                   item10, item11, item12, item13, item14, item15, item16, item17, item19,
-                   item20, item21, item23,
+item12 <- ggicc(fit,8,6)+apatheme+ggtitle("item12")+apatheme+scale_color_npg()+
+  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
+
+item13 <- ggicc(fit,9,6)+apatheme+ggtitle("item013")+apatheme+scale_color_npg()+
+  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
+
+item14 <- ggicc(fit,10,6)+apatheme+ggtitle("item14")+apatheme+scale_color_npg()+
+  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
+
+item15 <- ggicc(fit,11,6)+apatheme+ggtitle("item15")+apatheme+scale_color_npg()+
+  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
+
+item17 <- ggicc(fit,12,6)+apatheme+ggtitle("item17")+apatheme+scale_color_npg()+
+  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
+
+item18 <- ggicc(fit,13,6)+apatheme+ggtitle("item18")+apatheme+scale_color_npg()+
+  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
+
+item19 <- ggicc(fit,14,6)+apatheme+ggtitle("item19")+apatheme+scale_color_npg()+
+  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
+
+item20 <- ggicc(fit,15,6)+apatheme+ggtitle("item20")+apatheme+scale_color_npg()+
+  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
+
+item21 <- ggicc(fit,16,6)+apatheme+ggtitle("item21")+apatheme+scale_color_npg()+
+  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
+
+item22 <- ggicc(fit,17,6)+apatheme+ggtitle("item22")+apatheme+scale_color_npg()+
+  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
+
+ICC <- cowplot::plot_grid(item03, item04, item06, item07, item08, 
+                   item10, item11, item12, item13, item14, item15,  item17, item19,
+                   item20, item21, 
                       labels = "AUTO",
@@
 
-problem.icc <- cowplot::plot_grid(item01, item02, item03,  item05, item08, item09,
-                                  item10,  item13,  item16, item17,  item23,
-                                  labels = "AUTO",
-                                  ncol=4,  
-                                  label_size = 15, 
-                                  align = "v")
-
-ggsave("Figures/problem.icc.png",problem.icc , width = 12, height = 8, dpi = 600, bg = "white")
-
-good.icc <- cowplot::plot_grid( item04,  item06, item07,
-                                item11, item12, item14, item15, item18, item19,
-                               item20, item21, item22,
-                                  labels = "AUTO",
-                                  ncol=4,  
-                                  label_size = 15, 
-                                  align = "v")
-
-ggsave("Figures/good.icc.png",good.icc , width = 12, height = 8, dpi = 600, bg = "white")
-
 ```
@@
 ```{r item-plots, inclide =F}
-pacman::p_load(reshape,ggsci)
-Theta <- matrix(seq(-6,6, by = .1))
-
-item1.extract<- extract.item(fit, 1)
-item2.extract<- extract.item(fit, 2)
-item3.extract<- extract.item(fit, 3)
-item4.extract<- extract.item(fit, 4)
-item5.extract<- extract.item(fit, 5)
-item6.extract<- extract.item(fit, 6)
-item7.extract<- extract.item(fit, 7)
-item8.extract<- extract.item(fit, 8)
-item9.extract<- extract.item(fit, 9)
-item10.extract<-extract.item(fit, 10)
-item11.extract<- extract.item(fit, 11)
-item12.extract<- extract.item(fit, 12)
-item13.extract<- extract.item(fit, 13)
-item14.extract<- extract.item(fit, 14)
-item15.extract<- extract.item(fit, 15)
-item16.extract<- extract.item(fit, 16)
-item17.extract<-extract.item(fit, 17)
-item18.extract<- extract.item(fit, 18)
-item19.extract<- extract.item(fit, 19)
-item20.extract<- extract.item(fit, 20)
-item21.extract<-extract.item(fit, 21)
-item22.extract<- extract.item(fit, 22)
-item23.extract<- extract.item(fit, 23)
-
-item1 <- iteminfo(item1.extract, Theta)
-item2 <- iteminfo(item2.extract, Theta)
-item3 <- iteminfo(item3.extract, Theta)
-item4 <- iteminfo(item4.extract, Theta)
-item5 <- iteminfo(item5.extract, Theta)
-item6 <- iteminfo(item6.extract, Theta)
-item7 <- iteminfo(item7.extract, Theta)
-item8 <- iteminfo(item8.extract, Theta)
-item9 <- iteminfo(item9.extract, Theta)
-item10 <- iteminfo(item10.extract, Theta)
-item11 <- iteminfo(item11.extract, Theta)
-item12 <- iteminfo(item12.extract, Theta)
-item13 <- iteminfo(item13.extract, Theta)
-item14 <- iteminfo(item14.extract, Theta)
-item15 <- iteminfo(item15.extract, Theta)
-item16 <- iteminfo(item16.extract, Theta)
-item17 <- iteminfo(item17.extract, Theta)
-item18 <- iteminfo(item18.extract, Theta)
-item19 <- iteminfo(item19.extract, Theta)
-item20 <- iteminfo(item20.extract, Theta)
-item21 <- iteminfo(item21.extract, Theta)
-item22 <- iteminfo(item22.extract, Theta)
-item23 <- iteminfo(item23.extract, Theta)
-
-info.data <- as.data.frame(cbind(item1, item2, item3,item4,item5,item6,item7,item8,item9,item10,
-                                 item11,item12,item13,item14,item15,item16,item17,item18,item19,item20,
-                                 item21,item22,item23))
-
-item1.iic1 <- ggplot(info.data,aes(Theta,item1))+geom_line()+apatheme+
-  ggtitle(" Item01")+theme(legend.position = "none")+ylim(0,.7)+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info
-
-item2.iic1 <- ggplot(info.data,aes(Theta,item2))+geom_line()+apatheme+
-  ggtitle(" Item02")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info
-
-item3.iic1 <- ggplot(info.data,aes(Theta,item3))+geom_line()+apatheme+
-  ggtitle(" Item03")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info
-
-item4.iic1 <- ggplot(info.data,aes(Theta,item4))+geom_line()+apatheme+
-  ggtitle(" Item04")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info
-
-item5.iic1 <- ggplot(info.data,aes(Theta,item5))+geom_line()+apatheme+
-  ggtitle(" Item05")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info
-
-item6.iic1 <- ggplot(info.data,aes(Theta,item6))+geom_line()+apatheme+
-  ggtitle(" Item06")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))
-
-item7.iic1 <- ggplot(info.data,aes(Theta,item7))+geom_line()+apatheme+
-  ggtitle(" Item07")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))
-
-item8.iic1 <- ggplot(info.data,aes(Theta,item8))+geom_line()+apatheme+
-  ggtitle(" Item08")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info
-
-item9.iic1 <- ggplot(info.data,aes(Theta,item9))+geom_line()+apatheme+
-  ggtitle(" Item09")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info
-
-item10.iic1 <- ggplot(info.data,aes(Theta,item10))+geom_line()+apatheme+
-  ggtitle(" Item10")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info
-
-item11.iic1 <- ggplot(info.data,aes(Theta,item11))+geom_line()+apatheme+
-  ggtitle(" Item11 ")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))
-
-item12.iic1 <- ggplot(info.data,aes(Theta,item12))+geom_line()+apatheme+
-  ggtitle(" Item12")+
+
+iteminfo <- plot(fit, type = "infotrace",which.item =2)
+
+itemplot.01 <- tabledown::ggiteminfo(fit,1,6)+apatheme+
+  ggtitle(" Item03")+theme(legend.position = "none")+
   labs(y = "Item Information")+
@@
 
-item13.iic1 <- ggplot(info.data,aes(Theta,item13))+geom_line()+apatheme+
-  ggtitle(" Item13)")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info
-
-item14.iic1 <- ggplot(info.data,aes(Theta,item14))+geom_line()+apatheme+
-  ggtitle(" Item14")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))
-
-item15.iic1 <- ggplot(info.data,aes(Theta,item15))+geom_line()+apatheme+
-  ggtitle(" Item15 ")+
+itemplot.02 <- tabledown::ggiteminfo(fit,2,6)+apatheme+
+  ggtitle(" Item04")+theme(legend.position = "none")+
   labs(y = "Item Information")+
@@
 
-item16.iic1 <- ggplot(info.data,aes(Theta,item16))+geom_line()+apatheme+
-  ggtitle(" Item16")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info
-
-item17.iic1 <- ggplot(info.data,aes(Theta,item17))+geom_line()+apatheme+
-  ggtitle(" Item17")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info
-
-item18.iic1 <- ggplot(info.data,aes(Theta,item18))+geom_line()+apatheme+
-  ggtitle("Item18")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))
-
-item19.iic1 <- ggplot(info.data,aes(Theta,item19))+geom_line()+apatheme+
-  ggtitle(" Item19")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))
-
-item20.iic1 <- ggplot(info.data,aes(Theta,item20))+geom_line()+apatheme+
-  ggtitle(" Item20")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))
-
-item21.iic1 <- ggplot(info.data,aes(Theta,item21))+geom_line()+apatheme+
-  ggtitle(" Item21")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))
-
-item22.iic1 <- ggplot(info.data,aes(Theta,item22))+geom_line()+apatheme+
-  ggtitle(" Item22")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))
-
-item23.iic1 <- ggplot(info.data,aes(Theta,item23))+geom_line()+apatheme+
-  ggtitle(" Item23")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+ylim(0,.7)+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))# Low info
-
-ICC1 <- cowplot::plot_grid( item1.iic1, item2.iic1, item3.iic1, item4.iic1, item5.iic1, item8.iic1 ,  labels = "AUTO",ncol=2, label_size = 15,align = "v")
-ggsave("Figures/ICC1.png",ICC1 , width = 12, height = 8, dpi = 600, bg = "white")
-
-ICC2 <- cowplot::plot_grid( item9.iic1, item10.iic1, item13.iic1, item16.iic1, item17.iic1, item23.iic1 ,  labels = "AUTO",ncol=2, label_size = 15,align = "v")
-ggsave("Figures/ICC2.png",ICC2 , width = 12, height = 8, dpi = 600, bg = "white")
-
-ICC3 <- cowplot::plot_grid( item6.iic1, item7.iic1, item11.iic1, item12.iic1, item14.iic1, item15.iic1 ,  labels = "AUTO",ncol=2, label_size = 15,align = "v")
-ggsave("Figures/ICC3.png",ICC3 , width = 12, height = 8, dpi = 600, bg = "white")
-
-ICC4 <- cowplot::plot_grid( item18.iic1, item19.iic1, item20.iic1, item21.iic1, item22.iic1,  labels = "AUTO",ncol=2, label_size = 15,align = "v")
-ggsave("Figures/ICC4.png",ICC4 , width = 12, height = 8, dpi = 600, bg = "white")
-
-bad.info <- ICC1 <- cowplot::plot_grid( item1.iic1, item2.iic1, item3.iic1, item4.iic1, item5.iic1, item8.iic1 ,
-                                        item9.iic1, item10.iic1, item13.iic1, item16.iic1, item17.iic1, item23.iic1 ,
-
-                                        labels = "AUTO",ncol=3, 
-                                        label_size = 15,align = "v")
-ggsave("Figures/bad.info.png",bad.info, width = 12, height = 8, dpi = 600, bg = "white")
-
 good.info <- cowplot::plot_grid( item6.iic1, item7.iic1, item11.iic1, item12.iic1, item14.iic1, item15.iic1 , item18.iic1, item19.iic1, item20.iic1, item21.iic1, item22.iic1, 
@@
 ggsave("Figures/good.info.png",good.info, width = 12, height = 8, dpi = 600, bg = "white")
+
+test.info <- tabledown::ggtestinfo(irt.data,fit)+ apatheme+geom_line(colour = "black", size=1.5)+geom_area(fill ="palegreen4" )+geom_vline(xintercept = -3, colour ="black")+
+  geom_vline(xintercept = .5, colour ="black")
+library(plotly)
+info.p <- plotly::ggplotly(test.info)
 
@@
 library("lordif")
-DIF <- lordif(as.data.frame(irt.2), data$Sex, criterion = "Chisqr")
+gender <- as.data.frame(data$Gender)
+colnames(gender) <- "Gender"
+gender$Gender <- as.factor(gender$Gender)
+irt.data <- na.omit(irt.data)
+communication <- sem.data[,c(2:24)]
+dif.data <- cbind(gender, communication)
+dif.data <- na.omit(dif.data)
+dif.data.full <- as.data.frame(dif.data)
+DIF <- lordif(as.data.frame(irt.data), group = dif.data.full$Gender, criterion = "Chisqr")
+
 DIF$stats[,1:5]

### 2022-01-30 manuscript.Rmd
Validity analysis

@@
 irt.data <- na.omit(irt.data)
-irt.data <- irt.data %>% 
+irt.data.1 <- irt.data %>% 
   dplyr::select( CS03, CS04, CS06, CS07,CS08,CS10,CS11,    CS12, 
@@
 
-fit <- mirt(irt.data, model = 1, itemtype = 'graded', 
+fit <- mirt(irt.data.1, model = 1, itemtype = 'graded', 
                SE = TRUE, Se.type = 'MHRM',
@@
 
+```{r}
+
+val.data<- validity.data.full %>% 
+  dplyr::select( CS03, CS04, CS06, CS07,CS08,CS10,CS11,    CS12, 
+                 CS13,CS14,CS15,CS17, CS18, CS19, CS20 ,CS21, CS22) %>% 
+  rowwise() %>% 
+  mutate(Total_communication = sum(across(starts_with("CS")), na.rm = T))
+
+val.data.2 <- as.data.frame(cbind(val.data$Total_communication, validity.data.full$Total_HS, validity.data$Total_LS, validity.data.full$Total_SE))
+
+colnames(val.data.2) <- c("Communication", "Hopelessness", "Life Satisfaction", "SE")
+validity <- na.omit(val.data.2)
+```
+
+```{r correlationfunc, include =F}
+glrstab<- function(x, export=FALSE) {
+
+ r <-corr.test(x)$r	#taking just the correlation matrix; no N, or p
+ p <-corr.test(x)$p	#taking the p*s
+
+#define notions for significance levels
+ mystars <- ifelse(p < .001, "**"
+                   , ifelse(p < .01, "**"
+                            , ifelse(p < .05, "*"
+                                     , ifelse(p < .10, "+", " "))))
+
+ #round r, define new matrix Rnew with the correlations from rnd and paste mystars
+ rnd  <- papaja::printnum(r, gt1 = FALSE, digits = 2)  #round, drop leading 0 - Thanks CRSH!								                     
+ Rnew <- matrix(paste(rnd, mystars, sep=""), ncol=ncol(rnd))
+
+  #remove 1.0 correlations from diagonal  and set the strings
+ diag(Rnew) <- ''		
+ Rnew[upper.tri(Rnew)] <- ''
+
+ rownames(Rnew) <- paste(1:ncol(rnd), colnames(rnd), sep=" ")         #define number and name
+ colnames(Rnew) <- paste(1:ncol(rnd), "", sep="") 			       #define number
+
+#fun-part: we trim the top half 
+ Rnew[upper.tri(Rnew)] <- ''			
+ Rnew
+
+ #Rnew <- cbind(round(describe(x)[,3:4],2), Rnew)		     #describe x, M sD - put them in the matrix
+ #colnames(Rnew)[1:2] <- c("M","SD")					      		#Beschriftung der neuen Spalten
+ Rnew <- Rnew[,1:(ncol(Rnew)-1)]							        	#delete the last column (ugly)
+
+ #export to clipboard
+
+   if (export==TRUE){
+   result<-write.table(Rnew
+                       , "clipboard"
+                       , sep=";"
+                       , row.names=FALSE)
+ }
+ else result <- Rnew
+ return(result)
+
+}
+
+```
+
+```{r correlations, include =F}
+Cor <-glrstab(validity) #the function in action!
+
+cor.tab <- as_tibble(cor(validity))
+
+```
+
+```{r tabvalidity,  results='asis'}
+papaja::apa_table(Cor, escape  = FALSE
+                , caption = "Correlation matrix of the main variables"
+                , note    = "**p < .001")
+```
+
 ## Participants

### 2022-02-01 manuscript.Rmd
Decluttering

@@
 ---
-title             : "The title"
-shorttitle        : "Title"
+title             : "Psychometric Evaluation of the Bangla-translated Rotter Internal-External Scale through Classical Test Theory and Item Response Theory"
+shorttitle        : "Bangla Communication Scale"
 
 author: 
-  - name          : "First Author"
+  - name          : "Nusrat Jahan"
+    affiliation   : "1, *"
+    role:         
+      - Conceptualization
+      - Project Management
+
+      - Data Curation
+      - Writing - Original Draft Preparation
+
+    - name          : "Mushfiqul Anwar Siraji"
+    affiliation   : "2, *"
+    role:
+      - Conceptualization
+      - Project Management
+      - Formal Analysis
+      - Data Visualization
+      - Writing - Original Draft Preparation
+      - Writing - Review & Editing
+
+    - name          : "Zinnatul Boraka"
     affiliation   : "1"
     corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
+    address       : "Department of Educational and Counselling Psychology,University of Dhaka,Dhaka 1000"
     email         : "my@email.com"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
+    role:
       - Conceptualization
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
-  - name          : "Ernst-August Doelle"
-    affiliation   : "1,2"
-    role:
       - Writing - Review & Editing
@@
   - id            : "1"
-    institution   : "Wilhelm-Wundt-University"
+    institution   : "Department of Educational and Counselling Psychology,University of Dhaka"
   - id            : "2"
-    institution   : "Konstanz Business School"
+    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
+  - id            : "*"
+    institution   : "Joint first author"
 
@@
 ---
-
 ```{r setup, warning=FALSE, include=FALSE}
@@
 
+## Ethical Consideration
+
+All procedures performed in studies involving human participants were in accordance with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.
+This article does not contain any studies with animals performed by any of the authors.
+
+## Data and code availability
+All code and data underlying this article is available on a public GitHub repository (https://github.com/masiraji/Communication).
+
 \newpage

### 2022-02-01 manuscript.Rmd
yml header updated

@@
   - name          : "Nusrat Jahan"
-    affiliation   : "1, *"
+    affiliation   : "1"
+    corresponding : no    # Define only one corresponding author
     role:         
       - Conceptualization
-      - Project Management
-
       - Data Curation
       - Writing - Original Draft Preparation
-
   - name          : "Mushfiqul Anwar Siraji"
-    affiliation   : "2, *"
+    affiliation   : "2"
+    corresponding : no   # Define only one corresponding author
+    address       : "Monash University Malaysia,Jalan Lagoon Selatan, 47500 Bandar Sunway,Selangor Darul Ehsan, Malaysia."
+    email         : "mushfiqul.anwarsiraji@moansh.edu"
     role:
@@
 
-    - name          : "Zinnatul Boraka"
+  - name          : "Zinnatul Borak"
     affiliation   : "1"
@@
     address       : "Department of Educational and Counselling Psychology,University of Dhaka,Dhaka 1000"
-    email         : "my@email.com"
+    email         : "mushfiqul.anwarsiraji@moansh.edu"
     role:
@@
 
-bibliography      : ["references.bib"]
+bibliography      : ["r-references.bib", "references.bib"]
 
@@
 ---
+
 ```{r setup, warning=FALSE, include=FALSE}
@@
 pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap, foreign,DT,SimDesign)
+library(papaja)
 pacman::p_install_gh("jthomasmock/gtExtras")
@@
 
-```{r library, eval=FALSE, include=FALSE}
+```{r library,include=FALSE}
 #This chunk holds code for calling the required packages
@@
 nocite: |
-  `r cite_r("references.bib")`
+  `r papaja::cite_r("references.bib")`
 
@@
 
-# Methods
+# Study 1: Translations and Factor Structure
+
+Our first study had two objectives.
+First, we translated the English communication scale to Bangla language.
+Second, to identified the latent structure of the Bangla Communication Scale (BCS) using Exploratory Factor Analysis (EFA)
+
+## Methods
+
+## Participants
+
 ```{r data, include=F}
@@
 irt.data <- sem.data[,2:24]
-
-```
-
-```{r descriptivrd, eval=FALSE, include=FALSE}
-desc <- data[,c(3, 5,6)]
+```
+
+```{r sescrptives, include=FALSE}
+desc <- efa.data.full[,c(3,4,5)]
 ## Recoding desc$Sex
-desc$Sex <- fct_recode(desc$Sex,
+desc$Gender <- fct_recode(desc$Gender,
   "Boy" = "male",
@@
 )
-colnames(desc) <- c("Gender", "Social Status", "Age")
+colnames(desc) <- c("Gender", "Age", "Socio Economic Status")
 
@@
   modify_caption("Demographic Characteristics")
-```
-
-```{r gt-pic, include=F}
-des_tab  %>%    # build gtsummary table
-  as_gt() %>%             # convert to gt table
-  gt::gtsave(             # save table as image
-    filename = "Figures/demographics.png"
-  )
-```
-
-```{r}
-
-```
-
-```{r}
-reliability <- psych::alpha(com2, check.keys = T)
-```
+
+as_tibble(des_tab) -> desc_tibble 
+as_kable_extra(des_tab, format = "latex",booktabs = T) -> desc_kable #save it as a knitr::kable
+
+des.2 <- desc %>% 
+  psych::describeBy("Gender")
+female <- as.tibble(des.2$Female)
+male <- as.tibble(des.2$Male)
+
+```
+
+A cross-sectional survey was used to collect data from a large sample of students of grade 8-10 (n = `r nrow(efa.data)`) from ---- schools following convenience sampling method.
+T.
+For estimating the sample size for the CFA we followed the N:q rule [@RN1268; @RN1269; @RN1270; @RN1271] where 10 participants per parameters is required to earn trustworthiness of the result.
+Our sample size exceeds the requirement.
+Among `r nrow(data)` participants, `r female[1,2]` were female aged between `r female[4,8]` to `r female[4,9]` years (`r round(female[4,3],2)`±`r round(female[4,4],2)`).
+`r male[1,2]`  were male with an age range between `r male[4,8]` to `r male[4,9]` years (`r round(male[4,3],2)`±`r round(male[4,4],2)`).
+Table \@ref(tab:demographics) summarizes the demographics.
 

### 2022-02-01 manuscript.Rmd
Strudy-1 participants description added

@@
   psych::describeBy("Gender")
-female <- as.tibble(des.2$Female)
-male <- as.tibble(des.2$Male)
+female <- as.tibble(des.2$Girl)
+male <- as.tibble(des.2$Boy)
 
@@
 T.
-For estimating the sample size for the CFA we followed the N:q rule [@RN1268; @RN1269; @RN1270; @RN1271] where 10 participants per parameters is required to earn trustworthiness of the result.
+For estimating the sample size for the CFA we followed the N:q rule [@RN1268; @RN1269; @RN1270; @RN1271] which required 10 participants per parameters for trustworthiness of the result.
 Our sample size exceeds the requirement.
-Among `r nrow(data)` participants, `r female[1,2]` were female aged between `r female[4,8]` to `r female[4,9]` years (`r round(female[4,3],2)`±`r round(female[4,4],2)`).
-`r male[1,2]`  were male with an age range between `r male[4,8]` to `r male[4,9]` years (`r round(male[4,3],2)`±`r round(male[4,4],2)`).
-Table \@ref(tab:demographics) summarizes the demographics.
+Among `r nrow(efa.data))` participants, `r female[1,2]` were female aged between `r female[2,8]` to `r female[2,9]` years (`r round(female[2,3],2)`±`r round(female[2,4],2)`).
+`r male[1,2]`  were male with an age range between `r male[2,8]` participants `r male[2,9]` years (`r round(male[2,3],2)`±`r round(male[2,4],2)`).
+`r desc_tibble [4,2]` participants belonged to middle socio-economic status.
+`r desc_tibble [3,2]` and `r desc_tibble [5,2]` participants belonged to lower and upper socio-economic status-respectively.
 

### 2022-02-01 manuscript.Rmd
Participants grade 10-12 updated

@@
 
-A cross-sectional survey was used to collect data from a large sample of students of grade 8-10 (n = `r nrow(efa.data)`) from ---- schools following convenience sampling method.
+A cross-sectional survey was used to collect data from a large sample of students of grade 8-12 (n = `r nrow(efa.data)`) from 8schools following convenience sampling method.
 T.

### 2022-02-02 manuscript.Rmd
Participants update

@@
 `r desc_tibble [3,2]` and `r desc_tibble [5,2]` participants belonged to lower and upper socio-economic status-respectively.
+
+## Procedure
+Prior to data collection necessary authorization from school's authority and assent from the participating were obtained.
+Data collection was commenced between November 2021 to January 2022.
+The data collection took place in the classroom where students were at first briefed about 'communication skill'.
+Next.
+they filled up their sociademographics information and responded to our Bangla Communication Scale.
+All personal information (name, school,class) was codified and encrypted, producing a anonymous database.
+
+## Materials
+
+### Communication Scale
+
+### Bangla Communication Scale
+We translated the "Communication Scale" into Bangla Language following  International Test Commission (ITC) guidelines [@bartramITCGuidelinesTranslating2018] to translate and adapt Communication scale.
+Two bilingual researchers (PhD in Psychology) natives in Bangla translated the original English version to Bangla.
+Two translated versions were then judged and synthesized by the authors.
+Subsequently, two bilingual researchers (One PhD, one MS in Psychology) back-translated the Bangla scale into English with no knowledge of the original work.
+The authors synthesized the two back-translations and compared it with the original scale and made necessary amendments
 

### 2022-02-02 manuscript.Rmd
Introduction 1st paragraph

@@
 
+Communication is a complex behaviour of exchanging information among individuals combining physical and mental events.
+[@tanner2006advanced].
+Communication plays a central role among adolescents in developing self-identity, social relationships and creates the foundation of collective social activity [@haslett1989children].
+
+Often adults picture adolescents having inadequate and inept communication skills [@thurlow2003teenagers;@stern2005self].
+Media representation of adolescents often includes "storm-and stress", self absorbed and disengaged type behaviours [@porteous1980adolescents;@stern2005self].
+As such adolescents are often labelled as "lazy" and "disrespectful" by the adults [@public1999kids].
+On the contrary adolescents are highly engaged in work, community services and extracurricular activities and also more aspiring to earn an college degrees [@debard2004millennials; @schneider1999ambitious].
+Such a discrepancy between the reality of adolescent's image and adult's perception of the adolescents might be attributed to the mismatch of communication skills.
+The communication pattern of adolescents might not necessarily same as the adults.
+In addition to face to face communication, adolescents are vastly exposed to different virtual communication platforms.
+This may cause them to face more complex social challenges than the adults [@thurlow2003teenagers].
+"Communication capital" expresses the potential of civic-engagement that incorporates developing social relationships and influences collective social activity.
+The more communication capital an individual has the easier the instances of civic engagement become.
+
+Understanding the communication skills among the adolescents is vital as it is considered as the "key skill" in the education [@thurlow2001talkin].
+To promote better understanding of subject contents assessing the communication skill among adolescents is highly required.
+For this purpose "Communication Skill" sub-skill set [@barkman2002four]  was developed in 2002 as a part of The  National  On-line  Youth  Life  Skills  Evaluation System [@mincemoyer2005measuring] and since then it has been extensively used .
+
 # Study 1: Translations and Factor Structure
@@
 T.
-For estimating the sample size for the CFA we followed the N:q rule [@RN1268; @RN1269; @RN1270; @RN1271] which required 10 participants per parameters for trustworthiness of the result.
+For estimating the sample size for the CFA we followed the N:q rule [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]  which required 10 participants per parameters for trustworthiness of the result.
 Our sample size exceeds the requirement.

### 2022-02-02 manuscript.Rmd
Introduction part updated

@@
     institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
-  - id            : "*"
-    institution   : "Joint first author"
 
@@
 
-Communication is a complex behaviour of exchanging information among individuals combining physical and mental events.
-[@tanner2006advanced].
-Communication plays a central role among adolescents in developing self-identity, social relationships and creates the foundation of collective social activity [@haslett1989children].
+Communication is a complex behaviour of exchanging information among individuals [@tanner2006advanced].
+Communication plays a central role among adolescents in developing self-identity, social relationships and creates the foundation of collective social activity [@haslett1989children; @conti2008emotional; @spencer2013language].
+Inadequate communication skill may cause poor peer relationship resulting long-term socio-emotional difficulties including social anxiety, stress, low self-esteem and poor academic performance [@brinton2004social; @reed2020relative].
 
@@
 
-Understanding the communication skills among the adolescents is vital as it is considered as the "key skill" in the education [@thurlow2001talkin].
+Understanding the adolescents' communication skill  vital as it is considered as the "key skill" in the education [@thurlow2001talkin] and employment market [@olszewski2017training].
+In the western society, adolescents are now facing high unemployment [@lindsay2014employers].
+Lack of adequate communication skill is one of the root causes of this high unemployment [@lindsay2014employers].
+Similarly, lack of proper communication skill often promotes the propensity of anti-social behaviours and risk of exclusion from schools [@clegg2009language; @conti2004social].
+
 To promote better understanding of subject contents assessing the communication skill among adolescents is highly required.
-For this purpose "Communication Skill" sub-skill set [@barkman2002four]  was developed in 2002 as a part of The  National  On-line  Youth  Life  Skills  Evaluation System [@mincemoyer2005measuring] and since then it has been extensively used .
-
-# Study 1: Translations and Factor Structure
-
-Our first study had two objectives.
-First, we translated the English communication scale to Bangla language.
-Second, to identified the latent structure of the Bangla Communication Scale (BCS) using Exploratory Factor Analysis (EFA)
-
+For this purpose "Communication Skill" sub-skill set [@barkman2002four]  was developed in 2002 as a part of The  National  On-line  Youth  Life  Skills  Evaluation System [@mincemoyer2005measuring] and since then it has been extensively used [@fitzpatrick2005life].
+
+This study has two objectives: (a) To explore and validate the latent construct of "Bangla Communication Scale" using (b) To gather concurrent validity evidence (c) To increase the precision of the scale usining Item Response Theory guided analysis
 ## Methods
@@
 
-A cross-sectional survey was used to collect data from a large sample of students of grade 8-12 (n = `r nrow(efa.data)`) from 8schools following convenience sampling method.
+A cross-sectional survey was used to collect data from a large sample of students of grade 8-12 (n = `r nrow(efa.data)`) from 8 schools following convenience sampling method.
 T.
@@
 Our sample size exceeds the requirement.
-Among `r nrow(efa.data))` participants, `r female[1,2]` were female aged between `r female[2,8]` to `r female[2,9]` years (`r round(female[2,3],2)`±`r round(female[2,4],2)`).
+Among `r nrow(efa.data)` participants, `r female[1,2]` were female aged between `r female[2,8]` to `r female[2,9]` years (`r round(female[2,3],2)`±`r round(female[2,4],2)`).
 `r male[1,2]`  were male with an age range between `r male[2,8]` participants `r male[2,9]` years (`r round(male[2,3],2)`±`r round(male[2,4],2)`).
@@
 Next.
-they filled up their sociademographics information and responded to our Bangla Communication Scale.
+they filled up their soci-demographics information and responded to our Bangla Communication Scale.
 All personal information (name, school,class) was codified and encrypted, producing a anonymous database.
@@
 
-```{r}
+```{r, gtfig, include =F}
 
@@
 
-#Histogram
-#psych::multi.hist(EFA.data[,sapply(EFA.data, is.numeric)])
-
-# Univariate normality
-
-#creating normality function
-shapiro_test_df <- function(df, bonf= TRUE, alpha= 0.05) {
-  l <- lapply(df, shapiro.test)
-  s <- do.call("c", lapply(l, "[[", 1))
-  p <- do.call("c", lapply(l, "[[", 2))
-  if (bonf == TRUE) {
-    sig <- ifelse(p > alpha / length(l), "H0", "*")
-  } else {
-    sig <- ifelse(p > alpha, "H0", "*")
-  }
-  return(list(statistic= s,
-              p.value= p,
-              significance= sig,
-              method= ifelse(bonf == TRUE, "Shapiro-Wilks test with Bonferroni Correction",
-                             "Shapiro-Wilks test without Bonferroni Correction")))
-}
-
-Shapiro.efa <- shapiro_test_df(efa.data)
-
-efa.normality.tab = matrix(nrow = 48, ncol = 2)
-rownameprefix <- "Item"
-rownamesufix <- seq(1:48)
-my.item.names <- paste(rownameprefix,rownamesufix, sep = "" )
-rownames(efa.normality.tab) <- my.item.names
-colnames(efa.normality.tab) <- c("statistic", "p")
-
-efa.normality.tab[,1] <- apa(Shapiro.efa$statistic,2,T)
-efa.normality.tab[,2] <- apa(Shapiro.efa$p.value,2,T)
-
-efa.normalityprefix <- efa.normality.tab[,1]
-efa.normalitysufix <- Shapiro.efa$significance
-efa.normality.stat <- paste(efa.normalityprefix,efa.normalitysufix, sep = "" )
-
-# Multivariate Normality
-mardia <- psych::mardia(efa.data, na.rm = T, plot =F)
-
-# Descriptive Stats
-Descriptives <- psych::describe(EFA.data)
-alpha <- psych::alpha(EFA.data,check.keys=TRUE)
-Item.total <- alpha$item.stats
-
-Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), efa.normality.stat,  apa(Item.total$r.cor,2,T))
-
-colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
-rownameprefix <- "Item"
-rownamesufix <- seq(1:48)
-my.names <- paste(rownameprefix,rownamesufix, sep = "" )
-rownames(Des.combined) = (my.names)
-
 decriptives <- tabledown::des.tab(efa.data)
+colnames(decriptives) = c("Items","Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
+
+```
+
+```{r}
+apa_table(decriptives)
 ```
@@
 ## Item Analysis
-`
-
-```{r Cronbach, results='asis', width = 60}
+
+```{r Cronbach, include=FALSE, results='asis'}
 Cron.bach <- psych::alpha(efa.data,check.keys=TRUE) 
@@
 
-reduced.model.2F.2 <- dplyr::select(EFA.data ,
-                                    -c( CS07, CS13, CS16, CS05, CS10, CS19, CS03, CS02, CS09, CS23, CS17, CS04))
-
-correlations.red.2F.2 <- polychoric(reduced.model.2F.2)
-
-fa.2F.3 <- fa(r=correlations.red.2F.2$rho, nfactors = 2, fm= "pa",rotate ="promax",
-              residuals = TRUE, SMC = TRUE, max.iter = 500 )
-
-CC <- print(fa.2F.3, cut = .3, digits = 3, sort = TRUE)
-
-```
-
-```{r CFAitems, include=FALSE }
-#This chunk holds codes for 1st CFA
-
-model.1 <- "Communication =~ CS15 + CS21 +CS11 + CS20+ CS14+ CS19+ CS22+ CS12+ CS06+ CS07+ CS18+ CS08+        CS04+CS17+CS03+CS13+CS10"
-
+```
+
+```{r eval=FALSE, include=FALSE}
+model.1 <- "F1 =~ CS15 + CS22+CS20+CS14+CS18+CS13+CS06+CS10
+            F2 =~ CS19+CS04+CS17+CS12+CS08+CS07"
 fit.1 <- cfa(model.1, data = cfa.data, ordered = names(cfa.data),estimator = "WLSMV")
@@
                        "rmsea", "rmsea.ci.lower", "rmsea.ci.upper","srmr"))
+reliability1 <- semTools::reliability(fit.1, return.total = T)
+
+```
+
+```{r CFAitems, include=FALSE }
+#This chunk holds codes for 1st CFA
+
+model.1 <- "Communication =~ CS15 + CS21 +CS11 + CS20+ CS14+ CS19+ CS22+ CS12+ CS06+ CS07+ CS18+ CS08+        CS04+CS17+CS03+CS13+CS10"
+
+fit.1 <- cfa(model.1, data = cfa.data, ordered = names(cfa.data),estimator = "WLSMV")
+
+## Summary of Model 
+cfa.sum.1 <- summary(fit.1, fit.measures =TRUE,standardized = TRUE,rsq =TRUE)
+
+## Selected Fit measures 
+fit.measures.1 <- fitmeasures (fit.1,c("gfi", "agfi", "nfi","rfi", 
+                       "cfi","tli",
+                       "rmsea", "rmsea.ci.lower", "rmsea.ci.upper","srmr"))
 
@@
 
-png(filename="Manuscript.figures/CFAplot.png", 
+png(filename="figures/CFAplot.png", 
     type="cairo",
     units="in", 
-    width=12, 
-    height=12, 
+    width=6, 
+    height=6, 
     pointsize=12, 
@@
 
-```{r Shortcut Invariance}
+```{r Shortcut Invariance, eval=FALSE, include=FALSE}
 invariance.data <- cfa.data.full[, c(3, 6:28)]
@@
 
-```{r figcfa, fig.cap = "Five Factor  Model of LEBA obtained by Confirmatory Factor Analysis.
-By allowing item pair 41 and 30 to covary their error variance our model attained the best fit.",  out.height='100%', warning=FALSE}
+```{r figcfa, fig.cap = "CFA Plot.", warning=FALSE}
 
@@
 
-```{r}
+```{r, include =F}
 irt.data <- na.omit(irt.data)
@@
 item_misfits <- subset(item.fit, RMSEA.S_X2 >= .06)
+
+## Creating IRT table
+item.fit2 <- item.fit[,c(4,6,11,12,13,14)] 
+colnames(item.fit2) <- c("Standardized Outfit", "Standardized Infit", "S-Chi-square", "df", "RMSEA", "p")
+
+IRT.details <- cbind(items ,item.fit2)
+
+IRT.details <- IRT.details %>% 
+ dplyr::mutate_if(is.numeric, round, digits=3)
+
+IRT.details <- tibble::rownames_to_column(IRT.details, "Items")
+#write_csv(IRT.details, "table_raw/IRT_parameters.csv")
+
+#-3<b<3
+#.5<a<2; baker p12
+
+mean.discrimination <- mean(IRT.details$a)
+sd.discrimination <- sd(IRT.details$a)
+range.descrimination <- range(IRT.details$a)
+
+cat.prob <- IRT.details[,c(3:6)]
+cat.prob.long <- reshape::melt(cat.prob)
+range.difficulty <- range(cat.prob.long$value)
+
+range.outfit <-  range(IRT.details$Outfit)
+range.infit <-  range(IRT.details$Infit)
+range.rmsea <- range(IRT.details$RMSEA)
 
@@
 abline(v = -2, lwd = 2, lty = 2)
+
+person <- ggplot(personfit, aes(x=Zh)) + geom_histogram(binwidth=.5,col=I("black"),fill="palegreen4")+geom_vline(xintercept = -2)+
+  labs( y="Number of Participants", x = "Zh Statistics")+apatheme + xlim(-4,2)+
+   scale_y_continuous(limits = c(0, 40), expand = expand_scale(mult = c(0, 0.1)))
+
+# annotation.1 <- data.frame(
+#    x = (-3.1),
+#    y = (20),
+#    label = ("Most of the participants
+#         are within the guidline")
+# )
+# 
+# per.anno <-person + geom_label(data=annotation.1, aes( x=x, y=y, label=label),                 , 
+#            color="orange", 
+#            size=5 , angle=45, fontface="bold" )
+
+ggsave("Figures/person.png",person , width = 12, height = 8, dpi = 600, bg = "white")
 
@@
 ICC <- cowplot::plot_grid(item03, item04, item06, item07, item08, 
-                   item10, item11, item12, item13, item14, item15,  item17, item19,
-                   item20, item21, 
+                   item10, item11, item12, item13, item14, item15,  item17, item18, item19,
+                   item20, item21, item22,
                       labels = "AUTO",
-                     ncol=4,  
+                     ncol=3,  
                     label_size = 15, 
@@
 
-ggsave("Figures/ICC.png",ICC , width = 12, height = 12, dpi = 600, bg = "white")
+ggsave("Figures/ICC.png",ICC , width = 12, height =14, dpi = 600, bg = "white")
+
+```
+
+```{r figICC, eval=FALSE, fig.cap="Option Charecteritics Curve.", warning=FALSE, include=FALSE, out.height='100%'}
+
+knitr::include_graphics("Figures/ICC.png", dpi =600)
 
@@
 
-good.info <- cowplot::plot_grid( item6.iic1, item7.iic1, item11.iic1, item12.iic1, item14.iic1, item15.iic1 , item18.iic1, item19.iic1, item20.iic1, item21.iic1, item22.iic1, 
-                                 labels = "AUTO",ncol=3, label_size = 15,align = "v")
-
-ggsave("Figures/good.info.png",good.info, width = 12, height = 8, dpi = 600, bg = "white")
-
-test.info <- tabledown::ggtestinfo(irt.data,fit)+ apatheme+geom_line(colour = "black", size=1.5)+geom_area(fill ="palegreen4" )+geom_vline(xintercept = -3, colour ="black")+
-  geom_vline(xintercept = .5, colour ="black")
+# good.info <- cowplot::plot_grid( item6.iic1, item7.iic1, item11.iic1, item12.iic1, item14.iic1, item15.iic1 , item18.iic1, item19.iic1, item20.iic1, item21.iic1, item22.iic1, 
+#                                  labels = "AUTO",ncol=3, label_size = 15,align = "v")
+# 
+# 
+# ggsave("Figures/good.info.png",good.info, width = 12, height = 8, dpi = 600, bg = "white")
+
+test.info <- tabledown::ggtestinfo(irt.data.1, fit)+ apatheme+geom_line(colour = "black", size=1.5)+geom_area(fill ="#E64B3599" )
+# +geom_vline(xintercept = -3, colour ="black")+
+#   geom_vline(xintercept = .5, colour ="black")
+ggsave("Figures/TIC.png",test.info , width = 6, height = 4, dpi = 600, bg = "white")
+
 library(plotly)
@@
 
-```{r IRT2, include}
-
-irt.2 <- dplyr::select(EFA.data, -c(CS01,CS02,CS03,CS04, CS05,CS08, CS09, CS10, CS13, CS16, CS17,CS23))
-
-fit2 <- mirt(irt.2, model = 1, itemtype = 'graded', 
-               SE = TRUE, Se.type = 'MHRM',
-               technical = list(NCYCLES = 10000))
-
-occ <- plot(fit2, facet =T, type= "trace")
-
-# Model Parameters ####
-params2 <- coef(fit2, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
-items2 <- data.frame(params2$items)
-se2 <- coef(fit2, printSE = TRUE)
-
-# Model Fit (degrees of freedom too low to check model fit)
-model2 <- as.data.frame(M2(fit2))
-
-#Item fit
-item.fit2<- itemfit(fit2, fit_stats = c("S_X2",  "infit"),
-                                  impute=10)
-
-#Identifying Missfit items based on RMSEA Value
-item_misfits2 <- subset(item.fit2, RMSEA.S_X2 >= .06)
-
-## Creating IRT table
-item.fit3 <- item.fit2[,-c(1,2,4)] 
-colnames(item.fit3) <- c("Outfit", "Infit", "S-Chi-square", "df", "RMSEA", "p")
-
-IRT.details <- cbind(items2 ,item.fit3)
-
-IRT.details <- IRT.details %>% 
- dplyr::mutate_if(is.numeric, round, digits=3)
-
-IRT.details <- tibble::rownames_to_column(IRT.details, "Items")
-#write_csv(IRT.details, "table_raw/IRT_parameters.csv")
-
-#-3<b<3
-#.5<a<2; baker p12
-
-mean.discrimination <- mean(IRT.details$a)
-sd.discrimination <- sd(IRT.details$a)
-range.descrimination <- range(IRT.details$a)
-
-cat.prob <- IRT.details[,c(3:6)]
-cat.prob.long <- reshape::melt(cat.prob)
-range.difficulty <- range(cat.prob.long$value)
-
-range.outfit <-  range(IRT.details$Outfit)
-range.infit <-  range(IRT.details$Infit)
-range.rmsea <- range(IRT.details$RMSEA)
-
-# Person Fit ####
-personfit2 <- personfit(fit2) 
-personfit_model_misfits2 <- subset(personfit2, Zh < -2)
-rownames(personfit_model_misfits2)
-nrow(personfit_model_misfits2)
-
-person <- ggplot(personfit2, aes(x=Zh)) + geom_histogram(binwidth=.5,col=I("black"),fill="palegreen4")+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics")+apatheme + xlim(-4,2)+
-   scale_y_continuous(limits = c(0, 40), expand = expand_scale(mult = c(0, 0.1)))
-
-annotation.1 <- data.frame(
-   x = (-3.1),
-   y = (20),
-   label = ("Most of the participants
-        are within the guidline")
-)
-
-per.anno <-person + geom_label(data=annotation.1, aes( x=x, y=y, label=label),                 , 
-           color="orange", 
-           size=5 , angle=45, fontface="bold" )
-
-ggsave("Figures/person.png",per.anno , width = 12, height = 8, dpi = 600, bg = "white")
-
-# Plots ####
-
-OCC2 <- plot(fit2, type = "trace", facet =T, main = "Communication Scale OCC")
-info2 <- plot(fit2, type = "infoSE", main = "Communication Scale")
-iteminfo2 <- plot(fit2, type = "infotrace", 
-                    facet_items = T, main = "Communication Scale")
-
-##Test Info
-info <- tabledown::ggtestinfo(irt.2, fit2)+apatheme+geom_line(colour = "black", size=1.5)+geom_area(fill ="palegreen4" )+geom_vline(xintercept = -3, colour ="black")+
-  geom_vline(xintercept = .5, colour ="black")
-library(plotly)
-info.p <- plotly::ggplotly(info)
-
-annotation <- data.frame(
-   x = c(-4.2,1.5),
-   y = c(4.5,4.3),
-   label = c("Theta = -3", "Theta =.5")
-)
-
-info.anno <- info + geom_label(data=annotation, aes( x=x, y=y, label=label),
-           color="orange", 
-           size=7 , angle=45, fontface="bold" )
-
-ggsave("Figures/TIC.png",info.anno  , width = 12, height = 8, dpi = 600, bg = "white")
-
-#conditional reliability
+```{r figTIC, fig.cap = "TIC.",  out.height='100%', warning=FALSE}
+
+knitr::include_graphics("Figures/TIC.png", dpi =600)
+
+```
+
+```{r conrel-print, include=F}
+##
+png(filename="Figures/conrel.png", 
+    type="cairo",
+    units="in", 
+    width=12, 
+    height=2, 
+    pointsize=12, 
+    res=300)
 library(latticeExtra)
@@
 
-reliability.focused <- plot(fit2, type = 'rxx', theta_lim = c(-4, 2), 
+ plot(fit, type = 'rxx', theta_lim = c(-6, 6), 
       main="Conditional Reliability Plot", par.settings=c(apa.latice),col.line = "#E69F00",lwd = 3.5 )
 
-marginal.rel2 <- marginal_rxx(fit2)
-
-#scale characteristics curve
-scale2 <- plot(fit2, type = 'score', theta_lim = c(-6, 6), main = "")
-
-```
-
-```{r conrel-print, include=F}
-##
-png(filename="Figures/conrel.png", 
-    type="cairo",
-    units="in", 
-    width=12, 
-    height=8, 
-    pointsize=12, 
-    res=300)
-plot(fit2, type = 'rxx', theta_lim = c(-6, 6), 
-      main="", par.settings=c(apa.latice),col.line = "#E69F00",lwd = 3.5, cex =2.5 )+
-  layer(panel.abline(v = -4, colour = "red",panel=panel.filled_smooth))+
-  layer(panel.abline(v = 1.5))
-
 dev.off()
+```
+
+```{r figconrel, fig.cap = "Conditional Reliability.",  out.height='100%', warning=FALSE}
+
+knitr::include_graphics("Figures/conrel.png", dpi =600)
+
 ```
@@
 
-```{r dif}
+```{r dif, eval=FALSE, include=FALSE}
 library("lordif")
@@
   rowwise() %>% 
-  mutate(Total_communication = sum(across(starts_with("CS")), na.rm = T))
+  mutate(Total_communication = sum(across(starts_with("CS")), na.rm = T),
+         F1 = sum(CS15,CS22,CS20,CS14,CS18,CS13,CS06,CS10),
+         F2 = sum(CS19,CS04,CS17,CS12,CS08,CS07))
 
@@
 
-## Participants
-
-## Material
-
-## Procedure
-
-## Data analysis
-We used `r cite_r("references.bib")` for all our analyses.
-
 # Results

### 2022-02-04 manuscript.Rmd
Title Corrected

@@
 ---
-title             : "Psychometric Evaluation of the Bangla-translated Rotter Internal-External Scale through Classical Test Theory and Item Response Theory"
+title             : "Psychometric Evaluation of the Bangla Communication Scale through Classical Test Theory and Item Response Theory"
 shorttitle        : "Bangla Communication Scale"
@@
       - Conceptualization
+      - Project Management
       - Data Curation
@@
       - Project Management
-      - Formal Analysis
-      - Data Visualization
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
+      - Formal Analysis & Data Visualization
+      - Writing - Original Draft Preparation; Review & Editing
 
@@
     address       : "Department of Educational and Counselling Psychology,University of Dhaka,Dhaka 1000"
-    email         : "mushfiqul.anwarsiraji@moansh.edu"
+    email         : "institutional email of Bonhee mam"
     role:

### 2022-02-04 manuscript.Rmd
Landscape mode is now corrected

@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : 
+  papaja::apa6_pdf:
+    keep_tex: false
+    latex_engine: xelatex
+    includes:
+      in_header: header.tex
+mainfont: Arial
 ---
@@
 ```{r setup, warning=FALSE, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200)
-
+knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600, fig.width = 6,
+ fig.asp = 0.8,out.width = "80%", dev=c('png','postscript'))
+#options(knitr.duplicate.label = "allow")
 set.seed(123)
@@
 
-## Item Analysis
+## Item Analysis and Exploratory Factor Analysis
 
@@
 (ref:facIdFig) Factor Identification Methods (A) Parallel analysis  indicated the optimal number of factors were two.
-(B) Scree plot suggested One facor.
-(C) Hull method indicated 1 factors were required to balance the model fit and number of parameters.
+(B) Scree plot suggested One factor.
+(C) Hull method indicated one factor were required to balance the model fit and number of parameters.
 
@@
 
+```{r irttab, results='asis'}
+papaja::apa_table(IRT.details, caption = "Items discrimination and response category difficulty thresholds of 17 items in  Bangla Communication Scale (n =581)", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
+```
+
 ```{r OCC, include=F}
@@
 
-```{r item-plots, inclide =F}
-
-iteminfo <- plot(fit, type = "infotrace",which.item =2)
-
-itemplot.01 <- tabledown::ggiteminfo(fit,1,6)+apatheme+
-  ggtitle(" Item03")+theme(legend.position = "none")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))
-
-itemplot.02 <- tabledown::ggiteminfo(fit,2,6)+apatheme+
-  ggtitle(" Item04")+theme(legend.position = "none")+
-  labs(y = "Item Information")+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
-  xlab(expression(theta))+ ylab(expression(I(theta)))
+```{r Test-info, include =F}
+
+# iteminfo <- plot(fit, type = "infotrace",which.item =2)
+# 
+# itemplot.01 <- tabledown::ggiteminfo(fit,1,6)+apatheme+
+#   ggtitle(" Item03")+theme(legend.position = "none")+
+#   labs(y = "Item Information")+
+#   scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
+#   xlab(expression(theta))+ ylab(expression(I(theta)))
+# 
+# 
+# itemplot.02 <- tabledown::ggiteminfo(fit,2,6)+apatheme+
+#   ggtitle(" Item04")+theme(legend.position = "none")+
+#   labs(y = "Item Information")+
+#   scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+geom_area(fill ="palegreen4" )+
+#   xlab(expression(theta))+ ylab(expression(I(theta)))
+# 
+# 
+#
 
@@
 knitr::include_graphics("Figures/TIC.png", dpi =600)
+
+```
+
+```{r}
+# This chinks holds code of compiled item info code created using facet wrap. (Not included in manuscript)
+pacman::p_load(reshape,ggsci)
+Theta <- matrix(seq(-6,6, by = .1))
+
+##Item Extraction
+item03 <- extract.item(fit, 1)#item number
+item04 <- extract.item(fit, 2)
+item06 <- extract.item(fit, 3)
+item07 <- extract.item(fit, 4)
+item08 <- extract.item(fit, 5)
+item10 <- extract.item(fit,6)
+item11<- extract.item(fit, 7)
+item12 <-extract.item(fit, 8)
+item13 <- extract.item(fit, 9)
+item14 <- extract.item(fit, 10)
+item15 <- extract.item(fit, 11)
+item17 <- extract.item(fit, 12)
+item18 <- extract.item(fit, 13)
+item19 <- extract.item(fit, 14)
+item20 <- extract.item(fit, 15)
+item21 <- extract.item(fit, 16)
+item22 <- extract.item(fit, 17)
+
+##Item Info
+Item03 <- iteminfo(item03, Theta)
+Item04 <- iteminfo(item04, Theta)
+Item06 <- iteminfo(item06, Theta)
+Item07 <- iteminfo(item07, Theta)
+Item08 <- iteminfo(item08, Theta)
+Item10 <- iteminfo(item10, Theta)
+Item11 <- iteminfo(item11, Theta)
+Item12 <- iteminfo(item12, Theta)
+Item13 <- iteminfo(item13, Theta)
+Item14 <- iteminfo(item14, Theta)
+Item15 <- iteminfo(item15, Theta)
+Item17 <- iteminfo(item17, Theta)
+Item18<- iteminfo(item18, Theta)
+Item19 <- iteminfo(item19, Theta)
+Item20 <- iteminfo(item20, Theta)
+Item21 <- iteminfo(item21, Theta)
+Item22 <- iteminfo(item22, Theta)
+
+#Data frame
+
+item.info.data <- as.data.frame(cbind(Item03, Item04,Item06, Item07, Item08,
+                                      Item10, Item11, Item12, Item13, Item14,
+                                      Item15, Item17, Item18, Item19, Item20,
+                                      Item21, Item22))
+
+item.info.data.long <- melt(item.info.data)
+
+item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), item.info.data.long)
+
+pacman::p_load(ggsci)
+
+item.info.plot <- ggplot(item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
+  ggtitle("Item Information Plot")+theme(legend.position = "none")+
+  facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+geom_area()+ scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))
+
+# facet_wrap(~variable,scales = "free")++geom_hline(yintercept = .20, colour ="red")
+
+ggsave("Figures/itemInfoplot.png",item.info.plot, width = 8, height =8, dpi = 1200, bg ="white")
+
+```
+
+```{r figIIC, fig.cap = "Item Information Curve.",  out.height='100%',out.width='100%', warning=FALSE}
+
+knitr::include_graphics("Figures/itemInfoplot.png", dpi =600)
 
@@
 
-```{r figconrel, fig.cap = "Conditional Reliability.",  out.height='100%', warning=FALSE}
+```{r figconrel, fig.cap = "Conditional Reliability.", out.width= '100%', out.height='50%', warning=FALSE}
 

### 2022-02-04 manuscript.Rmd
Title changed

@@
 ---
-title             : "Psychometric Evaluation of the Bangla Communication Scale through Classical Test Theory and Item Response Theory"
+title             : "Psychometric Evaluation of the Bangla Communication Scale Among Adolescents:Latent structure, Reliability, validity, and gender invariance in a Bangladeshi adolescent sample"
 shorttitle        : "Bangla Communication Scale"

### 2022-02-04 manuscript.Rmd
Study 1 participants description

@@
 
-This study has two objectives: (a) To explore and validate the latent construct of "Bangla Communication Scale" using (b) To gather concurrent validity evidence (c) To increase the precision of the scale usining Item Response Theory guided analysis
+# Study-1: Translations and Exploratory Factor Analysis
+Study-1 had two objectives.
+First we translated the 23 items of the Communication Scale [@barkman2002four] from English to Bangla.
+Second, we conducted an Exploratory Factor Analysis (EFA) to identify the latent structure of the scale.
+
 ## Methods
 
-## Participants
+### Participants
 
@@
 
-A cross-sectional survey was used to collect data from a large sample of students of grade 8-12 (n = `r nrow(efa.data)`) from 8 schools following convenience sampling method.
-T.
-For estimating the sample size for the CFA we followed the N:q rule [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]  which required 10 participants per parameters for trustworthiness of the result.
-Our sample size exceeds the requirement.
+A cross-sectional survey was used to collect data from a large sample of students of grade 8-12 (n = `r nrow(efa.data)`) from 8 schools following convenience sampling method.One participant was excluded due to incomplete data.
+Participants were recruited following convenience sampling technique.
+For exploring the initial factor structure the recommended sample size is 250-300 [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
 Among `r nrow(efa.data)` participants, `r female[1,2]` were female aged between `r female[2,8]` to `r female[2,9]` years (`r round(female[2,3],2)`±`r round(female[2,4],2)`).
@@
 
-## Procedure
-Prior to data collection necessary authorization from school's authority and assent from the participating were obtained.
-Data collection was commenced between November 2021 to January 2022.
-The data collection took place in the classroom where students were at first briefed about 'communication skill'.
-Next.
-they filled up their soci-demographics information and responded to our Bangla Communication Scale.
-All personal information (name, school,class) was codified and encrypted, producing a anonymous database.
-
-## Materials
-
-### Communication Scale
-
-### Bangla Communication Scale
+### Materials
+
+#### Communication Scale
+
+#### Bangla Communication Scale
 We translated the "Communication Scale" into Bangla Language following  International Test Commission (ITC) guidelines [@bartramITCGuidelinesTranslating2018] to translate and adapt Communication scale.
@@
 The authors synthesized the two back-translations and compared it with the original scale and made necessary amendments
+
+### Data collection
+The project received intitutional ethics clearance from Department of Educational and Counselling Psychology (Project ID: ---).
+Prior to data collection necessary authorization from school's authority and assent from the participating were obtained.
+Necessary explanations were given in oral and written forms.It  was also mentioned in the explanatory statement that their participation was voluntary and that they could withdraw from participation anytime without being penalized and assent was recorded.
+Data collection was commenced between November 2021 to January 2022.
+The data collection took place in the classroom where students were at first briefed about 'communication skill'.
+Next.
+they filled up their socio-demographics information and responded to our Bangla Communication Scale.
+All personal information (name, school,class) was codified and encrypted, producing a anonymous database.
+
+## # Analytic strategies
+We used R (version 4.1.0) (Team, 2021), including several R packages (Barnier et al., 2021; R.
+Chalmers, 2012; Revelle, 2021; Rosseel, 2012; Siraji, 2021), for our analyses.
+Since Rotter's I-E scale used a dichotomous forced choice response and both univariate (Table 1) and multivariate normality assumptions are violated, we performed the exploratory factor analysis using a tetrachoric correlation matrix which was more robust to those violations (Watkins, 2020).
+We employed weighted least squares (WLS) as a factor extraction method to examine the latent structure of the scale.
+WLS is more robust towards violation of normality assumptions (Fabrigar et al., 1999).
+An orthogonal rotation technique: varimax was chosen following the literature investigating the latent structure of Rotter's I-E scale (Joe & Jahn, 1973; Mirels, 1970; Tobacyk, 1978).
+Before the EFA, necessary assumptions, including sample adequacy, quality of correlation matrix were assessed.
+As the commonalities for each item found in the previous studies were not  higher than .70 (Joe & Jahn, 1973; Mirels, 1970; Tobacyk, 1978), we relied on the Scree-plot rather than the Kaiser criterion of eigenvalues greater than one (Stevens, 2009).
+We supplemented the scree plot (Cattell, 1966) with Horn's parallel analysis (Horn, 1965), Minimum average partials method (MAP) (Velicer, 1976), and Hull method (Lorenzo-Seva et al., 2011).
+We compared the root mean square of the residual (RMSR) values obtained for the solutions to determine the best factor structure.
+RMSR≤.08 was preferred (Brown, 2015).
+Additionally, to identify the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors (Bandalos & Finney, 2019; Child, 2006; Mulaik, 2009; Watkins, 2020)
 

### 2022-02-04 manuscript.Rmd
EFA results updated

--- 2022-02-04 manuscript.Rmd
@@
 
-## Procedure
+### Materials
+
+#### Communication Scale
+
+Communication Scale [@barkman2002four] is a sub-skill set of The  National  On-line  Youth  Life  Skills  Evaluation System [@mincemoyer2005measuring].
+It has 23 items with a 5 Point Likert Type response scale (0=Never, 1=Rarely,  2=Sometimes,  3=Often,  4=Always).
+The total score range is 0-92 where a higher score would indicate higher communication skills among adolescents (age range 12-18).
+The internal consistency of the total scale, Cronbach $\alpha$ was .79
+
+#### Bangla Communication Scale
+We followed the International Test Commission  guidelines [@bartramITCGuidelinesTranslating2018] while translating the Communication Scale in Bangla.
+At first two bilingual researchers did the forward translation.
+These two forward translations were synthesized by the authors.
+Another four bilingual researchers did the backward translation of the synthesized Bangla Communication Scale.
+The authors again synthesized the back-translations, compared it with original scale and made necessary amendments.
+
+### Data collection
+The project received institutional ethics clearance from Department of Educational and Counselling Psychology (Project ID: ---).
 Prior to data collection necessary authorization from school's authority and assent from the participating were obtained.
+Necessary explanations were given in oral and written forms.It  was also mentioned in the explanatory statement that their participation was voluntary and that they could withdraw from participation any time without being penalized.
 Data collection was commenced between November 2021 to January 2022.
@@
 Next.
-they filled up their soci-demographics information and responded to our Bangla Communication Scale.
+they filled up their socio-demographics information and responded to our Bangla Communication Scale.
 All personal information (name, school,class) was codified and encrypted, producing a anonymous database.
 
-## Materials
-
-### Communication Scale
-
-### Bangla Communication Scale
-We translated the "Communication Scale" into Bangla Language following  International Test Commission (ITC) guidelines [@bartramITCGuidelinesTranslating2018] to translate and adapt Communication scale.
-Two bilingual researchers (PhD in Psychology) natives in Bangla translated the original English version to Bangla.
-Two translated versions were then judged and synthesized by the authors.
-Subsequently, two bilingual researchers (One PhD, one MS in Psychology) back-translated the Bangla scale into English with no knowledge of the original work.
-The authors synthesized the two back-translations and compared it with the original scale and made necessary amendments
-
+### Analytic strategies
+We used R (version 4.1.0) [@R-base], including several R packages [@R-lavaan; @R-mirt; @R-psych; @R-tabledown], for our analyses.
+Prior to the data analysis normality assumptions were checked.
+Our data violeted both univariate and multivariate normality.
+As such we used polychoric correlation matrix and 'principal axis" factor extraction method to conduct the exploratory factor analysis [@watkinsStepbyStepGuideExploratory2020].
+An oblique rotation method was employed.
+A posterior sampling adequacy was estimated using KMO statistics [@kaiserIndexFactorialSimplicity1974].
+TO identify the optimum number of factors required to explain the latent structure of our scale we used Scree plot [@cattellScreeTestNumber1966a], Horn's parallel analysis [@hornRationaleTestNumber1965], Hull method [@lorenzo-sevaHullMethodSelecting2011] and Minimum average partials method (MAP) [@velicerDeterminingNumberComponents1976].
+Lastly, to identify the simple structure, we followed the following guidelines  (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@childEssentialsFactorAnalysis2006a; @mulaikFoundationsFactorAnalysis2009; @watkinsStepbyStepGuideExploratory2020]
+
+### Results & Discussion
 ```{r, gtfig, include =F}
@@
 
+```{r item-analysis, include=FALSE, results='asis'}
+Cron.bach <- psych::alpha(correlations$rho,check.keys=TRUE) 
+Cron.bach$total %>% 
+  knitr::kable(caption = "Alpha", digits = 2) 
+Cron.bach$alpha.drop %>% 
+  knitr::kable(caption = "Alpha value if item is dropped", digits = 2) 
+Cron.bach$item.stats %>% 
+  knitr::kable(caption = "Corrected Item total Correlation", digits = 2)
+
+low.r.corec <- (min(Cron.bach$item.stats$r.cor))  #minimum item total correlation
+high.r.corec <- (max(Cron.bach$item.stats$r.cor))     # maximum item total correlation
+
+ordinal.alpha <- Cron.bach$total$raw_alpha
+ordinal.alpha.drop <- as.data.frame(Cron.bach$alpha.drop$raw_alpha)
+minimum.ordinal.alpha.drop <- min(ordinal.alpha.drop )
+maximum.ordinal.alpha.drop <- max(ordinal.alpha.drop )
+```
+
 ```{r EFAassumptions, include=FALSE}
@@
 decriptives <- tabledown::des.tab(efa.data)
-colnames(decriptives) = c("Items","Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
-
-```
-
-```{r}
+decriptives <- cbind(decriptives, ordinal.alpha.drop )
+colnames(decriptives) = c("Items","Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation", "Alpha Drop")
+descriptives <- cbind()
+
+item.total.correlation <- range(decriptives$`Item-Total Correlation`)
+```
+
+#### Sampling adequacy
+Kaiser-Meyer-Olkin (KMO) [@kaiserIndexFactorialSimplicity1974] statistics was used to check the sampling adequacy.
+The overall KMO value for 23 items was `r apa(KMO$MSA,2,T)`, which was above the cut-off value of .50, indicating an adequate sample.
+
+#### Descriptive statistics and item analysis
+Table\@ref(tab:tabDes) reports univariate descriptive statistics for the 23 items.
+All items were skewed and violeted univariate normality assessed by  The Shapiro-Wilk test indicated all the items violated normality assumptions [@shapiro1965analysis].
+Mardia's Test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] yielded Multivariate skew = 4030.49 (p <0.001) and multivariate kurtosis = 15.1 (p <0.001) indicating the violation of multivariate normality as well.
+As such we used polychoric correlation matrix which is more robust towards these violations.
+Our initial item analysis yelled internal consistency coefficient ordinal alpha = `r apa(ordinal.alpha,2,T)`.
+Alpha drop statistics (Table\@ref(tab:tabDes)) showed no substantial increase of ordinal alpha if any item is deleted and ranged between `r apa(minimum.ordinal.alpha.drop,T)`-`r apa(maximum.ordinal.alpha.drop,T)`.
+As such we subjected all items to EFA.
+
+Supplementary Table 1 and Figure \@ref(fig:corplot) depict the inter-item correlation coefficients of BCS.
+Bartlett’s test of sphericity [@RN1261], $\chi^2$ (`r bartlet$df`) = `rbartlet$chisq`, p < .001 indicated the inter-item correlations are significantly different than zero.
+However, only `r apa(cor.per,2,T)`% of the inter-item correlation coefficients were greater than absolute value of .30 in the obtained matrix.
+The corrected item-total correlations range was `r min(item.total.correlation)`-  `r max(item.total.correlation)` (Table\@ref(tab:tabDes)).
+
+```{r tab-des}
 apa_table(decriptives)
-```
-
-## Item Analysis and Exploratory Factor Analysis
-
-```{r Cronbach, include=FALSE, results='asis'}
-Cron.bach <- psych::alpha(efa.data,check.keys=TRUE) 
-Cron.bach$total %>% 
-  knitr::kable(caption = "Alpha", digits = 2) %>% 
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F)
-Cron.bach$alpha.drop %>% 
-  knitr::kable(caption = "Alpha value if item is dropped", digits = 2) %>% 
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F)
-
-Cron.bach$item.stats %>% 
-  knitr::kable(caption = "Corrected Item total Correlation", digits = 2) %>% 
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F)
-
-low.r.corec <- (min(Cron.bach$item.stats$r.cor))  #minimum item total correlation
-high.r.corec <- (max(Cron.bach$item.stats$r.cor))     # maximum item total correlation
-
 ```
@@
 
-(ref:figCor) Inter item polychoric correlation coefficients for the 48 items. 4.9 % inter-item correlation coefficients were higher than .30
+(ref:figCor) Inter item polychoric correlation coefficients for the 23 items. 9.8 % inter-item correlation coefficients were higher than |.30|
 
@@
 ```
-Scree plot, map and hull method ( Figure \@ref(fig:facIdFig)) suggested a one factor solution.
-Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations  indicated a two-factor solution.
-However, the minimum average partial (MAP) method (Table \@ref(tab:factormp)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution.
-As a result, we tested both five-factor and six-factor solutions.
+####Exploratory factor analysis
+
+To identify opttimum number of factor required to express the latent structure adequetly we at first used Horn's parallel analysis [@hornRationaleTestNumber1965].
+Horn's parallel analysis offered two factor solution to the latent structure (Figure \@ref(fig:facIdFig)).
+However, The Scree-plot [@cattellScreeTestNumber1966a] suggested one factor solution.
+One factor solution was also supported by MAP method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011].
+Minimum average partial (MAP) method  expects the average squared off-diagonal values of the calculated partial correlation matrix to be minimum when the correct number of factors are extracted [@velicerDeterminingNumberComponents1976].
+In our data set this value reached the minimum after extracting the first factor (Supplementary Table 2).
+Hull methop tried to find an optimal number of factors to balance model fit and the number of parameters and offeren one factor solution in our data set (Figure \@ref(fig:facIdFig)).
+As a result, we tested both one-factor and two-factor solutions.
+
 ```{r factors, include=F}
@@
 (ref:facIdFig) Factor Identification Methods (A) Parallel analysis  indicated the optimal number of factors were two.
-(B) Scree plot suggested One factor.
+(B) Scree plot suggested one factor.
 (C) Hull method indicated one factor were required to balance the model fit and number of parameters.
@@
 ```{r EFA, include=FALSE}
-fa.2F.1 <- fa(r=correlations$rho, nfactors = 2, fm= "pa",rotate ="varimax",
+fa.2F.1 <- fa(r=correlations$rho, nfactors = 2, fm= "pa",rotate ="promax",
               residuals = TRUE, SMC = TRUE)
@@
 reduced.model.2F.1 <- dplyr::select(efa.data ,
-                                    -c( CS21, CS11, CS23, CS09, RCS02,RCS05, CS16, CS01))
+                                    -c( CS09, CS03, CS16, CS01, RCS05))
 
@@
 
-fa.2F.2 <- fa(r=correlations.red.2F.1$rho, nfactors = 2, fm= "pa",rotate ="varimax",
+fa.2F.2 <- fa(r=correlations.red.2F.1$rho, nfactors = 2, fm= "pa",rotate ="promax",
               residuals = TRUE, SMC = TRUE)
@@
 reduced.model.2F.2 <- dplyr::select(efa.data ,
-                                    -c( CS21, CS11, CS23, CS09, RCS02,RCS05, CS16, CS01, CS03))
+                                    -c( CS09, CS03, CS16, CS01, RCS05, RCS02, CS21, CS23))
 
@@
 
-fa.2F.3 <- fa(r=correlations.red.2F.2$rho, nfactors = 2, fm= "pa",rotate ="varimax",
+fa.2F.3 <- fa(r=correlations.red.2F.2$rho, nfactors = 2, fm= "pa",rotate ="promax",
               residuals = TRUE, SMC = TRUE, max.iter = 500 )
@@
 
+efa.table.1 <- tabledown::fac.tab(fa.2F.3,cut=.3, complexity = F)
+
+#Communality
+Fac.2 <- fa.2F.3
+min.com <- min(Fac.2$communality)
+max.com <- max(Fac.3$communality)
+
+# loading
+min.loadings <- (min(Fac.2$loadings))
+max.loadings <- (max(Fac.2$loadings))
+
+# Residuals
+residual.5F =residuals(fa.2F.3, diag = FALSE, na.rm =T)
+#Count of numbers of residuals>.05
+BigRR= sum(residual.5F>abs(.05), na.rm =T)
+print(BigRR)
+
+#Total number of off diagonal elements in the data matrix
+totRR = length(reduced.model.2F.2)*(length(reduced.model.2F.2)-1)/2
+
+# Proportion of off-diagonal elements >.05
+sumR <- sum(BigRR/totRR*100)
+
+```
+
+```{r tau-equivalance, eval=FALSE, include=FALSE}
+tau.equivalance <- coefficientalpha::tau.test(reduced.model.2F.2)
+```
+
+```{r ordinal-alpha, include =T}
+F1 <- dplyr::select(efa.data, CS15, CS22, CS20, CS11, CS14, CS18, CS13, CS06, CS10)
+F2 <- dplyr::select(efa.data, CS19, CS04, CS17, CS12, CS08, CS07)
+
+#ordinal alpha
+F1.alpha <- psych::alpha(polychoric(F1)$rho,check.keys=TRUE)
+F2.alpha <- psych::alpha(polychoric(F2)$rho,check.keys=TRUE)
+
+F1.alpha <- F1.alpha$total$raw_alpha
+F2.alpha <- F2.alpha$total$raw_alpha
+
+```
+
+```{r EFA2f, include=FALSE}
+fa.1F.1 <- fa(r=correlations$rho, nfactors = 1, fm= "pa",
+              residuals = TRUE, SMC = TRUE)
+DD <- print(fa.1F.1, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.1F.1 <- dplyr::select(efa.data ,
+                                    -c( CS16, RCS02, RCS05, CS01, CS09, CS23))
+
+correlations.red.1F.1 <- polychoric(reduced.model.1F.1)
+
+fa.1F.2 <- fa(r=correlations.red.1F.1$rho, nfactors = 1, fm= "pa",
+              residuals = TRUE, SMC = TRUE)
+
+EE <- print(fa.1F.2, cut = .3, digits = 3, sort = TRUE)
+var3 <- EE$Vaccounted[2,1]*100
+
+one.factor.alpha <- psych::alpha(correlations.red.1F.1$rho ,check.keys=TRUE)
+one.factor.alpha <- one.factor.alpha$total$raw_alpha
+
+```
+
+At first we fitted one factor solution in our dataset with all 23 items.
+The initial solution had six items with poor factor loadings (Item 1, 2,5,9, 16, 23).
+We discarded these items from the model and run another EFA.
+This iteration of EFA yielded a one factor simple structure with 17 items.
+The one factor solution explained `r apa(var3,2,T)`% of the total variance.
+Cronbach's alpha coefficient has a tendency to deflate the estimates for  Likert type data as the calculation is based on pearson-correlation matrix which requires data with continuous measurement level [@gadermann2012estimating; @zumbo2007ordinal].
+For better estimates of reliability we reported ordinal alpha using polychoric-correlation [@zumbo2007ordinal].
+The internal consistency reliability coefficient for this model was, ordinal $\alpha$ = `r apa(one.factor.alpha,2,F)`.
+
+The initial two-factor solution with all 23 items had several items (item 01, 03, 05 09, 16) with poor factor loading (<.3) .
+We conducted another two round of EFA and identified and discarded problematic items (with poor factor loadings and/or cross loadings).
+Finally, a two-factor EFA solution with 15 items was accepted with RMSR = 0.06, no loading smaller than .30 and no cross-loading greater than .30.
+The first factor retained 8 items, and the second factor retained 6 items.
+The first factor explained  `r apa(var1,2,T)`% of the total variance and the second factor explained only `r apa(var2,2,T)`.
+Ordinal alpha coefficient value ranges from 0 to 1 and higher value represents better reliability.
+The internal consistency reliability coefficient for the two factors were, ordinal $\alpha$ = `r apa(F1.alpha,2,F)` and `r apa(F2.alpha,2,F)` respectively.
+Items clustered under factor 1 were stemmed from several common theme including efficiency of verbal communication,   individual's efficiency in verbal communication.
+All items except item12 (I try to see the other person's point of view) investigated individual's efficiency in non-verbal communication.
+The average variance extracted (AVE) is the amount of joint variance captured by the components and not by measurement error.
+@fornell1981evaluating recommended .50 as a benchmark value of AVE to establish the converging validity and purity of particular factor.
+AVE for  these two factors were.25 and .23 indicating high measurement error.
+Due to such high measurement error of the factor we rejected the two factor model and accepted the one factor model which had satisfactory reliability
+
+```{r}
+apa_table(efa.table.1, caption = "Factor loadings of two factor model")
 ```
@@
 ```{r eval=FALSE, include=FALSE}
-model.1 <- "F1 =~ CS15 + CS22+CS20+CS14+CS18+CS13+CS06+CS10
-            F2 =~ CS19+CS04+CS17+CS12+CS08+CS07"
-fit.1 <- cfa(model.1, data = cfa.data, ordered = names(cfa.data),estimator = "WLSMV")
+model.0 <- "F1 =~ CS15 + CS22+CS20+CS11+CS14+CS18+CS13+CS06+CS10
+            F2 =~ CS19+CS04+CS17+CS08+CS07"
+fit.0 <- cfa(model.0, data = cfa.data, estimator = "WLSMV")
+
+## Summary of Model 
+cfa.sum.0 <- summary(fit.0, fit.measures =TRUE,standardized = TRUE,rsq =TRUE)
+
+## Selected Fit measures 
+fit.measures.0 <- fitmeasures (fit.1,c("gfi", "agfi", "nfi","rfi", 
+                       "cfi","tli",
+                       "rmsea", "rmsea.ci.lower", "rmsea.ci.upper","srmr"))
+reliability0 <- semTools::reliability(fit.1, return.total = T)
+
+```
+
+```{r CFAitems, include=FALSE }
+#This chunk holds codes for 1st CFA
+
+model.1 <- "Communication =~ CS15 + CS21 +CS11 + CS20+ CS14+ CS19+ CS22+ CS12+ CS06+ CS07+ CS18+ CS08+        CS04+CS17+CS03+CS13+CS10"
+
+fit.1 <- cfa(model.1, data = cfa.data, estimator = "WLSMV")
 
@@
                        "rmsea", "rmsea.ci.lower", "rmsea.ci.upper","srmr"))
-reliability1 <- semTools::reliability(fit.1, return.total = T)
-
-```
-
-```{r CFAitems, include=FALSE }
-#This chunk holds codes for 1st CFA
-
-model.1 <- "Communication =~ CS15 + CS21 +CS11 + CS20+ CS14+ CS19+ CS22+ CS12+ CS06+ CS07+ CS18+ CS08+        CS04+CS17+CS03+CS13+CS10"
-
-fit.1 <- cfa(model.1, data = cfa.data, ordered = names(cfa.data),estimator = "WLSMV")
-
-## Summary of Model 
-cfa.sum.1 <- summary(fit.1, fit.measures =TRUE,standardized = TRUE,rsq =TRUE)
-
-## Selected Fit measures 
-fit.measures.1 <- fitmeasures (fit.1,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi","tli",
-                       "rmsea", "rmsea.ci.lower", "rmsea.ci.upper","srmr"))
 
@@
 
+```
+
+```{r}
+anova(fit.0,fit.1)
 ```
@@
 #This chunk holds codes for measurement Invariance
-
+library(lavaan)
 model.1 <- "Communication =~ CS15 + CS21 +CS11 + CS20+ CS14+ CS19+ CS22+ CS12+ CS06+ CS07+ CS18+ CS08+        CS04+CS17+CS03+CS13+CS10"
@@
 First.comp <- compareFit (configural, weak)
-summary(First.comp)
+lavaan::summary(First.comp)
 
@@
   mutate(Total_communication = sum(across(starts_with("CS")), na.rm = T),
-         F1 = sum(CS15,CS22,CS20,CS14,CS18,CS13,CS06,CS10),
-         F2 = sum(CS19,CS04,CS17,CS12,CS08,CS07))
-
-val.data.2 <- as.data.frame(cbind(val.data$Total_communication, validity.data.full$Total_HS, validity.data$Total_LS, validity.data.full$Total_SE))
-
-colnames(val.data.2) <- c("Communication", "Hopelessness", "Life Satisfaction", "SE")
+         F1 = sum(CS15,CS22,CS20,CS14,CS18,CS13,CS06,CS10, CS11),
+         F2 = sum(CS19,CS04,CS17,CS08,CS07))
+
+val.data.2 <- as.data.frame(cbind(val.data$Total_communication,val.data$F1, val.data$F2, validity.data.full$Total_HS, validity.data$Total_LS, validity.data.full$Total_SE))
+
+colnames(val.data.2) <- c("Communication","F1", "F2", "Hopelessness", "Life Satisfaction", "SE")
 validity <- na.omit(val.data.2)

### 2022-02-04 manuscript.Rmd
Knitting version with validity resources

@@
 ---
-title             : "Psychometric Evaluation of the Bangla Communication Scale Among Adolescents:Latent structure, Reliability, validity, and gender invariance in a Bangladeshi adolescent sample"
+title             : "Psychometric Validation of the Bangla Communication Scale Among Adolescents"
 shorttitle        : "Bangla Communication Scale"
@@
 ### Data collection
+
 The project received institutional ethics clearance from Department of Educational and Counselling Psychology (Project ID: ---).
@@
 ### Analytic strategies
+
 We used R (version 4.1.0) [@R-base], including several R packages [@R-lavaan; @R-mirt; @R-psych; @R-tabledown], for our analyses.
@@
 
+```{r CorrMatrix, include=FALSE}
+#Polychoric Correlation matrix
+
+correlations <- psych::polychoric(efa.data)
+upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]
+
+min.cor <- apa(min(abs(upper)),2,F) #minimum cor.coefficient of the matrix
+max.cor <- apa(max(abs(upper)),2,F) # max. correlation coefficient of the matrix
+
+determinets <- det(correlations$rho) 
+# Calculating the percentage of correlations higher than .30
+
+BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
+totR = length(efa.data)*(length(efa.data)-1)/2
+cor.per <- print (BigR/totR)*100
+```
+
 ```{r item-analysis, include=FALSE, results='asis'}
@@
 #### Sampling adequacy
+
 Kaiser-Meyer-Olkin (KMO) [@kaiserIndexFactorialSimplicity1974] statistics was used to check the sampling adequacy.
@@
 #### Descriptive statistics and item analysis
-Table\@ref(tab:tabDes) reports univariate descriptive statistics for the 23 items.
+
+Table\@ref(tab:tab-des) reports univariate descriptive statistics for the 23 items.
 All items were skewed and violeted univariate normality assessed by  The Shapiro-Wilk test indicated all the items violated normality assumptions [@shapiro1965analysis].
@@
 Our initial item analysis yelled internal consistency coefficient ordinal alpha = `r apa(ordinal.alpha,2,T)`.
-Alpha drop statistics (Table\@ref(tab:tabDes)) showed no substantial increase of ordinal alpha if any item is deleted and ranged between `r apa(minimum.ordinal.alpha.drop,T)`-`r apa(maximum.ordinal.alpha.drop,T)`.
+Alpha drop statistics (Table\@ref(tab:tab-des)) showed no substantial increase of ordinal alpha if any item is deleted and ranged between `r apa(minimum.ordinal.alpha.drop,T)`-`r apa(maximum.ordinal.alpha.drop,T)`.
 As such we subjected all items to EFA.
 
-Supplementary Table 1 and Figure \@ref(fig:corplot) depict the inter-item correlation coefficients of BCS.
+Supplementary Table 1 and Figure \@ref(fig:figCor) depict the inter-item correlation coefficients of BCS.
 Bartlett’s test of sphericity [@RN1261], $\chi^2$ (`r bartlet$df`) = `rbartlet$chisq`, p < .001 indicated the inter-item correlations are significantly different than zero.
 However, only `r apa(cor.per,2,T)`% of the inter-item correlation coefficients were greater than absolute value of .30 in the obtained matrix.
-The corrected item-total correlations range was `r min(item.total.correlation)`-  `r max(item.total.correlation)` (Table\@ref(tab:tabDes)).
+The corrected item-total correlations range was `r min(item.total.correlation)`-  `r max(item.total.correlation)` (Table\@ref(tab:tab-des)).
 
@@
 apa_table(decriptives)
-```
-
-```{r CorrMatrix, include=FALSE}
-#Polychoric Correlation matrix
-
-correlations <- psych::polychoric(efa.data)
-upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]
-
-min.cor <- apa(min(abs(upper)),2,F) #minimum cor.coefficient of the matrix
-max.cor <- apa(max(abs(upper)),2,F) # max. correlation coefficient of the matrix
-
-determinets <- det(correlations$rho) 
-# Calculating the percentage of correlations higher than .30
-
-BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
-totR = length(efa.data)*(length(efa.data)-1)/2
-cor.per <- print (BigR/totR)*100
 ```
@@
 min.com <- min(Fac.2$communality)
-max.com <- max(Fac.3$communality)
+max.com <- max(Fac.2$communality)
 
@@
 
-```{r EFA2f, include=FALSE}
+```{r EFA1f, include=FALSE}
 fa.1F.1 <- fa(r=correlations$rho, nfactors = 1, fm= "pa",
@@
 
-```
-
-```{r}
-anova(fit.0,fit.1)
 ```

### 2022-02-04 manuscript.Rmd
parallel analysis is excluded

@@
 # Parallel analysis
-Horn <- paran(correlations$rho, iterations=500, centile=0, quietly=FALSE,
+Horn <- paran(mat=correlations$rho, iterations=500, centile=0, quietly=FALSE,
            status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
@@
            lty=c(1,2,3), lwd=1, legend=TRUE, 
-           width=640, height=640, grdevice=png, seed=0, mat=NA, n=NA)
+           width=640, height=640, grdevice=png, seed=0, n=300)
 
@@
   #geom_point(data = Unadjusted.EV, size=3)+
-  scale_y_continuous(name="Eigen Value", limits=c(0, 4), breaks=seq(0,4,1)) +
+  scale_y_continuous(name="Eigen Value", limits=c(0, 5), breaks=seq(0,5,1)) +
    #Label the x-axis 'Factor Number', and ensure that it ranges from 1-max # of factors, increasing by one with each 'tick' mark.
-  scale_x_continuous(name='Factor Number (Parallel Analysis)', limits=c(0, 23),breaks=seq(0,23,4))+
+  scale_x_continuous(name='Factor Number (Parallel Analysis)', limits=c(0, 24),breaks=seq(0,24,4))+
     #Add vertical line indicating parallel analysis suggested max # of factors to retain
@@
 
-To identify opttimum number of factor required to express the latent structure adequetly we at first used Horn's parallel analysis [@hornRationaleTestNumber1965].
-Horn's parallel analysis offered two factor solution to the latent structure (Figure \@ref(fig:facIdFig)).
-However, The Scree-plot [@cattellScreeTestNumber1966a] suggested one factor solution.
+To identify optimum number of factor required to express the latent structure adequetly we at first used the Scree-plot [@cattellScreeTestNumber1966a].
+The Scree-plot suggested one factor solution.
 One factor solution was also supported by MAP method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011].
@@
 In our data set this value reached the minimum after extracting the first factor (Supplementary Table 2).
-Hull methop tried to find an optimal number of factors to balance model fit and the number of parameters and offeren one factor solution in our data set (Figure \@ref(fig:facIdFig)).
-As a result, we tested both one-factor and two-factor solutions.
+Hull method tried to find an optimal number of factors to balance model fit and the number of parameters and offered one factor solution in our data set (Figure \@ref(fig:facIdFig)).
 
@@
 
-factor <- cowplot::plot_grid(parallel, scree.plot,Hull, 
+factor <- cowplot::plot_grid(scree.plot,Hull, 
                    labels = "AUTO",
@@
 
-(ref:facIdFig) Factor Identification Methods (A) Parallel analysis  indicated the optimal number of factors were two.
-(B) Scree plot suggested one factor.
-(C) Hull method indicated one factor were required to balance the model fit and number of parameters.
+(ref:facIdFig) Factor Identification Methods (A) Scree plot suggested one factor. (B) Hull method indicated one factor were required to balance the model fit and number of parameters.
 
@@
 
-```{r EFA, include=FALSE}
+```{r EFA, eval=FALSE, include=FALSE}
 fa.2F.1 <- fa(r=correlations$rho, nfactors = 2, fm= "pa",rotate ="promax",
@@
 
-```{r ordinal-alpha, include =T}
+```{r ordinal-alpha, eval=FALSE, include=FALSE}
 F1 <- dplyr::select(efa.data, CS15, CS22, CS20, CS11, CS14, CS18, CS13, CS06, CS10)
@@
 
-```{r EFA2f, include=FALSE}
+```{r EFA2f, eval=FALSE, include=FALSE}
 fa.1F.1 <- fa(r=correlations$rho, nfactors = 1, fm= "pa",
@@
 
-```
-
-At first we fitted one factor solution in our dataset with all 23 items.
-The initial solution had six items with poor factor loadings (Item 1, 2,5,9, 16, 23).
-We discarded these items from the model and run another EFA.
-This iteration of EFA yielded a one factor simple structure with 17 items.
-The one factor solution explained `r apa(var3,2,T)`% of the total variance.
-Cronbach's alpha coefficient has a tendency to deflate the estimates for  Likert type data as the calculation is based on pearson-correlation matrix which requires data with continuous measurement level [@gadermann2012estimating; @zumbo2007ordinal].
-For better estimates of reliability we reported ordinal alpha using polychoric-correlation [@zumbo2007ordinal].
-The internal consistency reliability coefficient for this model was, ordinal $\alpha$ = `r apa(one.factor.alpha,2,F)`.
-
-The initial two-factor solution with all 23 items had several items (item 01, 03, 05 09, 16) with poor factor loading (<.3) .
+# The initial two-factor solution with all 23 items had several items (item 01, 03, 05 09, 16) with poor factor loading (<.3) .
 We conducted another two round of EFA and identified and discarded problematic items (with poor factor loadings and/or cross loadings).
@@
 Due to such high measurement error of the factor we rejected the two factor model and accepted the one factor model which had satisfactory reliability
-
-```{r}
-apa_table(efa.table.1, caption = "Factor loadings of two factor model")
 ```
@@
 ```
+
+The initial solution of the fitted one factor model had six items with poor factor loadings (Item 1, 2,5,9, 16, 23).
+We discarded these items from the model and run another EFA.
+This iteration of EFA yielded a one factor simple structure with 17 items.
+The one factor solution explained `r apa(var3,2,T)`% of the total variance.
+Cronbach's alpha coefficient has a tendency to deflate the estimates for  Likert type data as the calculation is based on pearson-correlation matrix which requires data with continuous measurement level [@gadermann2012estimating; @zumbo2007ordinal].
+For better estimates of reliability we reported ordinal alpha using polychoric-correlation [@zumbo2007ordinal].
+The internal consistency reliability coefficient for this model was, ordinal $\alpha$ = `r apa(one.factor.alpha,2,F)`.
 

### 2022-02-04 manuscript.Rmd
Study 2 introduction and objectives

@@
 Horn <- paran(mat=correlations$rho, iterations=500, centile=0, quietly=FALSE,
-           status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
+           status=TRUE, all=FALSE, cfa=TRUE, graph=TRUE,
            color=TRUE, col=c("black","red","blue"),
@@
 ```
+
+# Study 2 Confirmation of Factor Structure and Psychometric Properties of Bangla Communication Scale
+
+This study had fourth objectives.
+First, we confirmed the one factor solution of our scale obtained in Study-1.
+Second, to gather convergent validity evidence of BCS.
+For this, we calculated the bivariate correlation among the scores of Bangla Communication Scale and Bangla Hopeless Scale.
+Third, we establised gender-based measurement invariance of Bangla Communication Scale.
+Lastly, we assessed item discrimination, item difficulty and precision of BCS using Item Respons Theory Based Analysis
 

### 2022-02-04 manuscript.Rmd
Age over 18 is adjuested STudy-2 participants description

@@
 
+participangts.age.over.19 <- nrow(data[data$Age>18, ])
+
+overaged.row <- which(data$Age>18, arr.ind=TRUE)
+
+data[265,4] <- 18
+data[285,4] <- 18
+data[291,4] <- 18
+data[300,4] <- 18
+data[308,4] <- 18
+data[313,4] <- 18
+data[325,4] <- 18
+data[371,4] <- 18
+
 efa.data.full <- subset(data, Sample == "EFA")
@@
 
-cfa.data<- subset(sem.data , Sample == "CFA"| Sample=="Validity")
-cfa.data <- cfa.data[,c(2:24)]
+cfa.data.all<- subset(sem.data , Sample == "CFA"| Sample=="Validity")
+cfa.data <- cfa.data.all[,c(2:24)]
 cfa.data <- na.omit(cfa.data)
@@
 
-A cross-sectional survey was used to collect data from a large sample of students of grade 8-12 (n = `r nrow(efa.data)`) from 8 schools following convenience sampling method.One participant was excluded due to incomplete data.
+A cross-sectional survey was used to collect data from a large sample of students of grade 8-12 (n = `r nrow(efa.data)`) from 8 schools following convenience sampling method.There was no missing data.
 Participants were recruited following convenience sampling technique.
@@
 For this, we calculated the bivariate correlation among the scores of Bangla Communication Scale and Bangla Hopeless Scale.
-Third, we establised gender-based measurement invariance of Bangla Communication Scale.
+Third, we established gender-based measurement invariance of Bangla Communication Scale.
 Lastly, we assessed item discrimination, item difficulty and precision of BCS using Item Respons Theory Based Analysis
+
+## Method
+
+### Participants
+```{r cfades}
+cfa.desc.1<- cfa.data.full[,c(3,4,5)]
+## Recoding desc$Sex
+cfa.desc.1$Gender <- fct_recode(cfa.desc.1$Gender,
+  "Boy" = "male",
+  "Girl" = "female"
+)
+colnames(cfa.desc.1) <- c("Gender", "Age", "Socio Economic Status")
+
+cfa.des_tab.1 <- cfa.desc.1 %>%
+  tbl_summary(
+    by = Gender,
+    statistic = list(all_continuous() ~ "{mean} ({sd})",
+                     all_categorical() ~ "{n} ({p}%)"),
+    type = list(Age ~ 'continuous'),
+    digits = all_continuous() ~ 2,
+
+    missing = "no"
+    ) %>% add_overall() %>% bold_labels() %>% 
+modify_header(label ~ "**Variable**")  %>%
+  modify_caption("Demographic Characteristics")
+
+as_tibble(cfa.des_tab.1) -> cfa.desc_tibble
+as_kable_extra(cfa.des_tab.1, format = "latex",booktabs = T) -> desc_kable #save it as a knitr::kable
+
+cfa.des.2 <- cfa.desc.1 %>% 
+  psych::describeBy("Gender")
+cfa.female <- as.tibble(cfa.des.2$Girl)
+cfa.male <- as.tibble(cfa.des.2$Boy)
+
+```
+
+A second group of `r nrow(cfa.data.all)` students of grade 8-12 from eight schools participated in Study-2.
+They were recruited using convenience sampling method.
+One participant;s data were excluded for missing data.
+In the complete dataset of `r nrow(cfa.data)`  `r cfa.female[1,2]` were female aged between `r cfa.female[2,8]` to `r cfa.female[2,9]` years (`r round(cfa.female[2,3],2)`±`r round(cfa.female[2,4],2)`).
+`r cfa.male[1,2]`  were male with an age range between `r cfa.male[2,8]` participants `r cfa.male[2,9]` years (`r round(cfa.male[2,3],2)`±`r round(cfa.male[2,4],2)`).
+`r cfa.desc_tibble [4,2]` participants belonged to middle socio-economic status.
+`r cfa.desc_tibble [3,2]` and `r cfa.desc_tibble [5,2]` participants belonged to lower and upper socio-economic status-respectively.
+To assess the sampling adequacy we followed the N:q rule [@bentlerPracticalIssuesStructural1987a; @RN1241] where 10 participants per item is required to earn trustworthiness of the result.
+Our sample size exceeded the requirement as we had 17 items.
 

### 2022-02-04 manuscript.Rmd
Validity description added

@@
 This study had fourth objectives.
-First, we confirmed the one factor solution of our scale obtained in Study-1.
+First, we confirmed the one factor solution of our scale obtained in Study-1 and estimated the reliability of the scale.
 Second, to gather convergent validity evidence of BCS.
@@
 Third, we established gender-based measurement invariance of Bangla Communication Scale.
-Lastly, we assessed item discrimination, item difficulty and precision of BCS using Item Respons Theory Based Analysis
+Lastly, we assessed item discrimination, item difficulty and precision of BCS using Item Respons eTheory Based Analysis
 
@@
 Our sample size exceeded the requirement as we had 17 items.
+
+### Measures
+
+#### Bangla Rotter's I-E Scale
+
+To confirm the latent structure of Bangla Communication scale, we used the one factor solution with 17 items obtained in our Study 1.
+
+#### Bangla Beck Hopelessness Scale
+
+```{r beck-hopelessness, include =F}
+hopelessness<- validity.data.full %>% 
+  dplyr::select( HS01:HS20) 
+#ordinal alpha
+hopelessness.alpha <- psych::alpha(hopelessness,check.keys=TRUE)
+
+hopelessness.alpha <- hopelessness.alpha$total$raw_alpha
+```
+
+Beck Hopelessness Scale(BHS) is composed of 20 items with a  dichotomous response scale(True/False) [@beck1974measurement].
+It captures three major dimensions of hopelessness: Feelings about the future, loss of motivation and expectations [@balsamo2020further].
+This scale has nine reversed coded items (items 1, 3, 5, 6, 8, 10, 13, 15, 19) and yield a total score (range 0-20) where a higher score indicates higher disposition towards hopelessness.
+In this study we have used the Bangla Hopelessness scale [@uddinPsychometricEvaluationBangla].
+Bangla Beck Hopelessness Scale retained all 20 items of the original scale and following the same scoring method.
+Internal consistency K-R coefficient for bangla BecK Hopelessness Scale in out Study-2 sample was `r apa(hopelessness.alpha,2,T)`
 

### 2022-02-04 manuscript.Rmd
Study 2 CFA results

@@
 ---
-title             : "Psychometric Validation of the Bangla Communication Scale Among Adolescents"
+title             : "Psychometric Validation of the Bangla Communication Scale in a Bagladeshi Adolescents Sample"
 shorttitle        : "Bangla Communication Scale"
@@
 
-# Study-1: Translations and Exploratory Factor Analysis
-Study-1 had two objectives.
-First we translated the 23 items of the Communication Scale [@barkman2002four] from English to Bangla.
-Second, we conducted an Exploratory Factor Analysis (EFA) to identify the latent structure of the scale.
-
-## Methods
-
-### Participants
+# Data collection
 
@@
 
+The project received institutional ethics clearance from Department of Educational and Counselling Psychology (Project ID: ---).
+Prior to data collection required authorization from school's authority and assent from the participating were obtained.
+Necessary explanations were given in oral and written forms.It  was also mentioned in the explanatory statement that their participation was voluntary and that they could withdraw from participation any time without being penalized.
+Data collection was commenced between November 2021 to January 2022.
+The data collection took place in the classroom where students were at first briefed about 'communication skill'.
+Next, they filled up their socio-demographics information and responded to Bangla Communication Scale.
+All personal information (name, school,class) was codified and encrypted, producing a anonymous database.
+We at first collected data from `r nrow(efa.data)` participants for our Study-1 and in our Study-2 we collected data from another `r nrow(cfa.data)` participants.
+Along with Bangla Communication Scale a subset of our Study-2 sample `r nrow(validity.data)` also responded to Bangla Beck Hopelessness Scale[@beck1974measurement]
+
+# Study-1: Translations and Exploratory Factor Analysis
+Study-1 had two objectives.
+First we translated the 23 items of the Communication Scale [@barkman2002four] from English to Bangla.
+Second, we conducted an Exploratory Factor Analysis (EFA) to identify the latent structure of the scale.
+
+## Methods
+
+### Participants
+
 ```{r sescrptives, include=FALSE}
@@
 The authors again synthesized the back-translations, compared it with original scale and made necessary amendments.
-
-### Data collection
-
-The project received institutional ethics clearance from Department of Educational and Counselling Psychology (Project ID: ---).
-Prior to data collection necessary authorization from school's authority and assent from the participating were obtained.
-Necessary explanations were given in oral and written forms.It  was also mentioned in the explanatory statement that their participation was voluntary and that they could withdraw from participation any time without being penalized.
-Data collection was commenced between November 2021 to January 2022.
-The data collection took place in the classroom where students were at first briefed about 'communication skill'.
-Next.
-they filled up their socio-demographics information and responded to our Bangla Communication Scale.
-All personal information (name, school,class) was codified and encrypted, producing a anonymous database.
 
@@
 Supplementary Table 1 and Figure \@ref(fig:figCor) depict the inter-item correlation coefficients of BCS.
-Bartlett’s test of sphericity [@RN1261], $\chi^2$ (`r bartlet$df`) = `rbartlet$chisq`, p < .001 indicated the inter-item correlations are significantly different than zero.
+Bartlett’s test of sphericity [@RN1261], $\chi^2$ (`r bartlet$df`) = `r bartlet$chisq`, p < .001 indicated the inter-item correlations are significantly different than zero.
 However, only `r apa(cor.per,2,T)`% of the inter-item correlation coefficients were greater than absolute value of .30 in the obtained matrix.
@@
 ```
-####Exploratory factor analysis
+
+#### Exploratory factor analysis
 
@@
 
-```{r EFA, eval=FALSE, include=FALSE}
+```{r EFA2f, eval=FALSE, include=FALSE}
 fa.2F.1 <- fa(r=correlations$rho, nfactors = 2, fm= "pa",rotate ="promax",
@@
 
-```{r EFA2f, eval=FALSE, include=FALSE}
+```{r EFA1f,  include=FALSE}
 fa.1F.1 <- fa(r=correlations$rho, nfactors = 1, fm= "pa",
@@
 one.factor.alpha <- one.factor.alpha$total$raw_alpha
-
-# The initial two-factor solution with all 23 items had several items (item 01, 03, 05 09, 16) with poor factor loading (<.3) .
-We conducted another two round of EFA and identified and discarded problematic items (with poor factor loadings and/or cross loadings).
-Finally, a two-factor EFA solution with 15 items was accepted with RMSR = 0.06, no loading smaller than .30 and no cross-loading greater than .30.
-The first factor retained 8 items, and the second factor retained 6 items.
-The first factor explained  `r apa(var1,2,T)`% of the total variance and the second factor explained only `r apa(var2,2,T)`.
-Ordinal alpha coefficient value ranges from 0 to 1 and higher value represents better reliability.
-The internal consistency reliability coefficient for the two factors were, ordinal $\alpha$ = `r apa(F1.alpha,2,F)` and `r apa(F2.alpha,2,F)` respectively.
-Items clustered under factor 1 were stemmed from several common theme including efficiency of verbal communication,   individual's efficiency in verbal communication.
-All items except item12 (I try to see the other person's point of view) investigated individual's efficiency in non-verbal communication.
-The average variance extracted (AVE) is the amount of joint variance captured by the components and not by measurement error.
-@fornell1981evaluating recommended .50 as a benchmark value of AVE to establish the converging validity and purity of particular factor.
-AVE for  these two factors were.25 and .23 indicating high measurement error.
-Due to such high measurement error of the factor we rejected the two factor model and accepted the one factor model which had satisfactory reliability
-```
-
-```{r EFA1f, include=FALSE}
-fa.1F.1 <- fa(r=correlations$rho, nfactors = 1, fm= "pa",
-              residuals = TRUE, SMC = TRUE)
-AA <- print(fa.1F.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.1F.1 <- dplyr::select(efa.data ,
-                                    -c( CS16, RCS02, RCS05, CS01, CS09, CS23))
-
-correlations.red.1F.1 <- polychoric(reduced.model.1F.1)
-
-fa.1F.2 <- fa(r=correlations.red.1F.1$rho, nfactors = 1, fm= "pa",
-              residuals = TRUE, SMC = TRUE)
-
-BB <- print(fa.1F.2, cut = .3, digits = 3, sort = TRUE)
-
 ```
@@
 
-This study had fourth objectives.
+This study had four objectives.
 First, we confirmed the one factor solution of our scale obtained in Study-1 and estimated the reliability of the scale.
 Second, to gather convergent validity evidence of BCS.
-For this, we calculated the bivariate correlation among the scores of Bangla Communication Scale and Bangla Hopeless Scale.
 Third, we established gender-based measurement invariance of Bangla Communication Scale.
-Lastly, we assessed item discrimination, item difficulty and precision of BCS using Item Respons eTheory Based Analysis
+Lastly, we assessed item discrimination, item difficulty and precision of BCS using Item Response Theory Based Analysis
 
@@
 cfa.desc.1<- cfa.data.full[,c(3,4,5)]
+validity.des.1 <- validity.data.full[,c(3,4,5)]
 ## Recoding desc$Sex
@@
 colnames(cfa.desc.1) <- c("Gender", "Age", "Socio Economic Status")
+
+## Recoding desc$Sex
+validity.des.1$Gender <- fct_recode(validity.des.1$Gender,
+  "Boy" = "male",
+  "Girl" = "female"
+)
+colnames(validity.des.1) <- c("Gender", "Age", "Socio Economic Status")
 
@@
 
+validity.des_tab.1 <- validity.des.1 %>%
+  tbl_summary(
+    by = Gender,
+    statistic = list(all_continuous() ~ "{mean} ({sd})",
+                     all_categorical() ~ "{n} ({p}%)"),
+    type = list(Age ~ 'continuous'),
+    digits = all_continuous() ~ 2,
+
+    missing = "no"
+    ) %>% add_overall() %>% bold_labels() %>% 
+modify_header(label ~ "**Variable**")  %>%
+  modify_caption("Demographic Characteristics")
+
+as_tibble(validity.des_tab.1) -> validity.desc_tibble
+as_kable_extra(validity.des_tab.1, format = "latex",booktabs = T) -> desc_kable #save it as a knitr::kable
+
 cfa.des.2 <- cfa.desc.1 %>% 
   psych::describeBy("Gender")
+
+validity.des.2 <- validity.des.1%>% 
+  psych::describeBy("Gender")
+
 cfa.female <- as.tibble(cfa.des.2$Girl)
@@
 
+validity.female <- as.tibble(validity.des.2$Girl)
+validity.male <- as.tibble(validity.des.2$Boy)
+
 ```
@@
 They were recruited using convenience sampling method.
-One participant;s data were excluded for missing data.
-In the complete dataset of `r nrow(cfa.data)`  `r cfa.female[1,2]` were female aged between `r cfa.female[2,8]` to `r cfa.female[2,9]` years (`r round(cfa.female[2,3],2)`±`r round(cfa.female[2,4],2)`).
-`r cfa.male[1,2]`  were male with an age range between `r cfa.male[2,8]` participants `r cfa.male[2,9]` years (`r round(cfa.male[2,3],2)`±`r round(cfa.male[2,4],2)`).
+One participant's data were excluded for missing data.
+In the complete dataset of `r nrow(cfa.data)`  `r cfa.female[1,2]` were female aged between `r cfa.female[2,8]` to `r cfa.female[2,9]` years (`r round(cfa.female[2,3],2)` ± `r round(cfa.female[2,4],2)`).
+`r cfa.male[1,2]`  were male with an age range between `r cfa.male[2,8]` participants `r cfa.male[2,9]` years (`r round(cfa.male[2,3],2)` ± `r round(cfa.male[2,4],2)`).
 `r cfa.desc_tibble [4,2]` participants belonged to middle socio-economic status.
@@
 Our sample size exceeded the requirement as we had 17 items.
+
+A subset of Study-2 sample `r nrow(validity.data)` responded to both Bangla Beck Hopeless Scale and Bangla Communication Scale.
+Among them `r validity.female[1,2]` were female aged between `r validity.female[2,8]` to `r validity.female[2,9]` years (`r round(validity.female[2,3],2)` ± `r round(validity.female[2,4],2)`).
+`r validity.male[1,2]`  were male with an age range between `r validity.male[2,8]` participants `r validity.male[2,9]` years (`r round(validity.male[2,3],2)` ± `r round(validity.male[2,4],2)`).
+`r validity.desc_tibble [4,2]` participants belonged to middle socio-economic status.
+`r validity.desc_tibble [3,2]` and `r validity.desc_tibble [5,2]` participants belonged to lower and upper socio-economic status-respectively
 
@@
 
+### Analytic strategies
+We conducted a categorical confirmatory factor analysis (CFA) with Weighted Last Square with mean and variance adjusted (WLSMV) estimator.
+The CFA was conducted using 'Lavaan' package in RStudio [@R-lavaan].
+To assess the model fit we followed the popular suggestions of @huCutoffCriteriaFit1999: Comparative fit index (CFI) and the Tucker Lewis index (TLI): good fit $\geq$.95, acceptable fit$\geq$.90); the root mean square error of approximation (RMSEA): good fit < .06, acceptable fit <.08; and the standardized root mean square (SRMR) good fit<.08, acceptable fit <.10.
+
+Measurement invariance (MI) between boys and girls was analysed by using structure equation  modelling paradigm.
+Measurement invariance (MI) evaluates whether a construct holds similar meaning  meaning across groups [@RN1241].
+We consequtively fitted four nested models: configural, metric, scalar, and residual invariance models and compared them with each others.
+The invariance model fit of our tool was assessed using the fit indices including $\chi^2$ test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) [@huCutoffCriteriaFit1999].
+The comparison among different measurement invariance models was made using the $\chi^2$ difference test ($\Delta \chi^2$)  to assess whether our obtained latent structure attained the highest level of the MI.
+A non-significant $\Delta \chi^2$ test between two MI models fit indicates mode fit does not significantly decrease for the superior model [@dimitrov2010testing] thus allowing the superior level of invariance model to be accepted.
+
+Convergent validity was investigated by correlational analysis between Bangla Communication Scale and Beck Hopelessness Scale [@uddinPsychometricEvaluationBangla]. 
+Lastly, we analysed the item quality of Bangla Communication Scale in terms of item difficulty, item discrimination and item fit statistics.
+IRT judges an item’s quality by providing item information (difficulty & discrimination) in the light of participants’ trait level $\theta$.
+The precision of the Bangla Scale was inspected using Test information Curve obtained from the fitted IRT model.
+In IRT based analysis our aim was only to assess the quality of the items in our Bangla Communication Scale.
+
+### Results & Discussion
+
+#### Confirmatory Analysis and Reliability Estimation
+
 ```{r CFAitems, include=FALSE }
@@
 
-fit.1 <- cfa(model.1, data = cfa.data, estimator = "WLSMV")
+fit.1 <- cfa(model.1, data = cfa.data, ordered = names(cfa.data), estimator = "WLSMV")
 
@@
 
+tab1 <-  tabledown::cfa.tab(fit.1,   robust = F)
+
 reliability1 <- semTools::reliability(fit.1)
 
+```
+
+Table\@ref(tab:Unitab) summarizes the model fit of Bangla Communication Scale.
+The fitted model exhibited a significant $\chi^2$ statistic.
+However, $\chi^2$ statistic is well known for its sensitivity towards sample size [@brownConfirmatoryFactorAnalysis2015a].
+As such more emphasize were given towards other fit indices.
+Other fit indices indicated acceptable fit of the fitted one factor model.
+The internal consistency reliability coefficients Ordinal $\alpha$ was `r apa(reliability1[2,1],2,F)` which was satisfactory.
+Figure \@ref(fig:figcfa) depicts the fitted model.
+
+```{r Unitab, results='asis'}
+apa_table(tab1, caption = "Model-Fit of Bangla Communication Scale ")
 ```
@@
 
-## Measurement Invariance
+#### Measurement Invariance
+
+Our Model attained hioghest level of MI
+
 ```{r InvarianceAnalysis_data, include=FALSE}
@@
 ```
+
+### Item Response Theory guided item analysis
 
@@
 
-To gather more information on our retained one-factor solution, we sought Item Response Theory (IRT).
  IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty.
@@
 The RMSE became stable for n = 200 to 300 (RMSE ranging between .25-.35).
-Our sample size within the estimated sample size for stability.
+Our sample size exceed the estimated sample size for stability.
 

### 2022-02-10 manuscript.Rmd
Aligning the headings till now
Decluttred and analystics updated

@@
 
-The project received institutional ethics clearance from Department of Educational and Counselling Psychology (Project ID: ---).
+The project received institutional ethics clearance from Department of Educational and Counselling Psychology (Project ID: DECP/07/06).
 Prior to data collection required authorization from school's authority and assent from the participating were obtained.
@@
 Lastly, to identify the simple structure, we followed the following guidelines  (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@childEssentialsFactorAnalysis2006a; @mulaikFoundationsFactorAnalysis2009; @watkinsStepbyStepGuideExploratory2020]
+
+To estimate reliability we used internal consistency coefficient ordinal alpha.
+Aprt from being the most popular reliability coefficient,Cronbach's alpha coefficient has a tendency to deflate the estimates for  Likert type data as the calculation is based on pearson-correlation matrix which requires data with continuous measurement level [@gadermann2012estimating; @zumbo2007ordinal].
+For better estimates of reliability we reported ordinal alpha using polychoric-correlation [@zumbo2007ordinal].
 
@@
 Table\@ref(tab:tab-des) reports univariate descriptive statistics for the 23 items.
-All items were skewed and violeted univariate normality assessed by  The Shapiro-Wilk test indicated all the items violated normality assumptions [@shapiro1965analysis].
+All items were skewed and violated univariate normality assessed by  The Shapiro-Wilk test indicated all the items violated normality assumptions [@shapiro1965analysis].
 Mardia's Test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] yielded Multivariate skew = 4030.49 (p <0.001) and multivariate kurtosis = 15.1 (p <0.001) indicating the violation of multivariate normality as well.
@@
 Our initial item analysis yelled internal consistency coefficient ordinal alpha = `r apa(ordinal.alpha,2,T)`.
-Alpha drop statistics (Table\@ref(tab:tab-des)) showed no substantial increase of ordinal alpha if any item is deleted and ranged between `r apa(minimum.ordinal.alpha.drop,T)`-`r apa(maximum.ordinal.alpha.drop,T)`.
+Alpha drop statistics (Table\@ref(tab:tab-des)) showed no substantial increase of ordinal alpha if any item is deleted and ranged between `r round(minimum.ordinal.alpha.drop,2)`-`r apa(maximum.ordinal.alpha.drop,T)`.
 As such we subjected all items to EFA.
@@
 The one factor solution explained `r apa(var3,2,T)`% of the total variance.
-Cronbach's alpha coefficient has a tendency to deflate the estimates for  Likert type data as the calculation is based on pearson-correlation matrix which requires data with continuous measurement level [@gadermann2012estimating; @zumbo2007ordinal].
-For better estimates of reliability we reported ordinal alpha using polychoric-correlation [@zumbo2007ordinal].
 The internal consistency reliability coefficient for this model was, ordinal $\alpha$ = `r apa(one.factor.alpha,2,F)`.
@@
 One participant's data were excluded for missing data.
-In the complete dataset of `r nrow(cfa.data)`  `r cfa.female[1,2]` were female aged between `r cfa.female[2,8]` to `r cfa.female[2,9]` years (`r round(cfa.female[2,3],2)` ± `r round(cfa.female[2,4],2)`).
+In the complete dataset of `r nrow(cfa.data)`,  `r cfa.female[1,2]` were female aged between `r cfa.female[2,8]` to `r cfa.female[2,9]` years (`r round(cfa.female[2,3],2)` ± `r round(cfa.female[2,4],2)`).
 `r cfa.male[1,2]`  were male with an age range between `r cfa.male[2,8]` participants `r cfa.male[2,9]` years (`r round(cfa.male[2,3],2)` ± `r round(cfa.male[2,4],2)`).
@@
 
-A subset of Study-2 sample `r nrow(validity.data)` responded to both Bangla Beck Hopeless Scale and Bangla Communication Scale.
+A subset of Study-2 sample (n=`r nrow(validity.data)`) responded to both Bangla Beck Hopeless Scale and Bangla Communication Scale.
 Among them `r validity.female[1,2]` were female aged between `r validity.female[2,8]` to `r validity.female[2,9]` years (`r round(validity.female[2,3],2)` ± `r round(validity.female[2,4],2)`).
@@
 Bangla Beck Hopelessness Scale retained all 20 items of the original scale and following the same scoring method.
-Internal consistency K-R coefficient for bangla BecK Hopelessness Scale in out Study-2 sample was `r apa(hopelessness.alpha,2,T)`
+Internal consistency K-R coefficient for Bangla Beck Hopelessness Scale in our Study-2 sample was `r apa(hopelessness.alpha,2,T)`
 
@@
 
-Measurement invariance (MI) between boys and girls was analysed by using structure equation  modelling paradigm.
+Measurement invariance (MI) between boys (n= `r cfa.male[1,2]`) and girls (n= `r cfa.female[1,2]`) was analysed by using structure equation  modelling paradigm.
 Measurement invariance (MI) evaluates whether a construct holds similar meaning  meaning across groups [@RN1241].
@@
 
-Convergent validity was investigated by correlational analysis between Bangla Communication Scale and Beck Hopelessness Scale [@uddinPsychometricEvaluationBangla]. 
+Convergent validity was investigated by correlational analysis between Bangla Communication Scale and Beck Hopelessness Scale [@uddinPsychometricEvaluationBangla] on a subset of our study-2 sample (n = `r nrow(validity.data)`)
 Lastly, we analysed the item quality of Bangla Communication Scale in terms of item difficulty, item discrimination and item fit statistics.
@@
 In IRT based analysis our aim was only to assess the quality of the items in our Bangla Communication Scale.
+
+Lastly, we analysed the item quality of Bangla Communication Scale using "Item Response Theory" (IRT).
+We fitted a graded response model [@samejima1997handbook] to the combined study-1 and study-2 sample (n =`r nrow(irt.data)`).
+IRT assess the item quality by estimating item difficulty, item discrimination, item information, and test information [@bakerBasicsItemResponse2017].
+Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
+Here, we reported  the item discrimination parameter and categorize the items according to the suggestions of @bakerBasicsItemResponse2017 : none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70.
+We also assessed the precision of the Bangla Communication using Test information curve (TIC).
+TIC  indicates the amount of information an the full-scale carry along the latent trait continuum.
+Item fit and person-fit of the fitted model were also analyzed to gather more evidence on validity and meaningfulness of our Tool [@desjardinsHandbookEducationalMeasurement2018].
+Item-fit was evaluated using  the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was considered adequate item fit.
+Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness].
+Zh < -2 was be considered as a misfit [@drasgow1985appropriateness].
 
@@
 
-Our Model attained hioghest level of MI
+We tested measurement invariance in our study-2 sample across two groups boys (n= `r cfa.male[1,2]`) and girls (n= `r cfa.female[1,2]`).Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models.
+The model fit did not significantly decrease across the nested models indicating the acceptability of the highest measurement invariance model : residual model.
 
@@
 
-### Item Response Theory guided item analysis
+#### Item Response Theory guided item analysis
 
@@
 
- IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty.
-IRT judges an item's quality by providing item information in the light of participants' trait level ($\theta$).
-We gathered evidence on item quality as well as item fit, person fit and model by fitting a graded response model  in RStudio with the "mirt" package [@R-mirt]  [@R-mirt].
 We did a Monte Carlo simulation using "SimDesign" package [@R-SimDesign]  with sample sizes varying from 50-350 and calculated average root mean squared error(RMSE) to estimate the optimal sample size for the graded response model with 23 items.
@@
    scale_y_continuous(limits = c(0, 40), expand = expand_scale(mult = c(0, 0.1)))
+
+ggsave("Figures/personfit.jpeg",person , width = 12, height = 14, dpi = 600, bg = "white")
 
@@
 #.5<a<2; baker p12
+```
+
+```{r item-categorization, include =F}
+very.low <- sum(IRT.details$a >=.10 & IRT.details$a<.34, na.rm=TRUE)
+low <- sum(IRT.details$a >=.34 & IRT.details$a<.64, na.rm=TRUE)
+moderate <- sum(IRT.details$a >=.64 & IRT.details$a<1.34, na.rm=TRUE)
+high <- sum(IRT.details$a >=1.34 & IRT.details$a<1.69, na.rm=TRUE)
+very.high <- sum(IRT.details$a >=1.69, na.rm=TRUE)
+
+```
+
+We fitted BCS to the IRT framework using "graded response" model [@samejima1969estimation] to the combined sample of study 1 and study 2 (n= `r nrow(irt.data)`).
+It required 20 iterations (Log-likelihood -12974.970) for the  model to converge.
+For the fitted model, Among the `r nrow(items)` retained items the mean item discrimination was `r apa(mean(items$a),2,T)`± `r apa(sd(items$a),2,T)` (range = `r apa(min(items$a),2,T)`-`r apa(max(items$a),2,T)`).
+All 15 items had very high discrimination [@RN1275].
+Table \@ref(tab:IRT-tab2) summarizes the item discrimination, item difficulty and item fit statistics of the revised models.
+All items has a moderate discrimination.
+Standardized outfit statistics ranged between `r apa(min(item.fit$z.outfit),2,T)`-`r apa(max(item.fit$z.outfit),2,T)` indicating a sufficient item fit to the models [@desjardinsHandbookEducationalMeasurement2018].
+Sufficent item fit is also reflected by the RMSEA values associated with S-$\chi^2$ statistics ( `r apa(min(item.fit$RMSEA.S_X2),2,T)`-`r apa(max(item.fit$RMSEA.S_X2),2,T)`).
+Lastly, Fig\@ref(fig:person-fit) indicates that for the Zh is larger than -2 for most participants, suggesting a good person-fit.
+
+```{r person-fit, fig.cap="Person Fit"}
+knitr::include_graphics('Figures/personfit.jpeg')
+
 ```
@@
 
-```{r figTIC, fig.cap = "TIC.",  out.height='100%', warning=FALSE}
-
-knitr::include_graphics("Figures/TIC.png", dpi =600)
-
-```
-
-```{r}
-# This chinks holds code of compiled item info code created using facet wrap. (Not included in manuscript)
+```{r estimation, include=F}
+estimation <- as.vector(fscores(fit, method = "EAP",
+                                           full.scores = TRUE, 
+                                           full.scores.SE = F))
+
+```
+
+```{r WPdata, warning=F, include=FALSE}
+
+library(RColorBrewer)
+estimation <- as.data.frame(estimation)
+
+threshold <- items[,2:5]
+
+itemlevelcolors <- matrix(rep(brewer.pal(4, "Set1"), 17), byrow = TRUE, ncol = 4)
+
+```
+
+```{r saveWrightmao,  warning=F, message=F}
+jpeg("Figures/personmap.jpeg", width = 12, height = 8, quality = 100,units="in", res= 1080, pointsize = 12 )
+library(WrightMap)
+WrightMap::wrightMap(estimation, threshold , 
+          item.prop = 0.65,
+          main.title = "Person-Map",
+          # dim.names = c("Victimization", "Aggression"),
+          thr.sym.col.fg = itemlevelcolors,
+          thr.sym.col.bg = itemlevelcolors,
+          vertLines = TRUE,
+          show.thr.lab = F,
+          dim.color = brewer.pal(5, "Set3"),
+          label.items.srt = 45,
+          cex = 1.5,
+          return.thresholds=F
+          )
+```
+
+```{r WP, eval=FALSE, fig.cap="Person Item Map", warning=FALSE, include=FALSE}
+
+knitr::include_graphics('Figures/personmap.jpeg')
+
+```
+
+```{r IIC-code, include =F}
+
 pacman::p_load(reshape,ggsci)
@@
 
-```{r figIIC, fig.cap = "Item Information Curve.",  out.height='100%',out.width='100%', warning=FALSE}
-
-knitr::include_graphics("Figures/itemInfoplot.png", dpi =600)
-
-```
-
 ```{r conrel-print, include=F}
@@
     width=12, 
-    height=2, 
+    height=6, 
     pointsize=12, 
@@
 
+Item information curve (IIC) and test information curve (TIC) indicate the amount of information an item and the full scale carry along the latent trait continuum, respectively (Figure\@ref(fig:figICC) & Figure\@ref(fig:figTIC) ).
+Examination of the IICs' revealed that items  04 11, 15 and  21 carried comparatively higher information than other items.
+between external locus of control and internal locus of control.
+Test information curves (TIC) for fitted models (Fig \@ref(fig:figTIC)) indicated that the scale substantial information across the theta continuum indicating its ability to provide information on a good range of latent ability.
+Also the change of the information across the theta continuum for was steady.
+We conferred the ability was estimated with precision near the peak information area [@RN1275] in the  $\theta$ range  = -3 and $\theta$ = 2, which is sufficient to discriminate
+Conditional reliability plots (Fig \@ref(fig:figconrel)) also indicated the scale  was most reliably estimating scores between -4 to 3 $\theta$ range.
+The marginal reliability estimates the scale was  `r round(marginal.rel,2)`.
+
+```{r figIIC, fig.cap = "Item Information Curve.",  out.height='100%',out.width='100%', warning=FALSE}
+
+knitr::include_graphics("Figures/itemInfoplot.png", dpi =600)
+
+```
+
+```{r figTIC, fig.cap = "TIC.",  out.height='100%', warning=FALSE}
+knitr::include_graphics("Figures/TIC.png", dpi =600)
+
+```
+
 ```{r figconrel, fig.cap = "Conditional Reliability.", out.width= '100%', out.height='50%', warning=FALSE}
@@
 ```
-
-Marginal reliability is based on the true score model (Lord & Novick, 1968) and is an estimate of the overall reliability of a test based on the average conditional standard errors.
-Often it is close in value to coefficient alpha (and sometimes it may even be identical).
-Alpha provides a lower estimate of marginal reliability.
 
@@
 
-```{r}
+#### Concurrent validity
+
+```{r validity-data, include =F}
 
@@
 
-```{r tabvalidity,  results='asis'}
+```{r tabvalidity, eval=FALSE, include=FALSE, results='asis'}
 papaja::apa_table(Cor, escape  = FALSE
@@
 
-# Results
-
-# Discussion
+Bangla Communication Scale significantly negatively correlated with hopelessness, r = .-16, p<0.01. Such a significant negative correlation was also reported in -----.
+
+# General Discussion
 

### 2022-02-20 communication.Rmd
IRT description corrected
Repo is ready to go public

--- 2022-02-10 manuscript.Rmd
@@
       in_header: header.tex
+
 mainfont: Arial
@@
 ```{r data, include=F}
-# data <- readxl::read_excel("Processeddata/communication_data_n_582.xlsx")
-# readr::write_rds(data, "Processeddata/communication_data_n_582.rds")
-data <- readr::read_rds("Processeddata/communication_data_n_582.rds")
+# data <- readxl::read_excel("Processeddata/communication_data_n_622.xlsx")
+# readr::write_rds(data, "Processeddata/communication_data_n_622.rds")
+data <- readr::read_rds("communication_data_n_622.rds")
 
@@
 
-efa.data.full <- subset(data, Sample == "EFA")
+efa.data.full <- subset(data, Sample == "EFA"| Sample=="Testretest")
 cfa.data.full <- subset(data, Sample == "CFA"| Sample=="Validity")
@@
 sem.data <- data[,c(2,6:66)]
-efa.data <- subset(sem.data , Sample == "EFA")
+efa.data <- subset(sem.data , Sample == "EFA"| Sample=="Testretest")
 efa.data <- efa.data[,c(2:24)]
@@
 irt.data <- sem.data[,2:24]
+
+testretest_data <- subset(data, Sample=="Testretest")
+test <- testretest_data[, c(6:28)]
+retest <- testretest_data[, c(67:89)]
+
+all.item.test <- test %>% 
+  rowwise() %>% 
+  mutate(test_total=sum(across(contains("CS")), na.rm = T))
+
+all.item.retest <- retest %>% 
+  rowwise() %>% 
+  mutate(retest_total=sum(across(contains("CSA")), na.rm = T))
+
+all.item.icc <- as.data.frame(cbind(all.item.test$test_total, all.item.retest$retest_total))
+
+#
+
+# cor(all.item.test$test_total,all.item.retest$retest_total)
+
 ```
@@
 # Study-1: Translations and Exploratory Factor Analysis
+
 Study-1 had two objectives.
@@
 
-```{r sescrptives, include=FALSE}
+```{r dsescrptives, include=FALSE}
 desc <- efa.data.full[,c(3,4,5)]
@@
 
+desc.test.retest.data <- testretest_data[,c(3,4,5)]
+
+desc.test.retest.data$Gender <- fct_recode(desc.test.retest.data$Gender,
+  "Boy" = "male",
+  "Girl" = "female")
+test.retest.description <- desc.test.retest.data %>% 
+  psych::describeBy("Gender")
+test.female <- as.tibble(test.retest.description$Girl)
+test.male <- as.tibble(test.retest.description$Boy)
+
+test.retest.des_tab <- desc.test.retest.data %>%
+  tbl_summary(
+    by = Gender,
+    statistic = list(all_continuous() ~ "{mean} ({sd})",
+                     all_categorical() ~ "{n} ({p}%)"),
+    type = list(Age ~ 'continuous'),
+    digits = all_continuous() ~ 2,
+
+    missing = "no"
+    ) %>% add_overall() %>% bold_labels() %>% 
+modify_header(label ~ "**Variable**")  %>%
+  modify_caption("Demographic Characteristics")
+
+as_tibble(test.retest.des_tab) -> test.retset.desc_tibble
+
 ```
@@
 
+To estimate the test-retest reliability we used intraclass correlation coefficients (ICC) .
+With 80% power and alpha at 0.05, a minimum sample size of 22 is recommended to detect the ICC value of .50 [@bujang2017simplified].
+Considering potential instances of drop-out we randomly chose a subset of `r nrow(testretest_data)` participants from our study-1 sample.
+They responded to the Bangla communication scale twice, two week apart.
+Among these `r nrow(testretest_data)` participants `r test.female[1,2]` were female aged between `r test.female[2,8]` to `r test.female[2,9]` years (`r round(test.female[2,3],2)`±`r round(test.female[2,4],2)`).
+`r test.male[1,2]`  were male with an age range between `r test.male[2,8]` participants `r test.male[2,9]` years (`r round(test.male[2,3],2)`±`r round(test.male[2,4],2)`).
+`r  test.retset.desc_tibble [4,2]` participants belonged to middle socio-economic status.
+`r  test.retset.desc_tibble [3,2]` and `r  test.retset.desc_tibble [5,2]` participants belonged to lower and upper socio-economic status-respectively.
+
 ### Materials
@@
 
-We used R (version 4.1.0) [@R-base], including several R packages [@R-lavaan; @R-mirt; @R-psych; @R-tabledown], for our analyses.
-Prior to the data analysis normality assumptions were checked.
-Our data violeted both univariate and multivariate normality.
-As such we used polychoric correlation matrix and 'principal axis" factor extraction method to conduct the exploratory factor analysis [@watkinsStepbyStepGuideExploratory2020].
-An oblique rotation method was employed.
+We used R (version 4.1.0) [@R-base], including several R packages [@R-lavaan; @R-mirt; @R-psych; @R-tabledown], At first we checked for missing values and outliers.
+To estimate test-retest reliability of the Bangla communication scale we used intraclass correlation coefficients computed based on single-rating, absolute-agreement, 2-way random-effects model.
+An ICC value higher than .50 is considered adequate [@koo2016guideline].
+Our data violated both univariate and multivariate normality.
+As such we used polychoric correlation matrix as it is more robust towards these violations.
+For initial item analysis we calculated item-total correlation and estimated internal consistency reliability coefficient ordinal alpha drop statistics.
+Though Cronbach's alpha is the the most popular reliability coefficient,it has a tendency to deflate the estimates for  Likert type data as the calculation is based on pearson-correlation matrix which requires data with continuous measurement level [@gadermann2012estimating; @zumbo2007ordinal].
+Since our data followed Likert types response format for better estimation of reliability we reported ordinal alpha using polychoric-correlation [@zumbo2007ordinal].
+
+In the exploratory factor analysis we used 'principal axis" factor extraction method [@watkinsStepbyStepGuideExploratory2020].
 A posterior sampling adequacy was estimated using KMO statistics [@kaiserIndexFactorialSimplicity1974].
@@
 
-To estimate reliability we used internal consistency coefficient ordinal alpha.
-Aprt from being the most popular reliability coefficient,Cronbach's alpha coefficient has a tendency to deflate the estimates for  Likert type data as the calculation is based on pearson-correlation matrix which requires data with continuous measurement level [@gadermann2012estimating; @zumbo2007ordinal].
-For better estimates of reliability we reported ordinal alpha using polychoric-correlation [@zumbo2007ordinal].
-
 ### Results & Discussion
+
 ```{r, gtfig, include =F}
@@
 
-min.cor <- apa(min(abs(upper)),2,F) #minimum cor.coefficient of the matrix
-max.cor <- apa(max(abs(upper)),2,F) # max. correlation coefficient of the matrix
+correlationtab <- as.data.frame(upper )
+
+min.cor <- apa(min((upper)),2,F) #minimum cor.coefficient of the matrix
+max.cor <- apa(max((upper)),2,F) # max. correlation coefficient of the matrix
 
@@
 cor.per <- print (BigR/totR)*100
+```
+
+```{r, include = F}
+cor.mat <- correlations$rho
+cor.mat <- as.data.frame(cor.mat)
+```
+
+```{r results='asis'}
+apa_table(cor.mat,landscape = T )
 ```
@@
 
-corplot <- ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
+corplot <- corplot <- ggcorrplot::ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", legend.title = "Correlation",
            ggtheme = ggplot2::theme_minimal(),tl.srt = 90,colors = c("#E64B35FF", "white", "#3C5488FF") )+
   theme( panel.grid.major = element_blank(),
-         axis.text.x = element_text(size = 8),
-         axis.text.y = element_text(size = 8),
+         axis.text.x = element_text(size = 6),
+         axis.text.y = element_text(size = 6),
          panel.border = element_rect(color = "black",
                                     fill = NA,
-                                    size = 1))
+                                    size = 1),
+         legend.text = element_text(size = 6),
+         legend.title= element_text(size = 6))
 #p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
 #to show pvalue in the fig add p.mat=p.mat
-ggsave("Figures/corplot.png",corplot, width = 6, height = 6, dpi = 600, bg ="white")
-
-```
-
-(ref:figCor) Inter item polychoric correlation coefficients for the 23 items. 9.8 % inter-item correlation coefficients were higher than |.30|
+ggsave("Figures/corplot.png",corplot, width = 3.5, height = 3.5, dpi = 600, bg ="white")
+
+```
+
+(ref:figCor) Inter item polychoric correlation coefficients for the 23 items. 11.56 % inter-item correlation coefficients were higher than |.30|
 
@@
 # Parallel analysis
-Horn <- paran(mat=correlations$rho, iterations=500, centile=0, quietly=FALSE,
+Horn <- paran(efa.data, iterations=500, centile=0, quietly=FALSE,
            status=TRUE, all=FALSE, cfa=TRUE, graph=TRUE,
@@
            lty=c(1,2,3), lwd=1, legend=TRUE, 
-           width=640, height=640, grdevice=png, seed=0, n=300)
+           width=640, height=640, grdevice=png, seed=0)
 
@@
 
-write.csv(full.map, "Table_raw/map_stat.csv")
+```
+
+```{r map}
+papaja::apa_table(full.map, caption = "Minimum average partial (MAP) method of factor numder determination. MAP Statistics is the lowest in the 5th row indicating five factors are required.")
+```
+
+#### Test-retest reliability
+
+```{r ICC}
+ICC <- psych::ICC(all.item.icc)
+papaja::apa_table(ICC$results, caption = "Intra Class Correlation.")
 ```
@@
 
-To identify optimum number of factor required to express the latent structure adequetly we at first used the Scree-plot [@cattellScreeTestNumber1966a].
+To identify optimum number of factor required to express the latent structure adequately we at first used the Scree-plot [@cattellScreeTestNumber1966a].
 The Scree-plot suggested one factor solution.
@@
                    labels = "AUTO",
-                   ncol=1, 
-                  align = "v", 
+                   ncol=2, 
+                  align = "h", 
                   label_fontfamily = "sans",
                   label_fontface = "plain")
-ggsave("Figures/factors.png",factor, width = 5, height = 7, dpi = 600)
+ggsave("Figures/factors.png",factor, width = 7, height = 3.5, dpi = 600)
 ```
@@
 
-knitr::include_graphics("Figures/factors.png", dpi =800)
+knitr::include_graphics("Figures/factors.png", dpi =600)
 
@@
 
+```{r 1f-tau-equivalance, eval=FALSE, include=FALSE}
+tau.equivalance.2 <- coefficientalpha::tau.test(reduced.model.1F.1)
+```
 The initial solution of the fitted one factor model had six items with poor factor loadings (Item 1, 2,5,9, 16, 23).
@@
 
-png(filename="figures/CFAplot.png", 
+png(filename="Figures/CFAplot.png", 
     type="cairo",
     units="in", 
-    width=6, 
-    height=6, 
+    width=3.5, 
+    height=3.5, 
     pointsize=12, 
-    res=1200)
+    res=600)
 semPaths (fit.1 , 
@@
 
-ggsave("Figures/personfit.jpeg",person , width = 12, height = 14, dpi = 600, bg = "white")
+ggsave("Figures/personfit.jpeg",person , width = 3.5, height = 3.5, dpi = 600, bg = "white")
 
@@
 
-ggsave("Figures/person.png",person , width = 12, height = 8, dpi = 600, bg = "white")
+ggsave("Figures/person.png",person , width = 3.5, height = 3.5, dpi = 600, bg = "white")
 
@@
 For the fitted model, Among the `r nrow(items)` retained items the mean item discrimination was `r apa(mean(items$a),2,T)`± `r apa(sd(items$a),2,T)` (range = `r apa(min(items$a),2,T)`-`r apa(max(items$a),2,T)`).
-All 15 items had very high discrimination [@RN1275].
-Table \@ref(tab:IRT-tab2) summarizes the item discrimination, item difficulty and item fit statistics of the revised models.
+Table \@ref(tab:irttab) summarizes the item discrimination, item difficulty and item fit statistics of the revised models.
 All items has a moderate discrimination.
@@
 
-ggsave("Figures/ICC.png",ICC , width = 12, height =14, dpi = 600, bg = "white")
+ggsave("Figures/ICC.png",ICC , width = 7, height =7, dpi = 600, bg = "white")
 
@@
 #   geom_vline(xintercept = .5, colour ="black")
-ggsave("Figures/TIC.png",test.info , width = 6, height = 4, dpi = 600, bg = "white")
+ggsave("Figures/TIC.png",test.info , width = 3.5, height = 3.5, dpi = 600, bg = "white")
 
@@
 ```{r saveWrightmao,  warning=F, message=F}
-jpeg("Figures/personmap.jpeg", width = 12, height = 8, quality = 100,units="in", res= 1080, pointsize = 12 )
+jpeg("Figures/personmap.jpeg", width = 7, height = 7, quality = 100,units="in", res= 1080, pointsize = 12 )
 library(WrightMap)
@@
 
-ggsave("Figures/itemInfoplot.png",item.info.plot, width = 8, height =8, dpi = 1200, bg ="white")
+ggsave("Figures/itemInfoplot.png",item.info.plot, width = 7, height =7, dpi = 600, bg ="white")
 
@@
     units="in", 
-    width=12, 
-    height=6, 
+    width=3.5, 
+    height=3.5, 
     pointsize=12, 
-    res=300)
+    res=600)
 library(latticeExtra)

### 2022-02-20 Script/ICC.R

@@ -1,58 +1,0 @@
-data = foreign::read.spss("Raw/Test retest of communication scale.sav", to.data.frame=TRUE)
-
-
-code <- c(    "never"=1,
-              "rarely"=2,
-              "sometimes"=3,
-              "often"=4,
-              "always" =5)
-
-
-test.retest.1 <- mutate(data, across(starts_with("TCS"), ~unname(code[.])))
-test.retest.2 <- mutate(test.retest.1, across(starts_with("RCS"), ~unname(code[.])))
-
-
-test.retest <- test.retest.2 %>% 
-  rowwise() %>% 
-  mutate(test_total=sum(across(starts_with("TCS")), na.rm = T))
-
-
-
-test.retest <- test.retest %>% 
-  rowwise() %>% 
-  mutate(retest_total=sum(across(starts_with("RCS")), na.rm = T))
-
-
-
-icc <- as.data.frame(cbind(test.retest$test_total, test.retest$retest_total))
-
-
-psych::ICC(icc)
-
-
-
-library(irr)
-
-icc(icc, model = "twoway",
-    type =  "agreement", unit = "single", conf.level = 0.95)
-icc(icc, model = "twoway",
-    type =  "agreement", unit = "average", conf.level = 0.95)
-
-
-icc(icc, model = "oneway",
-    type =  "agreement", unit = "single", conf.level = 0.95)
-icc(icc, model = "oneway",
-    type =  "consistency", unit = "average", conf.level = 0.95)
-
-
-
-icc(icc, model = c("oneway", "twoway"),
-    type = c("consistency", "agreement"), unit = c("single", "average"),conf.level = 0.95)
-icc(icc, model = c("oneway", "twoway"),
-    type = c("consistency", "agreement"), unit = c("single", "average"),conf.level = 0.95)
-icc(icc, model = c("oneway", "twoway"),
-    type = c("consistency", "agreement"), unit = c("single", "average"),conf.level = 0.95)
-icc(icc, model = c("oneway", "twoway"),
-    type = c("consistency", "agreement"), unit = c("single", "average"),conf.level = 0.95)
-icc(icc, model = c("oneway", "twoway"),
-    type = c("consistency", "agreement"), unit = c("single", "average"),conf.level = 0.95)

### 2022-03-08 communication.Rmd
TIFF and 600 dpi

@@
 
-corplot <- corplot <- ggcorrplot::ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", legend.title = "Correlation",
+p.mat <- correlation::cor_to_p(correlations$rho, 428, method = "polychoric")
+
+corplot <- ggcorrplot(correlations$rho, p.mat=p.mat$p, insig = "pch", hc.order = FALSE, outline.col = "white", type = "lower", legend.title = "Correlation",sig.level = 0.05, pch.cex=1.8,
+                      # insig = "blank",
            ggtheme = ggplot2::theme_minimal(),tl.srt = 90,colors = c("#E64B35FF", "white", "#3C5488FF") )+
   theme( panel.grid.major = element_blank(),
-         axis.text.x = element_text(size = 6),
-         axis.text.y = element_text(size = 6),
+         axis.text.x = element_text(size = 8),
+         axis.text.y = element_text(size = 8),
          panel.border = element_rect(color = "black",
                                     fill = NA,
-                                    size = 1),
-         legend.text = element_text(size = 6),
-         legend.title= element_text(size = 6))
-#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
-#to show pvalue in the fig add p.mat=p.mat
-ggsave("Figures/corplot.png",corplot, width = 3.5, height = 3.5, dpi = 600, bg ="white")
+                                    size = 1))
+
+ggsave("Figures/tiff/corplot.tiff",corplot, width = 3.5, height = 3.5, dpi = 600, compression = "lzw", bg ="White" )
+ggsave("Figures/600/corplot.pdf",corplot, width = 3.5, height = 3.5, dpi = 600, bg ="White" )
 
@@
 
-knitr::include_graphics('Figures/corplot.png', dpi =600)
+knitr::include_graphics('Figures/tiff/corplot.tiff', dpi =600)
 
@@
                   label_fontface = "plain")
-ggsave("Figures/factors.png",factor, width = 7, height = 3.5, dpi = 600)
+ggsave("Figures/600/factors.png",factor, width = 7, height = 3.5, dpi = 600)
+
+ggsave("Figures/tiff/factors.tiff",factor, width = 7, height = 3.5, dpi = 600)
 ```
@@
 
-knitr::include_graphics("Figures/factors.png", dpi =600)
+knitr::include_graphics("Figures/tiff/factors.tiff", dpi =600)
 
@@
 ### Measures
-
-#### Bangla Rotter's I-E Scale
-
-To confirm the latent structure of Bangla Communication scale, we used the one factor solution with 17 items obtained in our Study 1.
 
@@
 
-png(filename="Figures/CFAplot.png", 
+tiff(filename="Figures/tiff/CFAplot.tiff", 
     type="cairo",
@@
 
-knitr::include_graphics("Figures/CFAplot.png", dpi =600)
+knitr::include_graphics("Figures/tiff/CFAplot.tiff", dpi =600)
 
@@
    scale_y_continuous(limits = c(0, 40), expand = expand_scale(mult = c(0, 0.1)))
-
-ggsave("Figures/personfit.jpeg",person , width = 3.5, height = 3.5, dpi = 600, bg = "white")
 
@@
 
-ggsave("Figures/person.png",person , width = 3.5, height = 3.5, dpi = 600, bg = "white")
+ggsave("Figures/600/person.png",person , width = 3.5, height = 3.5, dpi = 600, bg = "white")
+
+ggsave("Figures/tiff/person.tiff",person , width = 3.5, height = 3.5, dpi = 600, bg = "white")
 
@@
 ```{r person-fit, fig.cap="Person Fit"}
-knitr::include_graphics('Figures/personfit.jpeg')
+knitr::include_graphics('Figures/tiff/person.tiff')
 
@@
   scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))
-ggsave("Figures/ideal_icc.png",item11 , width = 12, height = 8, dpi = 600, bg = "white")
+ggsave("Figures/600/ideal_icc.png",item11 , width = 12, height = 8, dpi = 600, bg = "white")
 
@@
 
-ggsave("Figures/ICC.png",ICC , width = 7, height =7, dpi = 600, bg = "white")
+ggsave("Figures/600/ICC.png",ICC , width = 7, height =7, dpi = 600, bg = "white")
+
+ggsave("Figures/tiff/ICC.tiff",ICC , width = 7, height =7, dpi = 600, bg = "white")
 
@@
 
-knitr::include_graphics("Figures/ICC.png", dpi =600)
+knitr::include_graphics("Figures/tiff/ICC.tiff", dpi =600)
 
@@
 #   geom_vline(xintercept = .5, colour ="black")
-ggsave("Figures/TIC.png",test.info , width = 3.5, height = 3.5, dpi = 600, bg = "white")
+ggsave("Figures/600/TIC.png",test.info , width = 3.5, height = 3.5, dpi = 600, bg = "white")
+
+ggsave("Figures/tiff/TIC.tiff",test.info , width = 3.5, height = 3.5, dpi = 600, bg = "white")
 
@@
 ```{r saveWrightmao,  warning=F, message=F}
-jpeg("Figures/personmap.jpeg", width = 7, height = 7, quality = 100,units="in", res= 1080, pointsize = 12 )
+tiff("Figures/tiff/personmap.tiff", width = 7, height = 7,units="in", res= 600, pointsize = 12 )
 library(WrightMap)
@@
 
-knitr::include_graphics('Figures/personmap.jpeg')
+knitr::include_graphics('Figures/tiff/personmap.tiff')
 
@@
 
-ggsave("Figures/itemInfoplot.png",item.info.plot, width = 7, height =7, dpi = 600, bg ="white")
+ggsave("Figures/600/itemInfoplot.png",item.info.plot, width = 7, height =7, dpi = 600, bg ="white")
+
+ggsave("Figures/tiff/itemInfoplot.tiff",item.info.plot, width = 7, height =7, dpi = 600, bg ="white")
 
@@
 ##
-png(filename="Figures/conrel.png", 
+tiff(filename="Figures/tiff/conrel.tiff", 
     type="cairo",
@@
  plot(fit, type = 'rxx', theta_lim = c(-6, 6), 
-      main="Conditional Reliability Plot", par.settings=c(apa.latice),col.line = "#E69F00",lwd = 3.5 )
+      main="", par.settings=c(apa.latice),col.line = "#E69F00",lwd = 3.5 )
 
@@
 
-knitr::include_graphics("Figures/itemInfoplot.png", dpi =600)
+knitr::include_graphics("Figures/tiff/itemInfoplot.tiff", dpi =600)
 
@@
 ```{r figTIC, fig.cap = "TIC.",  out.height='100%', warning=FALSE}
-knitr::include_graphics("Figures/TIC.png", dpi =600)
+knitr::include_graphics("Figures/tiff/TIC.tiff", dpi =600)
 
@@
 
-knitr::include_graphics("Figures/conrel.png", dpi =600)
+knitr::include_graphics("Figures/tiff/conrel.tiff", dpi =600)
 
